### 2011-02-28 docs/crowdy_gui.tex
added the report for CHI

\documentclass{sig-alternate}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{url}
\usepackage{subfigure}

\begin{document}

\title{Crowdy: Social Crowd Visualization}

\numberofauthors{1} 
\author{\alignauthor Jeffrey McGee, Zhiyuan Cheng, Chiao-Fang Hsu, Pratheek Kumar Akireddy \\
\affaddr{Department of Computer Science and Engineering, Texas A\&M University} \\ \affaddr{ College Station, TX 77845 USA} \\
\email{jeffamcgee@gmail.com, chengzhy@gmail.com, drakihsu@cse.tamu.edu, pka293@cse.tamu.edu}
}

\maketitle
\begin{abstract}
Microblogging systems has provided the society with a more transparent channel for information distribution. Each individuals are empowered to spread the news and build their social networks. With the freedom of information generation, the issue now is the ``useful information'' identification, organization and visualization. For this project, we want to design an user interface that take both usefulness and usability into consideration. Our system will be able to adapt to different types of user and display the crowds emerged in a specific period of time as well as the topics discussed by the crowd from Twitter. The interface should both optimize the user experience and system speed. For evaluation, we will design some user study or inspection procedures in order to test the efficiency, effectivness and satisfaction of this system to our poential users.
\end{abstract}

\category{H.5.1}{Information Interfaces and Presentation}{Multimedia
Information Systems}[video]
\category{H.5.3}{Group and Organization Interfaces}[collaborative computing, computer-supported cooperative work]
\category{H.5.4}{Hypertext/Hypermedia}[architecture]

\terms{Design, Experimentation, Human Factors}

\keywords{interface, crowd, twitter}

\section{Introduction}
Along with the rise of real-time social web, the power of information distribution is no longer limited to the small set of news media but the massive amount of ordinary individuals. Websites like Digg and Reddit provides a news aggregation platform that filter and display interesting news pieces recommended by other users; social media object sharing sites like Youtube and Flickr let users to upload and browse videos and images; microblogging systems, like Twitter and Buzz, enable every user to host a broadcasting station of their own; last but not least, Facebook with all the mentioned function available, allowing users to build their own online social network and share their everyday experience with their friends. Thus, the need for services that exploit these massive data is increasing. People are looking for a new generation of applications for monitoring, analyzing, and distilling information from the prospective web of real-time content that reflects the current activity of the web's participants. The shift toward fresh web content can be seen in the growing interest in mining large-scale social media for information discovery and brand management, for intelligence analysis by the government and state media, and in identifying and disseminating disaster and emergency-related information.

Comparing with the traditional web information applications that apply expensive off-line analysis of web data, the new generation of real-time web applications must be able to consume, process and display the massive amounts of data on-the-fly. In this project, we look particular into twitter, a microblogging system, platform. We want to provide users a manageable exploratory interface that display the crowds and their associated participants/content at each time period. The term ``Crowd'' refers to the emerging hotspots on the real-time web. Unlike long-lived communities or groups, a crowd is intended to reflect a potentially short-lived ad-hoc collection of users. In twitter, there are potentially 100s of millions of active users inserting new messages into the system at a high-rate. With existing algorithm and architecture built by our lab in the backend, our goal is to reveal the ad-hoc crowds of users that reflect the real-time interests and highly-temporal group affiliations in a clear and manageable fashion.

Even though our current data is from Twitter, we expect the system to be useful to users who are not familiar with twitter. In fact, our system can be of useful to several types of users with different purpose in mind.

\subsubsection{How Might We Help}
Apart from the original twitter interface that provides only a local view of the most current tweets issued by each user's followee or some local trending topics, our final system should be able to aggregate the data to find global, regional, and local phenomenons. The final product is also adjustable that fit into different expertise and purpose of usage based on the role of the users.

\subsection{Conceptual Model}
The conceptual model of our system is a tool for finding patterns, trends, and communities. The interface displays groups of people who are talking with each other, puts their conversation on a map, and finds important words in the conversation. Users will expect different types of filtering option such as filtering by area(geo-feature), by time(timeline snapshot), by keyword(free-text, hashtag) or by the expecting property of the crowds(the longest living crowd, the most engaging crowd). The default view of the system is a set of global crowd discovered recently.

\subsection{User}
To better design our system interface, we want to understand our potential users. For different kinds of users, there exhibits different patterns of properties like the frequency of usage, the level of experience, the behavior tendency and the tuning options availability.
\begin{itemize}
	\item Analyst: Government or media analyst are experts in information trending and market research. They use the system regularly with the frequency between once per day to once per month depending on the urgency of the monitoring task itself. They would like to have customized interface that is able to make variety of filtering on the fly. They will most likely mine the data using our system and edit the report at the same time.

	\item Twitter Users: Twitter users who is already have familiarity with the Twitter world could have interest in using our system to know about crowds and hot-topics. The may use it regularly or occasionally. They adopt our system to assist their twittering experience. They might not devote a big amount of time and effort but just want a quick and fresh view of the current trend. For this purpose, we should provide a simple and personalized content display with some easy filtering options.

	\item Regular People: regular users with no Twitter experience would use our system as a window to gain some quick idea to what happened currently in the Twitter world. To satisfy their curiosity without personalized history to learn from, we provide a global trend as the first look. Ideally, the users will come back and build a history profile so we can customize the display in a long run. people could use it just once or , if they like the system, several times per day.

	\item Business People - corporate people is particularly interested in their own product or company. Like the analysts, they are asked to perform the trending survey in a regular basis. They are trained in finding information related to their product. They use our system to find the opinion from the general users. They also study their competitors in a hope to improve their own. For this type of user, we can do highly customized interface to pre-filter the crowds to display. We may also prepare a set of template so the business people with no computer science knowledge can easily drag-and-drop views related to their competitors and their own side by side.

\end{itemize}

\subsection{Cognitive Issue}
Some cognitive issues we need to consider including the other activities our users might be engaging in simultaneously. For example, the twitter user might be browsing twitter and plan to use our system to understand the crowds that talk about a certain keyword of interest. Another situation can be finding some interesting topics while playing with our system and decide to do search to read the related news article from Google or NY Times. Or, our users may discover an exciting crowd/topic and eager to share this discovery to his friends on the social websites(Twitter, Facebook, etc). That is to say, we does not expect our user to keep 100\% focus on interacting with the system. We need to provide mechanisms for tip reminding of behavior history.

In addition, with the nature of the temporal massive data, we do not expect our users to remember where to find the crowd/topic of interest that the user just encountered. We want to provide a Workspace panel so to release the stress on the memory requirment from the user.

\section{Related Work}

\section{Interface Design}

\begin{figure*}[t]
\centering
\includegraphics[width=400pt]{img/UIdesign.eps}
\caption{Crowdy User Interface Design}
\label{fig:UIdesign}
\end{figure*}

Figure \ref{fig:UIdesign} shows an outline of the prototype. We want to provide the user with a simple and flexible interface to maximize the exploring experience while minimize the memorizing overhead. Existing web applications show that the most general task should be the main focus and the other available options may be placed on the side or hidden according to their frequency of usage. Recall the primary function of our system is to visualize the Crowds emerged over time, thus, the crowd displaying window comes as our first priority panel for displaying. In the crowd displaying window, we further consider the needs of personalization for our potential users(e.g. Analyst). There is a Global View Panel and a personal workspace panel. The Personal Workspace Panel distinguishes from the Global View Panel in a way that it only shows the set of crowds marked by the user when exploring in the Global View Panel. To help our users quickly and easily transit between these two views, tabbing function is used. Inside each view, we need to decide the format of showing massive amount of timestamp attached crowds which has several metadata associated with it such as starting/ending time, crowd participants, tweets, location data, etc. To effectively organize these properties to assist quick and convenient retrieval by the user, we consider these two formats: timeline and list. For both view panel, these two formats are included but sized unequally. The size is adjustable(in the option panel) according to the user's need. Generally, ``timeline'' is more suitable for overview a larger amount of data while ``list'' is better for detail skimming in a smaller crowd set. We also provide several filtering option for both timeline and list format in the option panel. Some detail component in these three panel are list below.

\begin{itemize}
	\item \textit{Global View Panel} : The global view shows the global crowds in different format. When a crowded is marked by the user, a flag will be placed in front of each crowd item in each format.

			\begin{itemize}
				\item Timeline format displays the evolution of each crowd. First of all, a crowd is shown as a line from the starting time to the ending time. The size of the participants over time is indicated by color(e.g., small-large-medium $\longrightarrow$ green-red-blue). Top three keywords that describe the topic of the crowd is displayed explicitly on the timeline along with the crowd line. Extra information about the crowd can be viewed in the pop up box when the user clicks on the crowd line.
				\item List format displays each crowd with some specific sorting order. The default sorting order is by the starting time. Some other available sorting function including the ending time, the size of crowds and the ranging time. In the list format, crowds are displayed explicitly in three columns: time period, keywords and some of the participants. The latter two columns are clickable. After clicked, it will show the list of tweets and the full set of participants in a pop up window form. 
		\end{itemize}

	\item \textit{Personal Workspace Panel} : Similar as the Global View Panel but with only the set of crowds marked by the user in the Global View Panel.
	\item \textit{Filter Option Panel} : This panel explicitly display a set of most frequent used filtering options such as search and timeline scaling bar. We also provide the user with flexibility to adjust the default settings we provided such as the primary displaying format in the View Panel, list sorting function and time period filtering. Other filtering option is hidden and can be expanded when click on the right bottom corner of the Panel.
\end{itemize}

\section{Implementation}

\section{Evaluation}

\section{CONCLUSIONS}

\section{FUTURE WORK}

\bibliographystyle{abbrv}
\bibliography{reference} 
\end{document}

### 2011-03-01 docs/crowdy_gui.tex
wraped lines in crowdy_gui.tex to 80 characters
merged related work and reference section

@@
 \numberofauthors{1} 
-\author{\alignauthor Jeffrey McGee, Zhiyuan Cheng, Chiao-Fang Hsu, Pratheek Kumar Akireddy \\
-\affaddr{Department of Computer Science and Engineering, Texas A\&M University} \\ \affaddr{ College Station, TX 77845 USA} \\
-\email{jeffamcgee@gmail.com, chengzhy@gmail.com, drakihsu@cse.tamu.edu, pka293@cse.tamu.edu}
+\author{
+    \alignauthor Jeffrey McGee, Zhiyuan Cheng, Chiao-Fang Hsu, Pratheek
+    Kumar Akireddy \\
+    \affaddr{Department of Computer Science and Engineering, Texas A\&M
+    University} \\
+    \affaddr{ College Station, TX 77845 USA} \\
+    \email{jeffamcgee@gmail.com, chengzhy@gmail.com, drakihsu@cse.tamu.edu,
+    pka293@cse.tamu.edu}
 }
@@
 \begin{abstract}
-Microblogging systems has provided the society with a more transparent channel for information distribution.
-Each individuals are empowered to spread the news and build their social networks.
-With the freedom of information generation, the issue now is the ``useful information'' identification, organization and visualization.
-For this project, we want to design an user interface that take both usefulness and usability into consideration.
-Our system will be able to adapt to different types of user and display the crowds emerged in a specific period of time as well as the topics discussed by the crowd from Twitter.
-The interface should both optimize the user experience and system speed.
-For evaluation, we will design some user study or inspection procedures in order to test the efficiency, effectivness and satisfaction of this system to our poential users.
+Microblogging systems has provided the society with a more transparent channel
+for information distribution. Each individuals are empowered to spread the news
+and build their social networks. With the freedom of information generation,
+the issue now is the ``useful information'' identification, organization and
+visualization. For this project, we want to design an user interface that take
+both usefulness and usability into consideration. Our system will be able to
+adapt to different types of user and display the crowds emerged in a specific
+period of time as well as the topics discussed by the crowd from Twitter. The
+interface should both optimize the user experience and system speed. For
+evaluation, we will design some user study or inspection procedures in order to
+test the efficiency, effectivness and satisfaction of this system to our
+poential users.
 \end{abstract}
@@
 Information Systems}[video]
-\category{H.5.3}{Group and Organization Interfaces}[collaborative computing, computer-supported cooperative work]
+\category{H.5.3}{Group and Organization Interfaces}[collaborative computing,
+computer-supported cooperative work]
 \category{H.5.4}{Hypertext/Hypermedia}[architecture]
@@
 \section{Introduction}
-Along with the rise of real-time social web, the power of information distribution is no longer limited to the small set of news media but the massive amount of ordinary individuals.
-Websites like Digg and Reddit provides a news aggregation platform that filter and display interesting news pieces recommended by other users; social media object sharing sites like Youtube and Flickr let users to upload and browse videos and images; microblogging systems, like Twitter and Buzz, enable every user to host a broadcasting station of their own; last but not least, Facebook with all the mentioned function available, allowing users to build their own online social network and share their everyday experience with their friends.
-Thus, the need for services that exploit these massive data is increasing.
-People are looking for a new generation of applications for monitoring, analyzing, and distilling information from the prospective web of real-time content that reflects the current activity of the web's participants.
-The shift toward fresh web content can be seen in the growing interest in mining large-scale social media for information discovery and brand management, for intelligence analysis by the government and state media, and in identifying and disseminating disaster and emergency-related information.
+Along with the rise of real-time social web, the power of information
+distribution is no longer limited to the small set of news media but the
+massive amount of ordinary individuals. Websites like Digg and Reddit provides
+a news aggregation platform that filter and display interesting news pieces
+recommended by other users; social media object sharing sites like Youtube and
+Flickr let users to upload and browse videos and images; microblogging systems,
+like Twitter and Buzz, enable every user to host a broadcasting station of
+their own; last but not least, Facebook with all the mentioned function
+available, allowing users to build their own online social network and share
+their everyday experience with their friends. Thus, the need for services that
+exploit these massive data is increasing. People are looking for a new
+generation of applications for monitoring, analyzing, and distilling
+information from the prospective web of real-time content that reflects the
+current activity of the web's participants. The shift toward fresh web content
+can be seen in the growing interest in mining large-scale social media for
+information discovery and brand management, for intelligence analysis by the
+government and state media, and in identifying and disseminating disaster and
+emergency-related information.
 
-Comparing with the traditional web information applications that apply expensive off-line analysis of web data, the new generation of real-time web applications must be able to consume, process and display the massive amounts of data on-the-fly.
-In this project, we look particular into twitter, a microblogging system, platform.
-We want to provide users a manageable exploratory interface that display the crowds and their associated participants/content at each time period.
-The term ``Crowd'' refers to the emerging hotspots on the real-time web.
-Unlike long-lived communities or groups, a crowd is intended to reflect a potentially short-lived ad-hoc collection of users.
-In twitter, there are potentially 100s of millions of active users inserting new messages into the system at a high-rate.
-With existing algorithm and architecture built by our lab in the backend, our goal is to reveal the ad-hoc crowds of users that reflect the real-time interests and highly-temporal group affiliations in a clear and manageable fashion.
+Comparing with the traditional web information applications that apply
+expensive off-line analysis of web data, the new generation of real-time web
+applications must be able to consume, process and display the massive amounts
+of data on-the-fly. In this project, we look particular into twitter, a
+microblogging system, platform. We want to provide users a manageable
+exploratory interface that display the crowds and their associated
+participants/content at each time period. The term ``Crowd'' refers to the
+emerging hotspots on the real-time web. Unlike long-lived communities or
+groups, a crowd is intended to reflect a potentially short-lived ad-hoc
+collection of users. In twitter, there are potentially 100s of millions of
+active users inserting new messages into the system at a high-rate. With
+existing algorithm and architecture built by our lab in the backend, our goal
+is to reveal the ad-hoc crowds of users that reflect the real-time interests
+and highly-temporal group affiliations in a clear and manageable fashion.
 
-Even though our current data is from Twitter, we expect the system to be useful to users who are not familiar with twitter.
-In fact, our system can be of useful to several types of users with different purpose in mind.
+Even though our current data is from Twitter, we expect the system to be useful
+to users who are not familiar with twitter. In fact, our system can be of
+useful to several types of users with different purpose in mind.
 
 \subsubsection{How Might We Help}
-Apart from the original twitter interface that provides only a local view of the most current tweets issued by each user's followee or some local trending topics, our final system should be able to aggregate the data to find global, regional, and local phenomenons.
-The final product is also adjustable that fit into different expertise and purpose of usage based on the role of the users.
+Apart from the original twitter interface that provides only a local view of
+the most current tweets issued by each user's followee or some local trending
+topics, our final system should be able to aggregate the data to find global,
+regional, and local phenomenons. The final product is also adjustable that fit
+into different expertise and purpose of usage based on the role of the users.
 
 \subsection{Conceptual Model}
-The conceptual model of our system is a tool for finding patterns, trends, and communities.
-The interface displays groups of people who are talking with each other, puts their conversation on a map, and finds important words in the conversation.
-Users will expect different types of filtering option such as filtering by area(geo-feature), by time(timeline snapshot), by keyword(free-text, hashtag) or by the expecting property of the crowds(the longest living crowd, the most engaging crowd).
-The default view of the system is a set of global crowd discovered recently.
+The conceptual model of our system is a tool for finding patterns, trends, and
+communities. The interface displays groups of people who are talking with each
+other, puts their conversation on a map, and finds important words in the
+conversation. Users will expect different types of filtering option such as
+filtering by area(geo-feature), by time(timeline snapshot), by
+keyword(free-text, hashtag) or by the expecting property of the crowds(the
+longest living crowd, the most engaging crowd). The default view of the system
+is a set of global crowd discovered recently.
 
 \subsection{User}
-To better design our system interface, we want to understand our potential users.
-For different kinds of users, there exhibits different patterns of properties like the frequency of usage, the level of experience, the behavior tendency and the tuning options availability.
+To better design our system interface, we want to understand our potential
+users. For different kinds of users, there exhibits different patterns of
+properties like the frequency of usage, the level of experience, the behavior
+tendency and the tuning options availability.
 \begin{itemize}
-	\item Analyst: Government or media analyst are experts in information trending and market research.
-They use the system regularly with the frequency between once per day to once per month depending on the urgency of the monitoring task itself.
-They would like to have customized interface that is able to make variety of filtering on the fly.
-They will most likely mine the data using our system and edit the report at the same time.
+    \item Analyst: Government or media analyst are experts in information
+    trending and market research. They use the system regularly with the
+    frequency between once per day to once per month depending on the urgency
+    of the monitoring task itself. They would like to have customized interface
+    that is able to make variety of filtering on the fly. They will most likely
+    mine the data using our system and edit the report at the same time.
 
-	\item Twitter Users: Twitter users who is already have familiarity with the Twitter world could have interest in using our system to know about crowds and hot-topics.
-The may use it regularly or occasionally.
-They adopt our system to assist their twittering experience.
-They might not devote a big amount of time and effort but just want a quick and fresh view of the current trend.
-For this purpose, we should provide a simple and personalized content display with some easy filtering options.
+    \item Twitter Users: Twitter users who is already have familiarity with the
+    Twitter world could have interest in using our system to know about crowds
+    and hot-topics. The may use it regularly or occasionally. They adopt our
+    system to assist their twittering experience. They might not devote a big
+    amount of time and effort but just want a quick and fresh view of the
+    current trend. For this purpose, we should provide a simple and
+    personalized content display with some easy filtering options.
 
-	\item Regular People: regular users with no Twitter experience would use our system as a window to gain some quick idea to what happened currently in the Twitter world.
-To satisfy their curiosity without personalized history to learn from, we provide a global trend as the first look.
-Ideally, the users will come back and build a history profile so we can customize the display in a long run.
-people could use it just once or , if they like the system, several times per day.
+    \item Regular People: regular users with no Twitter experience would use
+    our system as a window to gain some quick idea to what happened currently
+    in the Twitter world. To satisfy their curiosity without personalized
+    history to learn from, we provide a global trend as the first look.
+    Ideally, the users will come back and build a history profile so we can
+    customize the display in a long run. people could use it just once or , if
+    they like the system, several times per day.
 
-	\item Business People - corporate people is particularly interested in their own product or company.
-Like the analysts, they are asked to perform the trending survey in a regular basis.
-They are trained in finding information related to their product.
-They use our system to find the opinion from the general users.
-They also study their competitors in a hope to improve their own.
-For this type of user, we can do highly customized interface to pre-filter the crowds to display.
-We may also prepare a set of template so the business people with no computer science knowledge can easily drag-and-drop views related to their competitors and their own side by side.
+    \item Business People - corporate people is particularly interested in
+    their own product or company. Like the analysts, they are asked to perform
+    the trending survey in a regular basis. They are trained in finding
+    information related to their product. They use our system to find the
+    opinion from the general users. They also study their competitors in a hope
+    to improve their own. For this type of user, we can do highly customized
+    interface to pre-filter the crowds to display. We may also prepare a set of
+    template so the business people with no computer science knowledge can
+    easily drag-and-drop views related to their competitors and their own side
+    by side.
 
@@
 \subsection{Cognitive Issue}
-Some cognitive issues we need to consider including the other activities our users might be engaging in simultaneously.
-For example, the twitter user might be browsing twitter and plan to use our system to understand the crowds that talk about a certain keyword of interest.
-Another situation can be finding some interesting topics while playing with our system and decide to do search to read the related news article from Google or NY Times.
-Or, our users may discover an exciting crowd/topic and eager to share this discovery to his friends on the social websites(Twitter, Facebook, etc).
-That is to say, we does not expect our user to keep 100\% focus on interacting with the system.
-We need to provide mechanisms for tip reminding of behavior history.
+Some cognitive issues we need to consider including the other activities our
+users might be engaging in simultaneously. For example, the twitter user might
+be browsing twitter and plan to use our system to understand the crowds that
+talk about a certain keyword of interest. Another situation can be finding some
+interesting topics while playing with our system and decide to do search to
+read the related news article from Google or NY Times. Or, our users may
+discover an exciting crowd/topic and eager to share this discovery to his
+friends on the social websites(Twitter, Facebook, etc). That is to say, we does
+not expect our user to keep 100\% focus on interacting with the system. We need
+to provide mechanisms for tip reminding of behavior history.
 
-In addition, with the nature of the temporal massive data, we do not expect our users to remember where to find the crowd/topic of interest that the user just encountered.
-We want to provide a Workspace panel so to release the stress on the memory requirment from the user.
+In addition, with the nature of the temporal massive data, we do not expect our
+users to remember where to find the crowd/topic of interest that the user just
+encountered. We want to provide a Workspace panel so to release the stress on
+the memory requirment from the user.
 
 \section{Related Work}
+Twitter is a microblogging platform which is fast gaining popularity
+among broad sections of society and has a global outreach spreading from
+developed, urban nations the likes of the United States where it has a high
+adoption rate\cite{akshayjava2009we}, to developing countries in parts of Asia
+and South America.
+
+Along with working on understanding microblogging usage and
+communities\cite{java2007we}, the main author - Akshay Java was one of the
+first few who dealt with the measurement of the usage and nature of communities
+in microblogging. In his latter study\cite{java2008mining}, he presented his
+observations of the microblogging phenomena and user intentions by studying the
+content, topological and geographical properties of such communities. He found
+that microblogging provides users with a more immediate form of communication
+to talk about their daily activities and to seek or share information.
+
+When it comes to visualization of the social crowd, a tool which in some ways
+shows similar objectives as us and stands out among the rest is
+Vizster\cite{heer2005vizster}. It is a visualization system for playful
+end-user exploration and navigation of large-scale online social networks. The
+design builds upon familiar node- link network layouts to contribute techniques
+for exploring connectivity in large graph structures, supporting visual search
+and analysis, and automatically identifying and visualizing community
+structures. The system facilitates a better discovery of people, connections,
+and communities to promote increased awareness of community structure and
+information exposure, while maintaining a fun and socially engaged online
+space. The creators of the tool were interested in crafting techniques for the
+situated exploration and visual analysis of large graph structures by a
+specific end-user population.
+
+Another related study was on how web-based retrieval from twitter can be used
+as knowledge base\cite{cheong2009integrating} which shows that the
+visualization system we try to attempt can be helpful. Marc Cheong et al. in
+this study tried to analyze demographics of the authors of Twitter messages and
+attempt to map a Twitter trend into what's going on in the real world. Their
+findings reveal a pattern behind trends on Twitter, and trying to evolve
+through visualization methods.  Their findings also enable us to understand the
+underlying characteristics behind the ``trend setters'', providing us a new
+perspective on the contributors of a trend.
+
+Identifying highly dynamic ad-hoc collections of users what we refer to as
+crowds in massive social messaging systems like Twitter and Facebook is
+important\cite{kamath2010identifying}. K. Y. Kamath et al. in the study have a
+salient feature of the proposed approach as an efficient locality-based
+clustering approach for identifying crowds of users in near real-time compared
+to more heavyweight static clustering algorithm. The study consisted of 711,612
+users and 61.3 million messages, which show how the proposed approach can
+efficiently and effectively identify Twitter-based crowds.
+
+In the other study based on the previous one, K. Y. Kamath et
+al\cite{kamath2011transient}, they add another salient feature - a novel crowd
+tracking and evolution approach for linking crowds across time periods. Unlike
+the more static and long-lived group-based membership offered on many social
+networks their goal is to support the discovery of organic and highly-temporal
+group affiliation, which they refer to as ``transient crowds''. A transient
+crowd according to them is a potentially short-lived ad-hoc collection of users
+bound together by some common thread – which can be communication-based,
+location-based or interest based. We are inspired by this idea of formation and
+detection of crowds. We try to implement detection of crowd in “crowdy” in a
+similar fashion.
 
@@
 
-Figure \ref{fig:UIdesign} shows an outline of the prototype.
-We want to provide the user with a simple and flexible interface to maximize the exploring experience while minimize the memorizing overhead.
-Existing web applications show that the most general task should be the main focus and the other available options may be placed on the side or hidden according to their frequency of usage.
-Recall the primary function of our system is to visualize the Crowds emerged over time, thus, the crowd displaying window comes as our first priority panel for displaying.
-In the crowd displaying window, we further consider the needs of personalization for our potential users(e.g.
-Analyst).
-There is a Global View Panel and a personal workspace panel.
-The Personal Workspace Panel distinguishes from the Global View Panel in a way that it only shows the set of crowds marked by the user when exploring in the Global View Panel.
-To help our users quickly and easily transit between these two views, tabbing function is used.
-Inside each view, we need to decide the format of showing massive amount of timestamp attached crowds which has several metadata associated with it such as starting/ending time, crowd participants, tweets, location data, etc.
-To effectively organize these properties to assist quick and convenient retrieval by the user, we consider these two formats: timeline and list.
-For both view panel, these two formats are included but sized unequally.
-The size is adjustable(in the option panel) according to the user's need.
-Generally, ``timeline'' is more suitable for overview a larger amount of data while ``list'' is better for detail skimming in a smaller crowd set.
-We also provide several filtering option for both timeline and list format in the option panel.
-Some detail component in these three panel are list below.
+Figure \ref{fig:UIdesign} shows an outline of the prototype. We want to provide
+the user with a simple and flexible interface to maximize the exploring
+experience while minimize the memorizing overhead. Existing web applications
+show that the most general task should be the main focus and the other
+available options may be placed on the side or hidden according to their
+frequency of usage. Recall the primary function of our system is to visualize
+the Crowds emerged over time, thus, the crowd displaying window comes as our
+first priority panel for displaying. In the crowd displaying window, we further
+consider the needs of personalization for our potential users(e.g. Analyst).
+There is a Global View Panel and a personal workspace panel. The Personal
+Workspace Panel distinguishes from the Global View Panel in a way that it only
+shows the set of crowds marked by the user when exploring in the Global View
+Panel. To help our users quickly and easily transit between these two views,
+tabbing function is used. Inside each view, we need to decide the format of
+showing massive amount of timestamp attached crowds which has several metadata
+associated with it such as starting/ending time, crowd participants, tweets,
+location data, etc. To effectively organize these properties to assist quick
+and convenient retrieval by the user, we consider these two formats: timeline
+and list. For both view panel, these two formats are included but sized
+unequally. The size is adjustable(in the option panel) according to the user's
+need. Generally, ``timeline'' is more suitable for overview a larger amount of
+data while ``list'' is better for detail skimming in a smaller crowd set. We
+also provide several filtering option for both timeline and list format in the
+option panel. Some detail component in these three panel are list below.
 
 \begin{itemize}
-	\item \textit{Global View Panel} : The global view shows the global crowds in different format. When a crowded is marked by the user, a flag will be placed in front of each crowd item in each format.
+    \item \textit{Global View Panel} : The global view shows the global crowds
+    in different format. When a crowded is marked by the user, a flag will be
+    placed in front of each crowd item in each format.
 
@@
         \item Timeline format displays the evolution of each crowd.
-First of all, a crowd is shown as a line from the starting time to the ending time.
-The size of the participants over time is indicated by color(e.g., small-large-medium $\longrightarrow$ green-red-blue).
-Top three keywords that describe the topic of the crowd is displayed explicitly on the timeline along with the crowd line.
-Extra information about the crowd can be viewed in the pop up box when the user clicks on the crowd line.
-				\item List format displays each crowd with some specific sorting order.
-The default sorting order is by the starting time.
-Some other available sorting function including the ending time, the size of crowds and the ranging time.
-In the list format, crowds are displayed explicitly in three columns: time period, keywords and some of the participants.
-The latter two columns are clickable.
-After clicked, it will show the list of tweets and the full set of participants in a pop up window form.
+        First of all, a crowd is shown as a line from the starting time
+        to the ending time. The size of the participants over time is
+        indicated by color(e.g., small-large-medium $\longrightarrow$
+        green-red-blue). Top three keywords that describe the topic of
+        the crowd is displayed explicitly on the timeline along with
+        the crowd line. Extra information about the crowd can be viewed
+        in the pop up box when the user clicks on the crowd line.
+        \item List format displays each crowd with some specific
+        sorting order. The default sorting order is by the starting
+        time. Some other available sorting function including the
+        ending time, the size of crowds and the ranging time. In the
+        list format, crowds are displayed explicitly in three columns:
+        time period, keywords and some of the participants. The latter
+        two columns are clickable. After clicked, it will show the list
+        of tweets and the full set of participants in a pop up window
+        form.
     \end{itemize}
 
-	\item \textit{Personal Workspace Panel} : Similar as the Global View Panel but with only the set of crowds marked by the user in the Global View Panel.
-	\item \textit{Filter Option Panel} : This panel explicitly display a set of most frequent used filtering options such as search and timeline scaling bar.
-We also provide the user with flexibility to adjust the default settings we provided such as the primary displaying format in the View Panel, list sorting function and time period filtering.
-Other filtering option is hidden and can be expanded when click on the right bottom corner of the Panel.
+    \item \textit{Personal Workspace Panel} : Similar as the Global View Panel
+    but with only the set of crowds marked by the user in the Global View
+    Panel.
+    \item \textit{Filter Option Panel} : This panel explicitly display a set of
+    most frequent used filtering options such as search and timeline scaling
+    bar. We also provide the user with flexibility to adjust the default
+    settings we provided such as the primary displaying format in the View
+    Panel, list sorting function and time period filtering. Other filtering
+    option is hidden and can be expanded when click on the right bottom corner
+    of the Panel.
 \end{itemize}

### 2011-03-01 docs/crowdy_gui.tex
massive copyediting

@@
 \begin{abstract}
-Microblogging systems has provided the society with a more transparent channel
-for information distribution. Each individuals are empowered to spread the news
+Microblogging systems have provided society with a more transparent channel
+for information distribution. Each individual is empowered to spread news
 and build their social networks. With the freedom of information generation,
-the issue now is the ``useful information'' identification, organization and
-visualization. For this project, we want to design an user interface that take
-both usefulness and usability into consideration. Our system will be able to
-adapt to different types of user and display the crowds emerged in a specific
+the issue now is identifiying, organizing, visualizing useful information.
+For this project, we want to design an user interface that takes
+both usefulness and usability into consideration. Our system will
+adapt to different types of users and display the crowds that form in a specific
 period of time as well as the topics discussed by the crowd from Twitter. The
@@
 evaluation, we will design some user study or inspection procedures in order to
-test the efficiency, effectivness and satisfaction of this system to our
+test the efficiency, effectivness, and satisfaction of this system to our
 poential users.
@@
 
-\keywords{interface, crowd, twitter}
+\keywords{interface, crowd, Twitter}
 
@@
 distribution is no longer limited to the small set of news media but the
-massive amount of ordinary individuals. Websites like Digg and Reddit provides
+massive amount of ordinary individuals. Websites like Digg and Reddit provide
 a news aggregation platform that filter and display interesting news pieces
 recommended by other users; social media object sharing sites like Youtube and
-Flickr let users to upload and browse videos and images; microblogging systems,
+Flickr let users upload and browse videos and images; microblogging systems,
 like Twitter and Buzz, enable every user to host a broadcasting station of
-their own; last but not least, Facebook with all the mentioned function
-available, allowing users to build their own online social network and share
-their everyday experience with their friends. Thus, the need for services that
-exploit these massive data is increasing. People are looking for a new
+their own; last but not least, Facebook allows users to build their own
+social network and share their everyday experience with their friends.
+Thus, there is a demand for services that
+exploit these massive sources of data. People are looking for a new
 generation of applications for monitoring, analyzing, and distilling
@@
 applications must be able to consume, process and display the massive amounts
-of data on-the-fly. In this project, we look particular into twitter, a
-microblogging system, platform. We want to provide users a manageable
-exploratory interface that display the crowds and their associated
-participants/content at each time period. The term ``Crowd'' refers to the
-emerging hotspots on the real-time web. Unlike long-lived communities or
-groups, a crowd is intended to reflect a potentially short-lived ad-hoc
-collection of users. In twitter, there are potentially 100s of millions of
-active users inserting new messages into the system at a high-rate. With
+of data on-the-fly. In this project, we look particular into Twitter, a
+microblogging platform. We want to provide users a manageable
+exploratory interface that displays the crowds and their associated
+participants/content at each time period.  We define a ``crowd'' to be a
+potentially short-lived ad-hoc collection of users.  There are several ways to
+identify crowds: users who message each other, users who are nearby, and users
+who use similar terms. In Twitter, there are potentially 100s of millions of
+active users inserting new messages into the system at a high rate. With
 existing algorithm and architecture built by our lab in the backend, our goal
@@
 Even though our current data is from Twitter, we expect the system to be useful
-to users who are not familiar with twitter. In fact, our system can be of
+to users who are not familiar with Twitter. In fact, our system can be of
 useful to several types of users with different purpose in mind.
@@
 \subsubsection{How Might We Help}
-Apart from the original twitter interface that provides only a local view of
+Apart from the original Twitter interface that provides only a local view of
 the most current tweets issued by each user's followee or some local trending
@@
 other, puts their conversation on a map, and finds important words in the
-conversation. Users will expect different types of filtering option such as
+conversation. Users will expect different types of filtering options such as
 filtering by area(geo-feature), by time(timeline snapshot), by
@@
 longest living crowd, the most engaging crowd). The default view of the system
-is a set of global crowd discovered recently.
+is a set of global crowds discovered recently.
 
@@
     frequency between once per day to once per month depending on the urgency
-    of the monitoring task itself. They would like to have customized interface
-    that is able to make variety of filtering on the fly. They will most likely
-    mine the data using our system and edit the report at the same time.
+    of the monitoring task itself. They would like to have a customized interface
+    that is able to apply a variety of filters on the fly. While they are 
+    investigating the data using our system, they are likely to be writing a
+    report.
 
-    \item Twitter Users: Twitter users who is already have familiarity with the
-    Twitter world could have interest in using our system to know about crowds
+    \item Twitter Users: Twitter users who already have familiarity with the
+    Twitter world can use our system to learn about crowds
     and hot-topics. The may use it regularly or occasionally. They adopt our
-    system to assist their twittering experience. They might not devote a big
+    system to assist their twittering experience. They might not devote a large
     amount of time and effort but just want a quick and fresh view of the
@@
 
-    \item Regular People: regular users with no Twitter experience would use
-    our system as a window to gain some quick idea to what happened currently
+    \item Regular People: regular users with no Twitter experience will use
+    our system as a window to gain an idea of what is currently happening
     in the Twitter world. To satisfy their curiosity without personalized
@@
     Ideally, the users will come back and build a history profile so we can
-    customize the display in a long run. people could use it just once or , if
+    customize the display in a long run. people could use it just once or, if
     they like the system, several times per day.
 
-    \item Business People - corporate people is particularly interested in
+    \item Business People - corporate employees are particularly interested in
     their own product or company. Like the analysts, they are asked to perform
@@
     interface to pre-filter the crowds to display. We may also prepare a set of
-    template so the business people with no computer science knowledge can
-    easily drag-and-drop views related to their competitors and their own side
-    by side.
+    templates so the business people with no computer science knowledge can
+    easily drag-and-drop views related to their competitors and their own
+    business side by side.
 
@@
 \subsection{Cognitive Issue}
-Some cognitive issues we need to consider including the other activities our
-users might be engaging in simultaneously. For example, the twitter user might
-be browsing twitter and plan to use our system to understand the crowds that
+Some cognitive issues we need to consider include the other activities our
+users might be engaging in simultaneously. For example, the Twitter user might
+be browsing Twitter and plan to use our system to understand the crowds that
 talk about a certain keyword of interest. Another situation can be finding some
@@
 \section{Related Work}
-Twitter is a microblogging platform which is fast gaining popularity
-among broad sections of society and has a global outreach spreading from
-developed, urban nations the likes of the United States where it has a high
-adoption rate\cite{akshayjava2009we}, to developing countries in parts of Asia
-and South America.
-
-Along with working on understanding microblogging usage and
+There has been some work into understanding how communities of users interact
+on social networks. Along with working on understanding microblogging usage and
 communities\cite{java2007we}, the main author - Akshay Java was one of the
@@
 
-When it comes to visualization of the social crowd, a tool which in some ways
-shows similar objectives as us and stands out among the rest is
+When it comes to visualization of social crowds, a tool which has
+similar objectives to ours is
 Vizster\cite{heer2005vizster}. It is a visualization system for playful
 end-user exploration and navigation of large-scale online social networks. The
-design builds upon familiar node- link network layouts to contribute techniques
+design builds upon familiar node-link network layouts to contribute techniques
 for exploring connectivity in large graph structures, supporting visual search
 and analysis, and automatically identifying and visualizing community
-structures. The system facilitates a better discovery of people, connections,
+structures. The system facilitates discovery of people, connections,
 and communities to promote increased awareness of community structure and
@@
 
-Another related study was on how web-based retrieval from twitter can be used
+Another related study was on how web-based retrieval from Twitter can be used
 as knowledge base\cite{cheong2009integrating} which shows that the
@@
 Figure \ref{fig:UIdesign} shows an outline of the prototype. We want to provide
-the user with a simple and flexible interface to maximize the exploring
-experience while minimize the memorizing overhead. Existing web applications
+the user with a simple and flexible interface to maximize their options for
+exploring while minimizing their memory overhead. Existing web applications
 show that the most general task should be the main focus and the other
 available options may be placed on the side or hidden according to their
-frequency of usage. Recall the primary function of our system is to visualize
-the Crowds emerged over time, thus, the crowd displaying window comes as our
-first priority panel for displaying. In the crowd displaying window, we further
+frequency of usage. Since the primary function of our system is to visualize
+the Crowds emerged over time, the crowd display window is our
+first priority. In the crowd display window, we
 consider the needs of personalization for our potential users(e.g. Analyst).
-There is a Global View Panel and a personal workspace panel. The Personal
-Workspace Panel distinguishes from the Global View Panel in a way that it only
-shows the set of crowds marked by the user when exploring in the Global View
-Panel. To help our users quickly and easily transit between these two views,
-tabbing function is used. Inside each view, we need to decide the format of
-showing massive amount of timestamp attached crowds which has several metadata
-associated with it such as starting/ending time, crowd participants, tweets,
+There is a global view panel and a personal workspace panel. The personal
+workspace panel distinguishes from the global view panel in a way that it only
+shows the set of crowds marked by the user when exploring in the global view
+panel. We have tabs to help our users quickly and easily transit between these
+two views. Inside each view, we need to decide the best format to condense
+a massive amount of data. Each crowd has metadata associated with it such as
+starting and ending time, crowd participants, topics, tweets,
 location data, etc. To effectively organize these properties to assist quick
 and convenient retrieval by the user, we consider these two formats: timeline
-and list. For both view panel, these two formats are included but sized
+and list. For both view panels, these two formats are included but sized
 unequally. The size is adjustable(in the option panel) according to the user's
-need. Generally, ``timeline'' is more suitable for overview a larger amount of
-data while ``list'' is better for detail skimming in a smaller crowd set. We
-also provide several filtering option for both timeline and list format in the
-option panel. Some detail component in these three panel are list below.
+need. Generally, ``timeline'' is more suitable for overview a large number of
+crowds while ``list'' is better for investigating details in a smaller set of crowds. We
+also provide several filtering options for both timeline and list format in the
+option panel. Some detailed components in these three panels are listed below.
 
@@
         indicated by color(e.g., small-large-medium $\longrightarrow$
-        green-red-blue). Top three keywords that describe the topic of
-        the crowd is displayed explicitly on the timeline along with
+        green-red-blue). The top three keywords that describe the topic of
+        the crowd are displayed explicitly on the timeline along with
         the crowd line. Extra information about the crowd can be viewed
@@
         sorting order. The default sorting order is by the starting
-        time. Some other available sorting function including the
+        time. Some other available sorting functions include the
         ending time, the size of crowds and the ranging time. In the
@@
     Panel.
-    \item \textit{Filter Option Panel} : This panel explicitly display a set of
-    most frequent used filtering options such as search and timeline scaling
-    bar. We also provide the user with flexibility to adjust the default
-    settings we provided such as the primary displaying format in the View
+    \item \textit{Filter Option Panel} : This panel explicitly displays a set of
+    the most frequently used filtering options such as search and timeline scaling.
+    We also provide the user with flexibility to adjust the default
+    settings we provided such as the primary display format in the View
     Panel, list sorting function and time period filtering. Other filtering
-    option is hidden and can be expanded when click on the right bottom corner
+    options are hidden and can be expanded with a click on the right bottom corner
     of the Panel.

### 2011-03-01 docs/crowdy_gui.tex
Merged some changes from Zhiyuan
did spellchecking and started implementation

@@
 
-\begin{document}
+\pdfpagewidth 8.5in
+\pdfpageheight 11in
 
@@
     \affaddr{ College Station, TX 77845 USA} \\
-    \email{jeffamcgee@gmail.com, chengzhy@gmail.com, drakihsu@cse.tamu.edu,
+    \email{jeffamcgee@gmail.com, zcheng@cse.tamu.edu, drakihsu@cse.tamu.edu,
     pka293@cse.tamu.edu}
 } 
+\begin{document}
 
@@
 for information distribution. Each individual is empowered to spread news
-and build their social networks. With the freedom of information generation,
-the issue now is identifiying, organizing, visualizing useful information.
+and build their social network. With the freedom of information generation,
+the issue now is identifying, organizing, and visualizing useful information.
 For this project, we want to design an user interface that takes
@@
 interface should both optimize the user experience and system speed. For
-evaluation, we will design some user study or inspection procedures in order to
-test the efficiency, effectivness, and satisfaction of this system to our
-poential users.
+evaluation, we will design a user study to
+test the efficiency, effectiveness, and satisfaction of this system to our
+potential users.
 \end{abstract}
@@
 encountered. We want to provide a Workspace panel so to release the stress on
-the memory requirment from the user.
+the memory requirement from the user.
 
@@
 location-based or interest based. We are inspired by this idea of formation and
-detection of crowds. We try to implement detection of crowd in “crowdy” in a
+detection of crowds. We try to implement detection of crowd in “Crowdy” in a
 similar fashion.
@@
 \section{Implementation}
+The system is designed to run in a user's web browser.
+As a result, we choose to use some fairly standard web tools to implement the system.
+The system that we are building the user interface on top of exposes a RESTful API.
+To retrieve data, our system makes an HTTP GET request to the server.
+The server returns data in the JSON format, which is easy to decode in Javascript.
+
+CherryPy
+Jinja
+
+jQuery
+Simile Timeline
+Google Maps API
 

### 2011-03-01 docs/crowdy_gui.tex
added implementation

@@
 location-based or interest based. We are inspired by this idea of formation and
-detection of crowds. We try to implement detection of crowd in “Crowdy” in a
+detection of crowds. We try to implement detection of crowd in ``Crowdy'' in a
 similar fashion.
@@
 \section{Implementation}
-The system is designed to run in a user's web browser.
-As a result, we choose to use some fairly standard web tools to implement the system.
-The system that we are building the user interface on top of exposes a RESTful API.
-To retrieve data, our system makes an HTTP GET request to the server.
-The server returns data in the JSON format, which is easy to decode in Javascript.
+The system is designed to run in a user's web browser.  As a result, we decided
+to use some fairly standard web tools to implement the system.  The system that
+we are building the user interface on top of exposes a RESTful API.  To
+retrieve data, our system makes an HTTP GET request to the server.  The server
+returns data in the JSON format, which is easy to decode in Javascript.
 
-CherryPy
-Jinja
+We are writing the portion of the web application that runs on the server in
+python, since that is what our team has the most experience with.  We chose the
+CherryPy framework to build the application because it is simple and lets us
+write testable code.  We are using the Jinja templating engine to generate the
+HTML pages.
 
-jQuery
-Simile Timeline
-Google Maps API
+The code that will run on the user's web browser has to be written in
+Javascript.  We use the jQuery library to handle events, retrieve JSON, and
+abstract away the idiosyncrasies of the various web browsers.  We are using the
+Simile Timeline library to produce the crowd timelines.  In the future, we may
+use the Google Maps API to display crowds on a map.
 

### 2011-03-01 docs/crowdy_gui.tex
merged new related work, minor edits

@@
 
-\section{Related Work}
-There has been some work into understanding how communities of users interact
-on social networks. Along with working on understanding microblogging usage and
-communities\cite{java2007we}, the main author - Akshay Java was one of the
-first few who dealt with the measurement of the usage and nature of communities
-in microblogging. In his latter study\cite{java2008mining}, he presented his
-observations of the microblogging phenomena and user intentions by studying the
-content, topological and geographical properties of such communities. He found
-that microblogging provides users with a more immediate form of communication
-to talk about their daily activities and to seek or share information.
-
-When it comes to visualization of social crowds, a tool which has
-similar objectives to ours is
-Vizster\cite{heer2005vizster}. It is a visualization system for playful
-end-user exploration and navigation of large-scale online social networks. The
-design builds upon familiar node-link network layouts to contribute techniques
-for exploring connectivity in large graph structures, supporting visual search
-and analysis, and automatically identifying and visualizing community
-structures. The system facilitates discovery of people, connections,
-and communities to promote increased awareness of community structure and
-information exposure, while maintaining a fun and socially engaged online
-space. The creators of the tool were interested in crafting techniques for the
-situated exploration and visual analysis of large graph structures by a
-specific end-user population.
-
-Another related study was on how web-based retrieval from Twitter can be used
-as knowledge base\cite{cheong2009integrating} which shows that the
-visualization system we try to attempt can be helpful. Marc Cheong et al. in
-this study tried to analyze demographics of the authors of Twitter messages and
-attempt to map a Twitter trend into what's going on in the real world. Their
-findings reveal a pattern behind trends on Twitter, and trying to evolve
-through visualization methods.  Their findings also enable us to understand the
-underlying characteristics behind the ``trend setters'', providing us a new
-perspective on the contributors of a trend.
-
-Identifying highly dynamic ad-hoc collections of users what we refer to as
-crowds in massive social messaging systems like Twitter and Facebook is
-important\cite{kamath2010identifying}. K. Y. Kamath et al. in the study have a
-salient feature of the proposed approach as an efficient locality-based
-clustering approach for identifying crowds of users in near real-time compared
-to more heavyweight static clustering algorithm. The study consisted of 711,612
-users and 61.3 million messages, which show how the proposed approach can
-efficiently and effectively identify Twitter-based crowds.
-
-In the other study based on the previous one, K. Y. Kamath et
-al\cite{kamath2011transient}, they add another salient feature - a novel crowd
-tracking and evolution approach for linking crowds across time periods. Unlike
-the more static and long-lived group-based membership offered on many social
-networks their goal is to support the discovery of organic and highly-temporal
-group affiliation, which they refer to as ``transient crowds''. A transient
-crowd according to them is a potentially short-lived ad-hoc collection of users
-bound together by some common thread – which can be communication-based,
-location-based or interest based. We are inspired by this idea of formation and
-detection of crowds. We try to implement detection of crowd in ``Crowdy'' in a
-similar fashion.
-
-\section{Interface Design}
-
 \begin{figure*}[t]
@@
 \end{figure*}
+
+\section{Related Work}
+Twitter\footnote{http://www.twitter.com} is a microblogging platform which is
+fast gaining popularity\cite{Oreilly:2009} among broad sections of society and
+has a global outreach spreading from developed, urban nations like the United
+States where it has a high adoption rate \cite{Java:2007}, to developing
+countries in parts of Asia and South America.
+
+Along with working on understanding microblogging usage and communities
+\cite{Java:2007}, the main author - Akshay Java was one of the first few who
+dealt with the measurement of the usage and nature of communities in
+microblogging. In his latter study \cite{Java:2008}, he presented his
+observations of the microblogging phenomena and user intentions by studying the
+content, topological and geographical properties of such communities. He found
+that microblogging provides users with a more immediate form of communication
+to talk about their daily activities and to seek or share information.
+
+When it comes to visualization of the social crowd, a tool which in some ways
+shows similar objectives as us and stands out among the rest is Vizster
+\cite{Heer:2005}. It is a visualization system for which can be used for
+exploration and navigation of the social networks of any scale. The system
+provides facilities to improve the functionalities like discovering people or
+connections which can help in promoting awareness of community structure and
+exposure to information. It maintains a fun element to it while providing these
+given features. It was aimed to provide specific end-users, functionalities
+like situated exploration and visual analysis of big-scale communities. It is
+based on a design of network layouts which have features like supporting visual
+search and analysis, exploring connectivity in large graphs and automatic
+identification and visualization of structures of communities.
+
+Another related study was on how web-based retrieval from twitter can be used
+as knowledge base \cite{Cheong:2009} which shows that the visualization system
+we try to attempt can be helpful. Marc Cheong et al. in this study tried to
+analyze demographics of the Twitter users and attempted to provide and analyze
+the trend in Twitter into what's going on in the real world. They enabled us to
+understand the underlying characteristics behind the trend setting in Twitter
+and thereby providing a new perspective on the contributors of a trend. They
+used visualization techniques along with artificial intelligence-based data
+mining methods to classify the Twitter messages dealing with the trend topic.
+
+Identifying highly dynamic ad-hoc collections of users what we refer to as
+crowds in massive social messaging systems like Twitter and Facebook is
+important \cite{krishna:2010}. K. Y. Kamath et al. in the study suggest an
+efficient locality-based clustering approach for identifying crowds of users in
+near real-time compared to more heavyweight static clustering algorithm. The
+study consisted of 711,612 users and 61.3 million messages, and tells what
+approaches to follow to efficiently and effectively identify Twitter-based
+crowds.
+
+In the other study based on the previous one, K. Y. Kamath et al
+\cite{krishna:2011}, they add another salient feature - a novel crowd tracking
+and evolution approach for linking crowds across time periods. Unlike the more
+static and long-lived group-based membership offered on many social networks
+their goal was to support the discovery of organic and highly-temporal group
+affiliation, which they refer to as ``transient crowds''. A transient crowd
+according to them is a potentially short-lived ad-hoc collection of users bound
+together by some common thread – which can be communication-based,
+location-based or interest based. We are inspired by this idea of formation and
+detection of crowds. We try to implement detection of crowd in Crowdy in a
+similar fashion.
+
+\section{Interface Design}
 
@@
 to use some fairly standard web tools to implement the system.  The system that
-we are building the user interface on top of exposes a RESTful API.  To
-retrieve data, our system makes an HTTP GET request to the server.  The server
-returns data in the JSON format, which is easy to decode in Javascript.
+we are building the user interface on top of exposes a RESTful API.  Although
+it is not a part of this project, it is important to understand how the backend
+works, and how it fits into this project.  First, a crawler retrieves tweets
+from Twitter using Twitter's REST API, search API, and streaming API.  Next,
+this data goes through several filters that add additional information to the
+users and tweets.  After that, a program finds groups of users based on their
+communication patterns.  This data is stored as JSON in a MongoDB database.
+The backend also provides the RESTful API that we connect to.  To retrieve
+data, our system makes an HTTP GET request to the server.  The server returns
+data in the JSON format, which is easy to decode in Javascript.  Our GUI never
+directly reads from or writes to the database.
 
-We are writing the portion of the web application that runs on the server in
-python, since that is what our team has the most experience with.  We chose the
+We are writing the portion of our web application that runs on the server in
+Python, since that is what our team has the most experience with.  We chose the
 CherryPy framework to build the application because it is simple and lets us
-write testable code.  We are using the Jinja templating engine to generate the
-HTML pages.
+write modular, testable code.  We are using the Jinja templating engine to
+generate the HTML pages. This makes it easy to have a consistent look across
+all of our pages without duplicating code.
 

### 2011-03-26 etc/settings.py
moved default location of mongo_host to sarge

@@ -7,7 +7,7 @@ class SettingsBunch(dict):
         self[name] = value
 
 settings = SettingsBunch(
-    mongo_host = 'sid.csdl.tamu.edu',
+    mongo_host = 'sarge.csdl.tamu.edu',
     mongo_database = 'crowds',
     beanstalk_host = 'localhost',
     beanstalk_port = 11300,

### 2011-03-27 api/models.py
default dateformat is now epoch, hid datetimes from localcrawl

@@ -15,6 +15,9 @@ class TwitterModel(Model):
         if self._id is None and from_dict and 'id' in from_dict:
             self._id = from_dict['id']
 
+    def to_d(self, dateformat="epoch", **kwargs):
+        #change the default dateformat to epoch
+        return Model.to_d(self, dateformat=dateformat, **kwargs)
 
 class TwitterIdProperty(IntProperty):
     pass
@@ -35,7 +38,10 @@ class User(TwitterModel):
         'profile_sidebar_border_color', 'profile_sidebar_fill_color',
         'profile_text_color', 'profile_use_background_image',
         'show_all_inline_media', 'time_zone', 'status', 'notifications',
-        'id', 'id_str', 'is_translator'
+        'id', 'id_str', 'is_translator',
+        # ncd and lcd were added to work around differences between datetimes in
+        # localcrawl and crowdy. - Jeff
+        'ncd','lcd',
     ]
     
     #properties from twitter
@@ -85,14 +91,14 @@ class Tweet(TwitterModel):
             ats = from_dict['entities']['user_mentions']
             self.mentions = [at['id'] for at in ats ]
 
-class Edges(Model):
+class Edges(TwitterModel):
     # I only store the first 5000 friends and followers
     _id = TwitterIdProperty('_id')
     friends = ListProperty('frs',int)
     followers = ListProperty('fols',int)
 
 
-class Crowd(Model):
+class Crowd(TwitterModel):
     _id = TextProperty('_id')
     start = DateTimeProperty('start')
     end = DateTimeProperty('end')
@@ -103,7 +109,7 @@ class Crowd(Model):
     size = IntProperty('size')
 
     def simple(self):
-        crowd = self.to_d(dateformat="epoch")
+        crowd = self.to_d()
         del crowd['merge']
         del crowd['split']
         crowd['users'] = [u['id'] for u in crowd['users']]

### 2011-03-28 api/crowd.py
addded crowd/users and crowd/tweets to api, fixed bug in maroon

@@ -1,6 +1,6 @@
 import cherrypy
 from cherrypy import tools
-from api.models import Crowd
+from api.models import Crowd,User,Tweet,Edges
 from utils import get_or_404
 
 @cherrypy.expose
@@ -15,3 +15,20 @@ def simple(cid):
     """returns a crowd, after removing information about when users leave
     and join plus when crowds split and merge"""
     return get_or_404(Crowd,cid).simple()
+
+@cherrypy.expose
+@tools.json_out()
+def users(cid):
+    "returns all the users in a crowd"
+    crowd = get_or_404(Crowd,cid)
+    uids = [u['id'] for u in crowd.users]
+    users = User.find(User._id.is_in(uids))
+    return [u.to_d() for u in users]
+
+@cherrypy.expose
+@tools.json_out()
+def tweets(cid):
+    "returns all the tweets in a crowd"
+    crowd = get_or_404(Crowd,cid)
+    tweets = crowd.tweets()
+    return [t.to_d() for t in tweets]

### 2011-03-28 api/models.py

@@ -114,3 +114,15 @@ class Crowd(TwitterModel):
         del crowd['split']
         crowd['users'] = [u['id'] for u in crowd['users']]
         return crowd
+
+    def tweets(self,limit=1000):
+        "returns all of the tweets involved in the crowd"
+        if self.type!='ats':
+            raise NotImplementedError
+        uids = [u['id'] for u in self.users]
+        return Tweet.find(
+            Tweet.user_id.is_in(uids)&
+            Tweet.mentions.is_in(uids)&
+            Tweet.created_at.range(self.start, self.end),
+            limit=limit,
+            sort=Tweet._id)

### 2011-03-28 maroon/mock.py

@@ -66,6 +66,8 @@ class MockDB(object):
     def in_coll(self, cls, _id):
         return _id in self.data[cls.__name__]
 
+def _list_if_needed(v):
+    return v if isinstance(v,list) else [v]
 
 _mongo_ops = {
     '$lte':operator.le,
@@ -73,8 +75,8 @@ _mongo_ops = {
     '$ne':operator.ne,
     '$gte':operator.ge,
     '$gt':operator.gt,
-    '$in':lambda v,l: v in l,
-    '$nin':lambda v,l: v not in l,
+    '$in':lambda v,l: any(x in l for x in _list_if_needed(v)),
+    '$nin':lambda v,l: all(x not in l for x in _list_if_needed(v)),
     '$exists':lambda v,x: bool(x)==(v is not None),
     '$all':lambda l,g: all(v in l for v in g),
     }

### 2011-03-28 tests/api_tests.py

@@ -20,16 +20,17 @@ class TestAPI(unittest.TestCase):
         jeff = api.user.id('106582358')
         self.failUnlessEqual(jeff['sn'],'JeffAMcGee')
         self.failUnlessRaises(cherrypy.HTTPError, api.user.id, '12')
+        #FIXME: check date format
     
     def test_user_tweets(self):
         #tweets(uid,start_date=None,end_date=None,limit=100):
         jan5 = '1294185600'
         jan16 = '1295136000'
-        before = api.user.tweets('106582358',end_date=jan5)
+        before = api.user.tweets('106582358',max_date=jan5)
         self.failUnlessEqual(len(before),3)
-        after = api.user.tweets('106582358',start_date=jan16)
+        after = api.user.tweets('106582358',min_date=jan16)
         self.failUnlessEqual(len(after),4)
-        mid = api.user.tweets('106582358',start_date=jan5,end_date=jan16)
+        mid = api.user.tweets('106582358',min_date=jan5,max_date=jan16)
         self.failUnlessEqual(len(mid),12)
         lim = api.user.tweets('106582358',limit=5)
         self.failUnlessEqual(len(lim),5)
@@ -38,6 +39,16 @@ class TestAPI(unittest.TestCase):
         crowd = api.crowd.simple('test1')
         self.failUnlessEqual(crowd['size'],2)
         self.failUnlessEqual(crowd['users'][0],106582358)
+
+    def test_crowd_users(self):
+        users = api.crowd.users('test1')
+        names = sorted(u['sn'].lower() for u in users)
+        self.failUnlessEqual(['jeffamcgee','nod'],names)
+
+    def test_crowd_tweets(self):
+        settings.pdb()
+        tweets = api.crowd.tweets('test1')
+        self.failUnlessEqual(len(tweets),6)
 
     def _assert_search_res(self, expected,**kwargs):
         res = api.search.crowd(**kwargs)

### 2011-03-28 web/root.py
Added a search tab.
 Committer: Dirk <dirk@nowitzki.(none)>

 On branch master
 Changes to be committed:
   (use "git reset HEAD <file>..." to unstage)

	modified:   etc/settings.py
	modified:   web/root.py
	modified:   web/static/css/infolab.css
	modified:   web/templates/base.html
	modified:   web/templates/index.html

 Untracked files:
   (use "git add <file>..." to include in what will be committed)

	web/static/css/datePicker.css
	web/static/css/demo.css
	web/static/images/calendar.gif
	web/static/scripts/calendar_date_select.js
	web/static/scripts/date.js
	web/static/scripts/jquery.dateP

@@ -17,3 +17,11 @@ def index():
 def list():
     return _render('list.html')
 
+@cherrypy.expose
+def search():
+    return _render('search.html')
+
+@cherrypy.expose
+def advanced_search():
+    return _render('advanced_search.html')
+

### 2011-03-29 web/root.py
social network visualization works

@@ -25,3 +25,7 @@ def search():
 def advanced_search():
     return _render('advanced_search.html')
 
+@cherrypy.expose
+def crowd(cid):
+    return _render('crowd.html',cid=cid)
+

### 2011-03-29 docs/crowdy_gui.tex

@@
 \centering
-\includegraphics[width=400pt]{img/UIdesign.eps}
+\includegraphics[width=\linewidth]{img/UIdesign.jpg}
 \caption{Crowdy User Interface Design}
@@
 crowds in massive social messaging systems like Twitter and Facebook is
-important \cite{krishna:2010}. K. Y. Kamath et al. in the study suggest an
+important \cite{krishna:2010}. Kamath et al. in the study suggest an
 efficient locality-based clustering approach for identifying crowds of users in
@@
 
-In the other study based on the previous one, K. Y. Kamath et al
+In the other study based on the previous one, Kamath et al
 \cite{krishna:2011}, they add another salient feature - a novel crowd tracking
@@
 \section{Implementation}
+
+\subsection{Workflows}
+
 The system is designed to run in a user's web browser. As a result, we decided
@@
 it is not a part of this project, it is important to understand how the backend
-works, and how it fits into this project.  First, a crawler retrieves tweets
-from Twitter using Twitter's REST API, search API, and streaming API.  Next,
-this data goes through several filters that add additional information to the
-users and tweets.  After that, a program finds groups of users based on their
-communication patterns.  This data is stored as JSON in a MongoDB database.
-The backend also provides the RESTful API that we connect to.  To retrieve
-data, our system makes an HTTP GET request to the server.  The server returns
-data in the JSON format, which is easy to decode in Javascript.  Our GUI never
-directly reads from or writes to the database.
+works, and how it fits into this project. The workflows of the system can be
+decomposed into following parts: (i) a crawler retrieves tweets from Twitter using
+Twitter's REST API, search API, and streaming API; (ii) the corresponding data
+go through several filters that add additional information to the users and
+tweets; (iii) a program finds groups of users (i.e., crowds) based on their 
+communication patterns; (iv) the data of crowds are stored as JSON in a MongoDB
+database; (v) the backend also provides the RESTful API that we connect to; (vi)
+to retrieve data, our system makes an HTTP GET request to the server, and the 
+server returns data in the JSON format, which is easy to decode in Javascript.
+To make the architecture clean, we never allow our GUI directly read from or 
+write to the database.
+
+\subsection{Techniques}
 
@@
 abstract away the idiosyncrasies of the various web browsers. We are using the
-Simile Timeline library to produce the crowd timelines.  In the future, we may
-use the Google Maps API to display crowds on a map.
+Simile Timeline library \cite{simile} to produce the crowd timelines. In the 
+future, we may use the Google Maps API to display crowds on a map.
+
+\subsection{Features}
+
+In the system, we provide three perspectives to visualize the crowds: (i) timeline;
+(ii) list; (iii) map. We also support search function so users are able to search 
+crowds given query of text, time period of crowd, and size of crowd, and visualize
+the crowds with the three options of perspectives.
+
+\subsubsection{Timeline}
+
+We apply the Simile Timeline library which is developed by MIT's Computer Science
+and Artificial Intelligence Laboratory. BLAHBLAH WAITING JEFF'S STUFF.
+
+The timeline view
+
+\subsubsection{List}
+
+The list view requires a dynamic table in which it display as many rows as the
+amount of crowds returned by the API. Concretely, we issue a jQuery for all the
+available crowds in the database. The javascript helps to create the dynamic
+table which includes the following columns: Period, Tweets, Users. Ideally,
+this table should support sorting by column. Other than that, we plan to 
+implement detail information box for the tweets and user column after a row 
+is selected. In order to provide users a more clean page view, we may 
+restrict 10 crowds per page and thus, a multiple page navigation is possible.
+
+\subsubsection{Map}
+
+\subsubsection{Search}
+
+In the search function of the system, we provide a main search box in which 
+users can type a textual query to search for crowds which contains the query.
+Besides, users can also click the link of advanced search, so that they can 
+choose options of words, time period of crowd, size of crowd, presentation ways,
+and results they would like to see per page. We maintain indices for each kind
+of queries in the MongoDB database, so that we can efficiently return the results
+to users. Whenever a query is issued, the systems send a HTTP GET request to the
+backend, and the server would return the corresponding search results.
+
+In our future direction, we will also provide query options like location, user's
+screen name. So that users can search crowds that are in a specific city or an 
+area, and also search crowds that a specific user is involved in.
 

### 2011-03-29 docs/crowdy_gui.tex
added crowd view to docs

@@
 
-We apply the Simile Timeline library which is developed by MIT's Computer Science
-and Artificial Intelligence Laboratory. BLAHBLAH WAITING JEFF'S STUFF.
-
-The timeline view
+We apply the Simile Timeline library which is developed by MIT's Computer
+Science and Artificial Intelligence Laboratory. The timeline shows all of the
+crowds at a given time span.  The timeline allows the analyist to zoom in on a
+specific time, and move forward and backward thorough time.  The visualization
+shows how long the crowd lasts, and the size of the crowd. We may make the
+crowd taller or shorter based on the size of the crowd.  We will also display a
+few keywords from each crowd.
 
@@
 
+\subsubsection{Crowd View}
+When an analyst clicks a crowd in the list, timeline, or map view, we show an
+expanded view of the crowd. This is a form of progressive disclosure, where we
+give the analyst more information as they need it.  At the moment, we just show
+a network graph where nodes represent users, and edges represent the tweets
+between users. We plan to add the ability to drill down even more.  When the
+analyst clicks on a node, we can give the analyst more information about the
+user that was clicked on. When the analyst clicks on an edge, we can show the
+conversation between two users.
+
 \section{Evaluation}

### 2011-03-31 web/static/scripts/crowd_network.js
moved arbor into list view

@@ -1,0 +1,101 @@
+// Based on the atlas demo for arbor.js:
+// http://arborjs.org/atlas/
+
+Renderer = function(canvas){
+  canvas = $(canvas).get(0)
+  var ctx = canvas.getContext("2d")
+  var particleSystem = null
+
+  var that = {
+    init:function(system){
+      particleSystem = system
+      particleSystem.screen({padding:[10, 50, 10, 50]})
+
+      //$(window).resize(that.resize)
+      that.resize()
+    
+      that.initMouseHandling()
+    },
+    redraw:function(){
+      if (particleSystem===null) return
+
+      ctx.clearRect(0,0, canvas.width, canvas.height)
+      ctx.strokeStyle = "#d3d3d3"
+      particleSystem.eachEdge(function(edge, pt1, pt2){
+          ctx.beginPath()
+          ctx.lineWidth = edge.data.weight;
+          ctx.moveTo(pt1.x, pt1.y)
+          ctx.lineTo(pt2.x, pt2.y)
+          ctx.stroke()
+      })
+
+      particleSystem.eachNode(function(node, pt){
+        var label = node.data.sn||""
+        var w = ctx.measureText(label).width + 6
+        pt.x = Math.floor(pt.x)
+        pt.y = Math.floor(pt.y)
+
+        ctx.clearRect(pt.x-w/2, pt.y-7, w,14)
+
+        // draw the text
+        if (label){
+          ctx.font = "bold 11px Arial"
+          ctx.textAlign = "center"
+          ctx.fillStyle = "#888888"
+          ctx.fillText(label, pt.x, pt.y+4)
+        }
+      })    		
+    },
+    resize:function(){
+      var w = 480, //$(window).width(),
+          h = 240; //$(window).height();
+      canvas.width = w; canvas.height = h
+      particleSystem.screenSize(w,h)
+      that.redraw()
+    },
+    initMouseHandling:function(){
+      // no-nonsense drag and drop (thanks springy.js)
+      selected = null;
+      nearest = null;
+      var dragged = null;
+      var oldmass = 1
+
+      $(canvas).mousedown(function(e){
+          var pos = $(this).offset();
+          var p = {x:e.pageX-pos.left, y:e.pageY-pos.top}
+          selected = nearest = dragged = particleSystem.nearest(p);
+
+          if (selected.node !== null){
+          dragged.node.fixed = true
+          }
+          return false
+      });
+
+      $(canvas).mousemove(function(e){
+        var old_nearest = nearest && nearest.node._id
[…]

### 2011-03-31 web/static/scripts/crowd_network.js
arbor in boxy works!

@@ -99,3 +99,37 @@ Renderer = function(canvas){
   }
   return that
 }
+
+function loadCrowdNetworkGraph(cid,canvas) {
+  jQuery.getJSON('/api/1/crowd/users/'+cid, function(users) {
+    jQuery.getJSON('/api/1/crowd/tweets/'+cid, function(tweets) {
+      var nodes = {}
+      $.each(users, function(i,user) {
+          nodes[user._id] = user;
+      });
+      var edges = {};
+      // make edges into a weighted undirected graph
+      $.each(tweets, function(i,tweet) {
+        if('ats' in tweet) {
+          $.each(tweet.ats, function(j,at) {
+            if(at in nodes && tweet.uid in nodes) {
+              from = Math.min(tweet.uid,at);
+              to = Math.max(tweet.uid,at);
+              if(!(from in edges))
+                edges[from] = {}
+              if(to in edges[from])
+                edges[from][to].weight+=1;
+              else
+                edges[from][to] = {weight:1};
+            }
+          });
+        }
+      });
+      //start the force directed layout
+      var sys = arbor.ParticleSystem(4000, 500, 0.5, 55)
+      sys.renderer = Renderer(canvas)
+      sys.merge({nodes:nodes, edges:edges})
+      sys.parameters({stiffness:600})
+    });
+  });
+}

### 2011-03-31 web/static/scripts/crowd_network.js
created loadCrowdPopup method

@@ -1,4 +1,4 @@
-// Based on the atlas demo for arbor.js:
+// Renderer is based on the atlas demo for arbor.js:
 // http://arborjs.org/atlas/
 
 Renderer = function(canvas){
@@ -100,36 +100,42 @@ Renderer = function(canvas){
   return that
 }
 
-function loadCrowdNetworkGraph(cid,canvas) {
-  jQuery.getJSON('/api/1/crowd/users/'+cid, function(users) {
-    jQuery.getJSON('/api/1/crowd/tweets/'+cid, function(tweets) {
-      var nodes = {}
-      $.each(users, function(i,user) {
-          nodes[user._id] = user;
-      });
-      var edges = {};
-      // make edges into a weighted undirected graph
-      $.each(tweets, function(i,tweet) {
-        if('ats' in tweet) {
-          $.each(tweet.ats, function(j,at) {
-            if(at in nodes && tweet.uid in nodes) {
-              from = Math.min(tweet.uid,at);
-              to = Math.max(tweet.uid,at);
-              if(!(from in edges))
-                edges[from] = {}
-              if(to in edges[from])
-                edges[from][to].weight+=1;
-              else
-                edges[from][to] = {weight:1};
-            }
-          });
+function loadCrowdNetworkGraph(canvas,users,tweets) {
+  var nodes = {}
+  $.each(users, function(i,user) {
+      nodes[user._id] = user;
+  });
+  var edges = {};
+  // make edges into a weighted undirected graph
+  $.each(tweets, function(i,tweet) {
+    if('ats' in tweet) {
+      $.each(tweet.ats, function(j,at) {
+        if(at in nodes && tweet.uid in nodes) {
+          from = Math.min(tweet.uid,at);
+          to = Math.max(tweet.uid,at);
+          if(!(from in edges))
+            edges[from] = {}
+          if(to in edges[from])
+            edges[from][to].weight+=1;
+          else
+            edges[from][to] = {weight:1};
         }
       });
-      //start the force directed layout
-      var sys = arbor.ParticleSystem(4000, 500, 0.5, 55)
-      sys.renderer = Renderer(canvas)
-      sys.merge({nodes:nodes, edges:edges})
-      sys.parameters({stiffness:600})
+    }
+  });
+  //start the force directed layout
+  var sys = arbor.ParticleSystem(4000, 500, 0.5, 55)
[…]

### 2011-04-22 intake/ats/ats_crowds.py
With debug code for ats_crowds.

@@ -258,14 +258,15 @@ class Crowd(object):
 class Crowds(object):
     def __init__(self, epoch, decayCoefficient = 1.0):
         self.epoch = epoch
-        self.crowds = {}
+        self.crowds = None
         self.decayCoefficient = decayCoefficient
     def getCrowds(self):
-        graphId = self.epoch.getGraphId()
-        for line in map(lambda l: l.strip().split(),
-                     open(self.epoch.getCrowdsFile(paramInfo = '%s'%self.decayCoefficient))):
-            crowd = Crowds.getCrowdFromLine(line, graphId)
-            if crowd!=None: self.crowds[crowd.crowdId] = crowd
+        if self.crowds==None:
+            graphId = self.epoch.getGraphId()
+            for line in map(lambda l: l.strip().split(),
+                         open(self.epoch.getCrowdsFile(paramInfo = '%s'%self.decayCoefficient))):
+                crowd = Crowds.getCrowdFromLine(line, graphId)
+                if crowd!=None: self.crowds[crowd.crowdId] = crowd
         return self.crowds
     @staticmethod
     def difference(crowd1, crowd2): return list(set(crowd1.users).intersection(set(crowd2.users)))
@@ -382,7 +383,122 @@ class Evolution(object):
 #            for user in filter(lambda u: u not in usersInNextCrowds, currentCrowd.users):
 #                UTC.saveUserToCrowd({'_id': user, 'r': [currentCrowd.crowdId], 'b': ''})
 
+    @staticmethod
+    def debugBuildCrowdEvolutionGraph(currentCrowdsObject, nextCrowdsObject, currentTime):
+        from operator import itemgetter
+        def getParentCrowds(possibleParentCrowds):
+            sizeToCrowdMap = {}
+            [sizeToCrowdMap.setdefault(possibleParentCrowds[c], []).append(c) for c in possibleParentCrowds.keys()]
+            sortedParentCrowds = sorted(sizeToCrowdMap.iteritems(), key=itemgetter(0), reverse=True)
+            if sortedParentCrowds: 
+                return sortedParentCrowds[0][1]
+            else: return ['None']
+        # Current crowds are the older crowds and the next crowds are the latest discovered crowds.
+#        currentCrowdsObject, nextCrowdsObject = Crowds(currentEpoch, decayCoefficient), Crowds(currentEpoch.next(), decayCoefficient)
[…]

### 2011-04-22 intake/ats/ats_crowds.py
Fixed the issue with None crowds.

@@ -330,8 +330,10 @@ class Evolution(object):
                     if parentCrowd not in crowdsWithChildren:
                         # Crowd crowd continued as before.
                         currentCrowd = currentCrowds[parentCrowd]
-                        crowdsDB.save({'_id': currentCrowd.parentCrowdId, 'users': nextCrowd.users})
-                        nextCrowds[nextCrowd.crowdId].parentCrowdId = currentCrowd.parentCrowdId
+                        pid=currentCrowd.parentCrowdId
+                        if pid=='None': pid=currentCrowd.crowdId
+                        crowdsDB.save({'_id': pid, 'users': nextCrowd.users})
+                        nextCrowds[nextCrowd.crowdId].parentCrowdId = pid
                         crowdsWithChildren.append(currentCrowd.parentCrowdId)
                     else:
                         # The crowd split from the parent.

### 2011-04-22 api/crowd.py
added star to api

@@ -1,7 +1,7 @@
 import cherrypy
 from cherrypy import tools
 from api.models import Crowd,User,Tweet,Edges
-from utils import get_or_404
+from utils import get_or_404, parse_bool
 
 @cherrypy.expose
 @tools.json_out()
@@ -32,3 +32,16 @@ def tweets(cid):
     crowd = get_or_404(Crowd,cid)
     tweets = crowd.tweets()
     return [t.to_d() for t in tweets]
+
+@cherrypy.expose
+@tools.json_out()
+def star(cid,starred='t'):
+    "star or unstar a crowd"
+    #FIXME: this should verify that it was a POST
+    crowd = get_or_404(Crowd,cid)
+    starred = parse_bool(starred)
+    if starred!=crowd.star:
+        crowd.star = starred
+        crowd.save()
+    return crowd.simple()
+

### 2011-04-22 api/models.py

@@ -107,6 +107,7 @@ class Crowd(TwitterModel):
     merge = ListProperty('merge')
     split = ListProperty('split')
     size = IntProperty('size')
+    star = BoolProperty('star')
 
     def simple(self):
         crowd = self.to_d()

### 2011-04-23 maroon/__init__.py
updated maroon to add sort_list to find

@@ -1,8 +1,8 @@
 from maroon import *
 from tee import TeeDB
 from mock import MockDB
+from maroondb import MaroonDB, ASCENDING, DESCENDING
 
-from mongo import MongoDB
 try:
     from mongo import MongoDB
 except ImportError:

### 2011-04-23 maroon/maroon.py

@@ -386,10 +386,16 @@ class Model(ModelPart):
     _rev = IdProperty('_rev')
 
     def save(self):
+        "Save the model to the database, may overwrite existing objects"
         return self.database.save(self)
 
     def delete(self):
+        "remove the object from the database"
         return self.database.delete_id(self.__class__.__name__,self._id)
+
+    def merge(self):
+        "Use this object to update an object that is already in the database."
+        return self.database.merge(self)
 
     @classmethod
     def bulk_save(cls, models):

### 2011-04-23 maroon/maroondb.py

@@ -1,0 +1,33 @@
+
+try:
+    from mongo import ASCENDING, DESCENDING
+except ImportError:
+    ASCENDING, DESCENDING = 1,-1
+
+class MaroonDB(object):
+    def get_all(self, cls, **kwargs):
+        return self.find(cls,None,**kwargs)
+
+    def _sort_key_list(self, sort=None, sort_list=None, descending=False):
+        if sort_list and sort:
+            raise ValueError("Do not set sort_list and sort parameters.")
+        if sort:
+            return [(_field_name(sort),DESCENDING if descending else ASCENDING)]
+        elif sort_list:
+            return [_sort_key_item(x,descending) for x in sort_list]
+        else:
+            return []
+
+
+def _sort_key_item(item,desc):
+    if isinstance(item,(list,tuple)):
+        return (_field_name(item[0]), item[1])
+    else:
+        return (_field_name(item), DESCENDING if desc else ASCENDING)
+
+
+def _field_name(field):
+    try:
+        return field.name
+    except AttributeError:
+        return field

### 2011-04-23 maroon/mock.py

@@ -6,8 +6,9 @@ from collections import defaultdict
 from operator import attrgetter
 import operator
 import glob
+from maroondb import MaroonDB, ASCENDING, DESCENDING
 
-class MockDB(object):
+class MockDB(MaroonDB):
     """Read a tiny database from the filesystem, and modify it in-memory.
     This class is only for testing and debuging purposes!"""
     def __init__(self, path=None, module=None):
@@ -35,10 +36,7 @@ class MockDB(object):
     def get_id(self, cls, _id):
         return self.data[cls.__name__].get(_id,None)
 
-    def get_all(self, cls, **kwargs):
-        return self.find(cls,None,**kwargs)
-
-    def find(self, cls, q, limit=None, sort=None, descending=False, **kwargs):
+    def find(self, cls, q=None, limit=None, **kwargs):
         long_names = cls.long_names
         if q:
             try:
@@ -51,14 +49,13 @@ class MockDB(object):
                 ]
         else:
             results = self.data[cls.__name__].values()
-        if sort is not None:
-            try:
-                name = sort.name
-            except AttributeError:
-                name = sort
-            results.sort(
-                key=attrgetter(long_names.get(name)),
-                reverse=descending)
+        sort_args = self._sort_key_list(**kwargs)
+        if sort_args:
+            sort_args.reverse()
+            for name,dir in sort_args:
+                results.sort(
+                    key=attrgetter(long_names.get(name)),
+                    reverse=(dir==DESCENDING))
         if limit is not None:
             results = results[0:limit]
         return results

### 2011-04-23 maroon/mongo.py

@@ -4,11 +4,10 @@ by Jeremy Kelley <jeremy@33ad.org> and Jeff McGee <JeffAMcGee@gmail.com>
 '''
 
 import pymongo
-from pymongo.database import Database
-from pymongo import ASCENDING, DESCENDING
+from maroondb import MaroonDB
 
 
-class MongoDB(Database):
+class MongoDB(pymongo.database.Database,MaroonDB):
     def __init__(self, connection=None, name='maroon', **kwargs):
         if connection==None:
             connection = pymongo.Connection(**kwargs)
@@ -29,30 +28,32 @@ class MongoDB(Database):
         model._id = d['_id'] # save the unique id from mongo
         return model
 
+    def merge(self, model):
+        d = model.to_d(dateformat="datetime")
+        del d['_id']
+        self._coll(model).find_and_modify(
+            {'_id':model._id},
+            {'$set':d},
+            upsert=True,
+            )
+
     def get_id(self, cls, _id):
         d = self[cls.__name__].find_one(_id)
         return cls(d) if d else None
 
-    def get_all(self, cls, **kwargs):
-        return self.find(cls,None,**kwargs)
-
-    def find(self, cls, q, limit=None, sort=None, descending=False, **kwargs):
+    def find(self, cls, q=None, limit=None, **kwargs):
         coll = self[cls.__name__]
         try:
             q = q.to_mongo_dict()
         except AttributeError:
             pass
         cursor = coll.find(q, **kwargs)
-        if sort !=None:
-            try:
-                name = sort.name
-            except AttributeError:
-                name = sort
-            cursor = cursor.sort(name,DESCENDING if descending else ASCENDING)
-        if limit != None:
-            cursor = cursor.limit(limit)
+        sort_args = self._sort_key_list(**kwargs)
+        if sort_args:
+            cursor.sort(sort_args)
+        if limit:
+            cursor.limit(limit)
         return (cls(d) for d in cursor)
 
     def in_coll(self, cls, _id):
         return bool(self[cls.__name__].find(dict(_id=_id)).count())
-

### 2011-04-23 maroon/tests/database_tests.py

@@ -40,6 +40,15 @@ class TestBasicModelCreationAndAssignment(unittest.TestCase):
         ob = SimpleModel.get_id("mustafa")
         self.failUnlessEqual(3, ob.int2)
 
+    def test_merge(self):
+        f = FunModel(_id='7',enum='red')
+        f.save()
+        g = FunModel(_id='7',dic={'three':4})
+        g.merge()
+        ob = FunModel.get_id('7').to_d()
+        del ob['ca']
+        self.failUnlessEqual(ob, dict(_id='7', e='red', d={'three':4}))
+
     def test_missing_fields(self):
         obj1 = SimpleModel({'_id':'simba','i1':2})
         obj1.save()

### 2011-04-23 maroon/tests/query_tests.py

@@ -97,6 +97,8 @@ class TestQueries(unittest.TestCase):
         n = NumberModel.n
         self.failUnlessEqual( [1,4,5,9], _query_to_list(
             n.is_in([1,4,5,9]) ))
+        self.failUnlessEqual( [3,4,6,8,9], _query_to_list(
+            NumberModel.factors.is_in([3,4]) ))
 
     def test_is_not_in(self):
         n = NumberModel.n
@@ -131,10 +133,18 @@ class TestQueries(unittest.TestCase):
         self.failUnlessEqual(range(11), _query_to_list({}))
 
     def test_sort(self):
+        #sort by property
         sorted = [nm.n for nm in NumberModel.find(sort=NumberModel.n)]
         self.failUnlessEqual(range(11), sorted)
-        results = NumberModel.find(NumberModel.n.range(4,8),sort='quad')
-        self.failUnlessEqual([0,1,1,4], [nm.quad for nm in results])
+        #sort by a field name
+        subset = NumberModel.n.range(4,8)
+        res = NumberModel.find(subset,sort='quad')
+        self.failUnlessEqual([0,1,1,4], [nm.quad for nm in res])
+        #sort by a list of fields
+        res = NumberModel.find(subset,sort_list=['quad',NumberModel.n])
+        self.failUnlessEqual([5,4,6,7], [nm.n for nm in res])
+        res = NumberModel.find(subset,sort_list=['quad',('n',maroon.DESCENDING)])
+        self.failUnlessEqual([5,6,4,7], [nm.n for nm in res])
 
 
 if __name__ == '__main__':

### 2011-04-23 maroon/mongo.py
search sorts starred items to the top

@@ -11,7 +11,7 @@ class MongoDB(pymongo.database.Database,MaroonDB):
     def __init__(self, connection=None, name='maroon', **kwargs):
         if connection==None:
             connection = pymongo.Connection(**kwargs)
-        Database.__init__(self,connection,name)
+        pymongo.database.Database.__init__(self,connection,name)
 
     def _coll(self, model):
         return self[model.__class__.__name__]

### 2011-04-23 api/models.py
added default value for star

@@ -107,7 +107,7 @@ class Crowd(TwitterModel):
     merge = ListProperty('merge')
     split = ListProperty('split')
     size = IntProperty('size')
-    star = BoolProperty('star')
+    star = BoolProperty('star',default=False)
 
     def simple(self):
         crowd = self.to_d()

### 2011-04-23 maroon/couch.py
mergeing lots of changes to maroon

@@ -18,9 +18,9 @@ class CouchDB(Database,MaroonDB):
             ds.append(d)
         self.bulk_save(ds)
 
-    def get_id(self, cls, _id):
+    def get_id(self, cls, _id, **kwargs):
         try:
-            d = self.open_doc(_id)
+            d = self.open_doc(_id, **kwargs)
             return cls(d)
         except ResourceNotFound:
             return None

### 2011-04-23 maroon/maroon.py

@@ -332,7 +332,8 @@ class ModelPart(object):
         self.__dict__[n] = v
 
     def __repr__(self):
-        return pprint.pformat(self.to_d())
+        d = pprint.pformat(self.to_d())
+        return "%s(%s)"%(self.__class__.__name__,d)
 
     @classmethod
     def update_long_names(cls):
@@ -381,6 +382,14 @@ class ModelProperty(TypedProperty):
         return val
 
 
+class ModelListProperty(ListProperty):
+    def __init__(self, name, kind=ModelPart, **kwargs):
+        ListProperty.__init__(self, name, kind, **kwargs)
+
+    def to_d(self, val, **kwargs):
+        return [x.to_d(**kwargs) for x in val]
+
+
 class Model(ModelPart):
     _id = IdProperty("_id")
     _rev = IdProperty('_rev')
@@ -404,10 +413,14 @@ class Model(ModelPart):
     @classmethod
     def in_db(cls,_id):
         return cls.database.in_coll(cls, _id)
+    
+    @classmethod
+    def __contains__(cls,_id):
+        return cls.in_db(_id)
 
     @classmethod
-    def get_id(cls, _id):
-        return cls.database.get_id(cls,_id)
+    def get_id(cls, _id, **kwargs):
+        return cls.database.get_id(cls,_id, **kwargs)
 
     @classmethod
     def get_all(cls,**kwargs):

### 2011-04-23 maroon/maroondb.py

@@ -5,16 +5,23 @@ except ImportError:
     ASCENDING, DESCENDING = 1,-1
 
 class MaroonDB(object):
+    def merge(self, model):
+        old = self.get_id(model.__class__,model._id)
+        d = model.to_d(dateformat="datetime")
+        d.pop('_rev',None)
+        old.update(d)
+        old.save()
+
     def get_all(self, cls, **kwargs):
         return self.find(cls,None,**kwargs)
 
-    def _sort_key_list(self, sort=None, sort_list=None, descending=False):
+    def _sort_key_list(self, sort=None, sort_list=None, desc=False, **kwargs):
         if sort_list and sort:
             raise ValueError("Do not set sort_list and sort parameters.")
         if sort:
-            return [(_field_name(sort),DESCENDING if descending else ASCENDING)]
+            return [(_field_name(sort),DESCENDING if desc else ASCENDING)]
         elif sort_list:
-            return [_sort_key_item(x,descending) for x in sort_list]
+            return [_sort_key_item(x,desc) for x in sort_list]
         else:
             return []
 

### 2011-04-23 maroon/mock.py

@@ -33,7 +33,7 @@ class MockDB(MaroonDB):
         self.data[model.__class__.__name__][model._id] = model
         return model
 
-    def get_id(self, cls, _id):
+    def get_id(self, cls, _id, **kwargs):
         return self.data[cls.__name__].get(_id,None)
 
     def find(self, cls, q=None, limit=None, **kwargs):

### 2011-04-23 maroon/mongo.py

@@ -37,22 +37,19 @@ class MongoDB(pymongo.database.Database,MaroonDB):
             upsert=True,
             )
 
-    def get_id(self, cls, _id):
-        d = self[cls.__name__].find_one(_id)
+    def get_id(self, cls, _id, **kwargs):
+        d = self[cls.__name__].find_one(_id, **kwargs)
         return cls(d) if d else None
 
-    def find(self, cls, q=None, limit=None, **kwargs):
+    def find(self, cls, q=None, **kwargs):
         coll = self[cls.__name__]
         try:
             q = q.to_mongo_dict()
         except AttributeError:
             pass
-        cursor = coll.find(q, **kwargs)
         sort_args = self._sort_key_list(**kwargs)
-        if sort_args:
-            cursor.sort(sort_args)
-        if limit:
-            cursor.limit(limit)
+        kwargs.pop("sort",None)
+        cursor = coll.find(q, sort=sort_args, **kwargs)
         return (cls(d) for d in cursor)
 
     def in_coll(self, cls, _id):

### 2011-04-23 maroon/tests/database_tests.py

@@ -47,6 +47,7 @@ class TestBasicModelCreationAndAssignment(unittest.TestCase):
         g.merge()
         ob = FunModel.get_id('7').to_d()
         del ob['ca']
+        ob.pop('_rev',None)
         self.failUnlessEqual(ob, dict(_id='7', e='red', d={'three':4}))
 
     def test_missing_fields(self):

### 2011-04-23 maroon/tests/query_tests.py

@@ -8,6 +8,7 @@ from mock import MockDB
 import unittest
 
 import maroon
+import maroondb
 from maroon import Model, TextProperty, IntProperty, ListProperty, BogusQuery
 
 
@@ -143,13 +144,17 @@ class TestQueries(unittest.TestCase):
         #sort by a list of fields
         res = NumberModel.find(subset,sort_list=['quad',NumberModel.n])
         self.failUnlessEqual([5,4,6,7], [nm.n for nm in res])
-        res = NumberModel.find(subset,sort_list=['quad',('n',maroon.DESCENDING)])
+        res = NumberModel.find(subset,sort_list=['quad',('n',maroondb.DESCENDING)])
         self.failUnlessEqual([5,6,4,7], [nm.n for nm in res])
 
 
 if __name__ == '__main__':
-    Model.database = MockDB(None)
-    #Model.database = MongoDB(None,'test_maroon',port=2727)
-    #Model.database.NumberModel.remove()
+    db = sys.argv[1]
+    if db=='mongo':
+        Model.database = MongoDB(None,'test_maroon',port=2727)
+        Model.database.NumberModel.remove()
+    elif db=='mock':
+        Model.database = MockDB(None)
     _number_set_up()
+    del sys.argv[1]
     unittest.main()

### 2011-04-24 api/models.py
added chart to crowd detail view

@@ -1,4 +1,5 @@
 import datetime
+from datetime import timedelta
 try:
     import simplejson as json
 except:

### 2011-04-24 web/root.py

@@ -1,31 +1,85 @@
 #!/usr/bin/env python
 import cherrypy
 from cherrypy import tools
+import api.crowd
+import datetime
+from datetime import datetime as dt
+from collections import defaultdict
+
+from graphy.backends import google_chart_api
+from graphy import common
 
 from jinja2 import Environment, FileSystemLoader
 #FIXME: I don't like that this is a global variable - Jeff
 _env = Environment(loader=FileSystemLoader('web/templates'))
 
+
 def _render(path, **kwargs):
     return _env.get_template(path).render(**kwargs)
+
 
 @cherrypy.expose
 def index():
     return _render('index.html')
 
+
 @cherrypy.expose
 def list():
     return _render('list.html')
 
-#@cherrypy.expose
-#def search():
-#    return _render('search.html')
 
 @cherrypy.expose
 def advanced_search():
     return _render('advanced_search.html')
 
+
+CHART_WIDTH = 335
+CHART_HEIGHT = 150
+
+
+def _label_axis(axis,hours,delta,format):
+    positions = [h for h in hours if h%delta==0]
+    axis.min = hours[0]
+    axis.max = hours[-1]
+    axis.label_positions = positions
+    axis.labels = [
+            dt.utcfromtimestamp(p*3600).strftime(format)
+            for p in positions]
+
+
+def _chart_html(stamps):
+    counts = defaultdict(int)
+    for s in stamps:
+        counts[s/3600]+=1
+    start, end = min(counts.keys()),max(counts.keys())
+    hours = range(start-1,end+2)
+    data = [counts[h] for h in hours]
+    start_dt = dt.utcfromtimestamp(start*3600)
+    
+    chart = google_chart_api.LineChart(data)
+    if len(hours)>=48:
+        _label_axis(chart.bottom,hours,24,"%m/%e")
+    else:
+        if len(hours)>=9:
+            _label_axis(chart.bottom,hours,6,"%H:00")
+        else:
+            _label_axis(chart.bottom,hours,1,"%H:00")
+        day_axis = chart.AddAxis(common.AxisPosition.BOTTOM, common.Axis())
+        _label_axis(day_axis,hours,24,"%m/%e")
+
+    chart.left.min = 0
+    chart.left.max = max(data)
+    chart.left.labels = [chart.left.max*i/4 for i in range(1,5)]
+    chart.left.label_positions = chart.left.labels
+    
[…]

### 2011-04-24 web/root.py
the crowd popup returns json and saves 2 api calls

@@ -75,11 +75,11 @@ def _chart_html(stamps):
     return chart.display.Img(CHART_WIDTH, CHART_HEIGHT)
 
 
+@tools.json_out()
 @cherrypy.expose
 def crowd(cid):
+    users = api.crowd.users(cid)
     tweets = api.crowd.tweets(cid)
     stamps = [int(t['ca']) for t in tweets]
-
-    return _render('crowd.html',
-            cid=cid,
-            time_chart=_chart_html(stamps))
+    html = _render('crowd.html', time_chart=_chart_html(stamps))
+    return dict(users=users, tweets=tweets, html=html)

### 2011-04-24 web/static/scripts/crowd_network.js

@@ -170,10 +170,8 @@ function showTweets(list,tweets,users,start,next){
 //	nextpage.onclick=showTweets(tweets,users,start);
 //}
 
-function loadCrowdPopup(cid,elem) {
-  jQuery.getJSON('/api/1/crowd/users/'+cid, function(users) {
-    jQuery.getJSON('/api/1/crowd/tweets/'+cid, function(tweets) {
-        loadCrowdNetworkGraph(elem.find('canvas'),users,tweets);
+function loadCrowdPopup(cid,elem,users,tweets) {
+    loadCrowdNetworkGraph(elem.find('canvas'),users,tweets);
 	var list = elem.find('.mylist');
 	var next = elem.find('.next');
 
@@ -188,6 +186,4 @@ function loadCrowdPopup(cid,elem) {
 			start += 5; 
 		});
 	}
-    });
-  });
 }

### 2011-04-24 intake/ats/ats_crowds.py
Changed file data path,

@@ -12,7 +12,7 @@ from datetime import datetime
 #crawled_data_path = '/mnt/chevron/kykamath/data/twitter/ats/crawler/'
 #crowd_path = '/mnt/chevron/kykamath/data/twitter/ats'
 #data_dir = '/mnt/sid/hou_crowds'
-data_dir = '/data/twitter/crowdy/ats/hou'
+data_dir = '/home/kykamath/hou'
 crawled_data_path = '%s/crawler/'%data_dir
 crowd_path = data_dir
 crowd_type = 'ats'

### 2011-04-24 intake/ats/ats_crowds.py
Add try:except for KeyError.

@@ -230,7 +230,16 @@ class MCL(object):
             for i in data: graph_file.write('%s %s %d\n'%(dataMap[i[0]], dataMap[i[1]], i[2]))
             graph_file.close()
             os.system('mcl graph -q x -V all --abc -o graph.out')
-            for l in open('graph.out'): clusters.append([reverseDataMap[i] for i in l.strip().split()])
+#           for l in open('graph.out'): clusters.append([reverseDataMap[i] for i in l.strip().split()]) 
+            for l in open('graph.out'): 
+                clusterList=[]
+                for i in l.strip().split():
+                    try:
+                        clusterList.append(reverseDataMap[i]) 
+                    except KeyError: 
+                        print 'Key not found'
+                        pass
+                clusters.append(clusterList)
             os.system('rm -rf /tmp/mcl_dir/*')
         return clusters
     def writeClusters(self):

### 2011-04-24 intake/ats/ats_crowds.py
Added code to check list size..

@@ -247,7 +247,7 @@ class MCL(object):
         data = []
         for line in open(self.epoch.getGraphFile(paramInfo = '%s'%self.decayCoefficient)):
             tempD = line.strip().split()
-            data.append((tempD[0], tempD[1], int(tempD[2])))
+            if len(tempD)>=3: data.append((tempD[0], tempD[1], int(tempD[2])))
         clusters, id = {}, 1
         for d in MCL._graphCluster(data): 
             clusters[id] = d

### 2011-04-24 docs/crowdy_gui.tex
Chiao updated the report tex file.

@@
 
-The list view requires a dynamic table in which it display as many rows as the
+The list view requires a dynamic table in which it displays as many rows as the
 amount of crowds returned by the API. Concretely, we issue a jQuery for all the
 available crowds in the database. The javascript helps to create the dynamic
-table which includes the following columns: Period, Tweets, Users. Ideally,
-this table should support sorting by column. Other than that, we plan to 
-implement detail information box for the tweets and user column after a row 
-is selected. In order to provide users a more clean page view, we may 
-restrict 10 crowds per page and thus, a multiple page navigation is possible.
+table which includes the following columns: Like, Period and number of users in the crowd.
+Users can click on the ``like'' of each crowd to indicate the preference.
+The preferred crowds will be push up to the beginning of the list.
+Once a row of crowd is clicked, a slide down box with detail information(crowd user network, tweets) will be shown below.
+In order to provide users a cleaner page view, we restrict 5 tweets per page to show in the slide down box and thus, a multiple page navigation is possible.
 
@@
 \section{CONCLUSIONS}
-
+In conclusion, we have implemented the Social Crowd Visualization system as a web application that enable users to visualize,summarize and organize temporal crowd formation on Twitter.
+We studied several types of potential users and design the interface carefully to meet their needs.
+We implemented a few different layout format and a search component to ease the crowd retrieval effort on user.
+Finally, we design a sequence of possible evaluations for this system.
+The interface will be continually improved as it is also an on-going DARPA project with the InfoLab.
+As the next step, a few direction such as user model construction and map view implementation will be carried out.
 \section{FUTURE WORK}

### 2011-04-24 web/root.py
cleaned up tweet chart a little

@@ -33,8 +33,8 @@ def advanced_search():
     return _render('advanced_search.html')
 
 
-CHART_WIDTH = 335
-CHART_HEIGHT = 150
+CHART_WIDTH = 480
+CHART_HEIGHT = 240
 
 
 def _label_axis(axis,hours,delta,format):
@@ -58,19 +58,20 @@ def _chart_html(stamps):
     
     chart = google_chart_api.LineChart(data)
     if len(hours)>=48:
-        _label_axis(chart.bottom,hours,24,"%m/%e")
+        _label_axis(chart.bottom,hours,24,"%b %e")
     else:
         if len(hours)>=9:
             _label_axis(chart.bottom,hours,6,"%H:00")
         else:
             _label_axis(chart.bottom,hours,1,"%H:00")
         day_axis = chart.AddAxis(common.AxisPosition.BOTTOM, common.Axis())
-        _label_axis(day_axis,hours,24,"%m/%e")
+        _label_axis(day_axis,hours,24,"%b %e")
 
     chart.left.min = 0
     chart.left.max = max(data)
     chart.left.labels = [chart.left.max*i/4 for i in range(1,5)]
     chart.left.label_positions = chart.left.labels
+    chart.display.extra_params['chtt']="Tweets per Hour"
     
     return chart.display.Img(CHART_WIDTH, CHART_HEIGHT)
 

### 2011-04-25 intake/ats/ats_crowds.py
Creating crowds of size >=4, to see if this increases speed of crowd creation.

@@ -12,14 +12,16 @@ from datetime import datetime
 #crawled_data_path = '/mnt/chevron/kykamath/data/twitter/ats/crawler/'
 #crowd_path = '/mnt/chevron/kykamath/data/twitter/ats'
 #data_dir = '/mnt/sid/hou_crowds'
-data_dir = '/home/kykamath/hou'
+#data_dir = '/home/kykamath/hou'
+data_dir = '/data/twitter/crowdy/ats1/'
 crawled_data_path = '%s/crawler/'%data_dir
 crowd_path = data_dir
 crowd_type = 'ats'
 edge_threshold_weight = 1.3
+minimumNumberOfUsersInCrowd = 4
 
 # DB initialization
-mongodb_connection = Connection('localhost', 27017)
+mongodb_connection = Connection('localhost', 27020)
 crowds_db = mongodb_connection.hou
 edges = crowds_db.ats_graph_edges
 edges.ensure_index('_id')
@@ -272,6 +274,7 @@ class Crowds(object):
         self.decayCoefficient = decayCoefficient
     def getCrowds(self):
         if self.crowds==None:
+            self.crowds={}
             graphId = self.epoch.getGraphId()
             for line in map(lambda l: l.strip().split(),
                          open(self.epoch.getCrowdsFile(paramInfo = '%s'%self.decayCoefficient))):
@@ -283,7 +286,7 @@ class Crowds(object):
     @staticmethod
     def getCrowdFromLine(line, graphId):
         splitIndex, splitIndex2, splitIndex3 = line.index(':ilab:'), line.index(':ilab2:'), line.index(':ilab3:')
-        if len(line[1:splitIndex])>=3:
+        if len(line[1:splitIndex])>=minimumNumberOfUsersInCrowd:
             return Crowd('%s:%s'%(graphId, line[0]), line[splitIndex3+1] ,line[1:splitIndex], 
                          map(lambda id: int(id), line[splitIndex+1:splitIndex2]), 
                          map(lambda id: int(id), line[splitIndex2+1:splitIndex3]))
@@ -329,6 +332,7 @@ class Evolution(object):
                     [users.remove(u) for u in commonUsers]
                 else: users.remove(users[0])
             parentCrowds = getParentCrowds(possibleParentCrowds)
+
             if len(parentCrowds)==1:
                 if parentCrowds[0]=='None':
                     # First time the crowd is observed.
@@ -379,120 +383,108 @@ class Evolution(object):
                             else:
                                 # The crowd has split into this crowd.
[…]

### 2011-04-25 tests/ats/ats_crowds_tests.py

@@ -5,10 +5,10 @@ Created on Feb 21, 2011
 '''
 import sys
 from pymongo.connection import Connection, database
-sys.path.append('../../intake')
+sys.path.append('../../intake/ats')
 import unittest
 from operator import itemgetter
-from ats.ats_crowds import Epoch, GraphReader, MCL, Evolution, CrowdsDB
+from ats_crowds import Epoch, GraphReader, MCL, Evolution, CrowdsDB
 
 #TEST_STARTING_EPOCH = 1280639087
 #TEST_ENDING_EPOCH = 1288846743

### 2011-04-25 intake/ats/ats_crowds.py
Creating crowds of size >=4, to see if this increases speed of crowd creation.

@@ -21,7 +21,7 @@ edge_threshold_weight = 1.3
 minimumNumberOfUsersInCrowd = 4
 
 # DB initialization
-mongodb_connection = Connection('localhost', 27020)
+mongodb_connection = Connection('localhost', 27017)
 crowds_db = mongodb_connection.hou
 edges = crowds_db.ats_graph_edges
 edges.ensure_index('_id')

### 2011-04-25 intake/ats/ats_crowds.py
Creating crowds of size >=4, to see if this increases speed of crowd creation.

@@ -12,8 +12,8 @@ from datetime import datetime
 #crawled_data_path = '/mnt/chevron/kykamath/data/twitter/ats/crawler/'
 #crowd_path = '/mnt/chevron/kykamath/data/twitter/ats'
 #data_dir = '/mnt/sid/hou_crowds'
-#data_dir = '/home/kykamath/hou'
-data_dir = '/data/twitter/crowdy/ats1/'
+data_dir = '/home/kykamath/hou'
+#data_dir = '/data/twitter/crowdy/ats1/'
 crawled_data_path = '%s/crawler/'%data_dir
 crowd_path = data_dir
 crowd_type = 'ats'

### 2011-04-25 web/root.py
Fixed both timeline view and list view for advanced search. Should work fine. The only problem left is probably the images for pre and next button in selecting dates in calendar.

@@ -28,11 +28,6 @@ def list():
     return _render('list.html')
 
 
-@cherrypy.expose
-def advanced_search():
-    return _render('advanced_search.html')
-
-
 CHART_WIDTH = 480
 CHART_HEIGHT = 240
 

### 2011-04-25 web/static/scripts/crowd_network.js
star in list working

@@ -170,7 +170,39 @@ function showTweets(list,tweets,users,start,next){
 //	nextpage.onclick=showTweets(tweets,users,start);
 //}
 
-function loadCrowdPopup(cid,elem,users,tweets) {
+function starclick()
+{
+	alert("clicked")
+}
+
+function loadCrowdPopup(cid,elem,users,tweets,star) {
+    image0=new Image();
+    image1=new Image();
+    image0.src ="/static/images/yellow_star.jpg";
+    image1.src ="/static/images/red_star.jpg";
+    var str = elem.find('.star');
+    if(star==true)
+    {
+	str.attr("src",image1.src);
+    }
+    else
+    {
+	str.attr("src",image0.src);
+    }
+    str.click(function(){
+	if(star==true)
+	{
+	 str.attr("src",image0.src);
+	 star=false;
+	 jQuery.getJSON('/api/1/crowd/star/'+cid+'?starred=0');
+	}
+	else
+	{
+	 str.attr("src",image1.src);
+	 star=true;
+	 jQuery.getJSON('/api/1/crowd/star/'+cid+'?starred=1');
+	} 
+    });
     elem.find('.tabs').tabs("div.pane")
     loadCrowdNetworkGraph(elem.find('canvas'),users,tweets);
 	var list = elem.find('.mylist');

### 2011-04-25 intake/module.py
calculate degree centrality and clustering coeff

@@ -85,7 +85,8 @@ class CrowdFilter(Filter):
     def run(self):
         crowds = Crowd.get_all()
         for crowd in self.cfilter(crowds):
-            pass
+            if crowd:
+                crowd.save()
 
 
 class Grouper(Filter):

### 2011-04-25 intake/network.py

@@ -1,0 +1,35 @@
+import networkx as nx
+import operator
+from heapq import nlargest
+
+from etc.settings import settings
+from api.models import Crowd, Tweet
+from intake.module import CrowdFilter
+
+
+class CrowdNetworkFilter(CrowdFilter): 
+    def cfilter(self, crowds):
+        for crowd in crowds:
+            print "analyzing network for %s"%crowd._id
+            tweets = crowd.tweets(limit=0)
+            graph = self.make_graph(tweets)
+            crowd.clust_coeff = self.clust_coeff(graph)
+            self.central_users(crowd, graph)
+            yield crowd
+
+    def make_graph(self, tweets):
+        edges = [(tweet.user_id,at)
+            for tweet in tweets
+            for at in tweet.mentions
+            if tweet.user_id!=at]
+        return nx.Graph(edges)
+
+    def clust_coeff(self, graph):
+        return nx.average_clustering(graph)
+
+    def central_users(self, crowd, graph):
+        deg = nx.degree_centrality(graph)
+        for user in crowd.users:
+            user['cent']=deg.get(user['id'],0)
+        #pick the 10 users with the greatest centrality
+        crowd.central_users = nlargest(10, deg.iterkeys(), key=deg.__getitem__)

### 2011-04-26 api/search.py
added clustering coefficient

@@ -31,6 +31,8 @@ def crowd(q="", limit='100', sort=None, simple='t', **kwargs):
         when the crowd ended
     {min,max}_size
         the number of users involved in the crowd
+    {min,max}_clco
+        the clustering coefficient of the crowd (from 0 to 1.0)
 
     Here are some example calls:
 
@@ -49,6 +51,7 @@ def crowd(q="", limit='100', sort=None, simple='t', **kwargs):
         returns 10 crowds in the full format
     """
     query = (
+        range_from_params(Crowd, 'clco', float, kwargs) &
         range_from_params(Crowd, 'start', parse_date, kwargs) &
         range_from_params(Crowd, 'end', parse_date, kwargs) &
         range_from_params(Crowd, 'size', int, kwargs))

### 2011-04-26 api/utils.py

@@ -15,7 +15,7 @@ def parse_date(dstr):
 def range_from_params(cls, key, filter, kwargs):
     start = kwargs.get('min_'+key)
     end = kwargs.get('max_'+key)
-    return getattr(cls,key).range(
+    return getattr(cls,cls.long_names[key]).range(
             None if start is None else filter(start),
             None if end is None else filter(end))
 

### 2011-04-26 docs/crowdy_gui.tex
Added feature in search to support searching by minimum value of clustering coefficient

@@
 
-\section{Evaluation}
+\section{Evaluation Plan}
+In order to evaluate our system, we planned to conduct a 2-step usability study
+which includes a pilot study, and an evaluation study. In the pilot study, we
+will ask a relative small number of users (e.g., 5 - 10 people) to try our
+system, and fill in the usability questionaire. Then, we will refine the system
+based on the feedbacks from the pilot study (i.e., fixing bugs reported by users,
+modifying featuers that were not preferred). Finally, a large scale evaluation
+study also in the form of questionaire will be conducted on a user base of 30 -
+50 users including three types of users we mentioned earlier: normal users, 
+Twitter users, and analysts. The refinement step and the large-scale detailed
+evaluation study will be generated after the step of the pilot study. Thus, in
+this report, we only focus on the design of the pilot study.
+
+\subsection{Pilot Study}
+
+The pilot study we propose contains XX 5-scale likert (i.e., very good, good,
+okay, bad, and very bad) questions, and YY open questions. The questions are
+listed below:
+
+\begin{itemize}
+\item Whether the interface for timeline view is easy to use?
+\item Whether the interface for list view is easy to use?
+\item Whether the search feature for timeline view is easy to use?
+\item Whether the search results in the timeline view could answer the information
+need for your query.
+\item Whether the search feature for list view is easy to use?
+\item Whether the search results in the list view could answer the information
+need for your query.
+\item Whether 
+\end{itemize}
 
 \section{CONCLUSIONS}
-In conclusion, we have implemented the Social Crowd Visualization system as a web application that enable users to visualize,summarize and organize temporal crowd formation on Twitter.
-We studied several types of potential users and design the interface carefully to meet their needs.
-We implemented a few different layout format and a search component to ease the crowd retrieval effort on user.
-Finally, we design a sequence of possible evaluations for this system.
-The interface will be continually improved as it is also an on-going DARPA project with the InfoLab.
-As the next step, a few direction such as user model construction and map view implementation will be carried out.
+In conclusion, we have implemented the Social Crowd Visualization system as a
+web application that enable users to visualize,summarize and organize temporal
+crowd formation on Twitter. We studied several types of potential users and
+design the interface carefully to meet their needs. We implemented a few
+different layout format and a search component to ease the crowd retrieval
+effort on user. Finally, we design a sequence of possible evaluations for this
+system. The interface will be continually improved as it is also an on-going
+DARPA project with the InfoLab. As the next step, a few direction such as user
+model construction and map view implementation will be carried out.
+
 \section{FUTURE WORK}

### 2011-04-26 docs/crowdy_gui.tex
Updated Pratheek's part and my part in the documentation.

@@
 according to them is a potentially short-lived ad-hoc collection of users bound
-together by some common thread – which can be communication-based,
+together by some common thread - which can be communication-based,
 location-based or interest based. We are inspired by this idea of formation and
@@
 similar fashion.
+
+Some other studies related come from areas like social network visualization,
+short text visualization, progressive disclosure, and user modeling. Considering
+social network visualization , studies like \cite{Boyd:2008} by Boyd et al described features
+of on-line social networking sites and the history of the social networking sites,
+and the changes during their developments.Deeper understanding of the social
+networks can help boost the research in social network visualization. In Moreno's
+following work \cite{Moreno:1953}, he emphasized the use of pictorial representations to map
+social relations and the embedded patterns. He considered people as nodes in the
+network and relations between people as the edges in the network.Laumann et al
+\cite{Laumann:1966} applied computational procedure, multidimensional scaling to locate nodes in
+visualizing network. The authors are also the first to plot the networks in three
+dimensions. Other examples of good visualizations can be Facebook Friend Wheel
+\cite{facebook_wheel} which visualizes a Facebook user's network of friends in a wheel format and
+Trendsmap \cite{trends_map} which plots real time trending topics over two-dimensional (latitude,
+longitude) world map, and you can zoom in to see the trending topics for a specific
+location or an area.
+
+In the area of short text visualization, studies like \cite{Bishop:2007} tell that these social
+web-sites serve to fulfill their users' desires to interact with and help others.
+The authors also proposed a 3-level framework for understanding why members of online
+communities participate or not. According to the 3-level framework, users make
+comments or short-text post to have their voice be heard. Leggett and Shipman \cite{Leggett:04} 
+proposed and described the characteristic of interactive communication in seven
+dimensions in a similar way to examine characteristics of communication for a
+commenting system like roles,voices,interaction,indirection,history,narrative
+and media. In \cite{Hsu:09}, they tried to understand how an on-line community itself
+perceives the relative quality of its own user-contributed content and further
+used the information to promote valuable opinion from the flood of comments
+that attached to each social object.We compared three different visualization
+approaches including the traditional list view, the quantitative aggregation
+view and the personalized space view. We learned that, to best present massive
+metadata such as user contributed comments to the end user, a personalized
+filtering model is needed and that a 2D space positional layout is desired
+such as in the case of Plurk and Opinion Space systems.
+
+In the area of progressive disclosure, Phan et al built a prototype of a system
+that visualized packet traces from a computer network \cite{Phan:07} which is similar to
+the problem investigated. They introduced the concept of progressive multiples
+which combines progressive disclosure with small multiples. In Scalability in
+System Management GUIs \cite{Dieberger:06}, the authors use semantic zooming to show information
+about network configuration at various levels of detail, which can tell about
+the way progressive disclosure can be used for system administrators.In An
+Interactive Ambient Visualization for Code Smells \cite{Murphy:10}, the authors describe a
+method for alerting uses about code that may need refactoring. They created a
+plug-in for Eclipse that detected questionable code and alerts the programmer.
+This shows progressive disclosure for software developers.
+
+Involving user models and visualization into the picture, studies like \cite{Schlungbaum:97} tell
+that the individualization often depends on the user's expectation of the user
+interface which might be adapted or adaptable or adaptive user interface. Papers
+like \cite{Ho:01} explain that the user model selection is crucial for any tool and how
+the visualization can help in the discovering and building knowledge. Data and
+knowledge visualization module of such a system can be used to help the user
+interaction in other modules. This helps in better user interaction experience
+irrespective of which module of the system he/she is interacting with.The user's
+knowledge, preferences, goals etc. are generally included in the user model when
+visualization is concerned in such tools \cite{Henderson}. Also, critical factors like cognitive
+load on the user ought to be considered when such tools are made to ensure
+effectiveness.The identification of target users is also a important factor to be
+considered.Model-based tools like TADEUS can include explicit task and user models
+in their system, over potential to work in integrated user interface development
+environments and support the entire user interface life cycle. Although research
+papers like \cite{Schlungbaum:97}, talk about how different software tools can be used for helping
+the user designers create interfaces with consideration of user models , there have
+been efforts to combine user model with task and domain models to help developers
+in creating and designing user interface \cite{Tran:10}. Systems like DB-USE along with TADEUS
+help us in understanding of how user model can be combined with other models to help
+in creating/designing better user interface for applications which are mainly
+concerned with visualization.
 

### 2011-04-27 web/static/scripts/crowd_network.js
small cleanups

@@ -23,7 +23,7 @@ Renderer = function(canvas){
       ctx.strokeStyle = "#d3d3d3"
       particleSystem.eachEdge(function(edge, pt1, pt2){
           ctx.beginPath()
-          ctx.lineWidth = edge.data.weight;
+          ctx.lineWidth = Math.min(10,edge.data.weight);
           ctx.moveTo(pt1.x, pt1.y)
           ctx.lineTo(pt2.x, pt2.y)
           ctx.stroke()

### 2011-04-27 docs/crowdy_gui.tex
Updated evaluation part in the report.
add future work in the report

@@
 \documentclass{sig-alternate}
-\usepackage{algorithm}
-\usepackage{algorithmic}
+%\usepackage{algorithm}
+%\usepackage{algorithmic}
 \usepackage{url}
@@
 
-\begin{figure*}[t]
-\centering
-\includegraphics[width=\linewidth]{img/UIdesign.jpg}
-\caption{Crowdy User Interface Design}
-\label{fig:UIdesign}
-\end{figure*}
-
 \section{Related Work}
@@
 
-Figure \ref{fig:UIdesign} shows an outline of the prototype. We want to provide
+This section illustrate an outline of the prototype. We want to provide
 the user with a simple and flexible interface to maximize their options for
@@
 
-\subsubsection{Map}
-
 \subsubsection{Search}
@@
 The pilot study we propose contains XX 5-scale likert (i.e., very good, good,
-okay, bad, and very bad) questions, and YY open questions. The questions are
-listed below:
+okay, bad, and very bad) questions, and YY open questions. The likert-scale questions
+are listed below:
 
@@
 \item Whether the search feature for timeline view is easy to use?
+\item Whether the search feature for list view is easy to use?
 \item Whether the search results in the timeline view could answer the information
 need for your query.
-\item Whether the search feature for list view is easy to use?
 \item Whether the search results in the list view could answer the information
 need for your query.
-\item Whether 
+\end{itemize}
+
+Besides, here are the open questions:
+\begin{itemize}
+\item What are the features that you like most? Why?
+\item What are the features that you don't like / hate most? Why?
+\item What features that you would like Crowdy to implement in the future?
+\item Any other comments? 
 \end{itemize}
@@
 system. The interface will be continually improved as it is also an on-going
-DARPA project with the InfoLab. As the next step, a few direction such as user
-model construction and map view implementation will be carried out.
+DARPA project with the InfoLab.
 
 \section{FUTURE WORK}
+There are several natural extensions of this system that we will carry on in the near future.
+Fist of all, we see that building user model may be beneficial to enhance the user experience over different operation sessions.
+Currently, the user behaviors are recorded globally as if there is only one user using Crowdy.
+Once the user model component is implemented, we can seperate individual preference and possibly show the preference of users with different level granularity.
+In addition, we can better learn the user preference as different role and improve our data filtering mechanism accordingly.
+
+Secondly, we will also consider implementing map view.
+The map view can better present the geographical aspect of the crowds.
+As a portion of the tweet data we have crawled contains location information, it would be interesting to show as a map how users in a crowd distribute.
+
+In third, we see a need to contextually summarize the crowds.
+With informative keywords to represent each crowd, we can obtain more valuable search results.
+For example, the search of ``howdy'' should be some crowds with ``howdy'' as the main theme instead of a big crowd with ``howdy'' appears in 1 tweet only.
+Besides, users of the system will be able to distinquish and identify crowds of interest at a first glance.
+This can ease the browsing expereince of users.
 

### 2011-04-28 intake/network.py
fixed import of settings_dev, added title field

@@ -3,7 +3,7 @@ import operator
 from heapq import nlargest
 
 from etc.settings import settings
-from api.models import Crowd, Tweet
+from api.models import Crowd, Tweet, User
 from intake.module import CrowdFilter
 
 
@@ -15,6 +15,7 @@ class CrowdNetworkFilter(CrowdFilter):
             graph = self.make_graph(tweets)
             crowd.clust_coeff = self.clust_coeff(graph)
             self.central_users(crowd, graph)
+            self.set_title(crowd)
             yield crowd
 
     def make_graph(self, tweets):
@@ -33,3 +34,8 @@ class CrowdNetworkFilter(CrowdFilter):
             user['cent']=deg.get(user['id'],0)
         #pick the 10 users with the greatest centrality
         crowd.central_users = nlargest(10, deg.iterkeys(), key=deg.__getitem__)
+
+    def set_title(self, crowd):
+        users = [User.get_id(uid,fields=['sn']) for uid in crowd.central_users[0:3]]
+        crowd.title = ", ".join(u.screen_name for u in users if u)
+        print crowd.title

### 2011-04-28 docs/crowdy_gui.tex
star feature included in report

@@
 In order to provide users a cleaner page view, we restrict 5 tweets per page to show in the slide down box and thus, a multiple page navigation is possible.
+Each crowd has a star-feature attached to it which can be used by the user to mark his favourite crowds.This feature is present in the detailed view of the crowd which is activated as said earlier by selecting the row of a crowd.This is used to rearrange the list of crowds with the starred crowds appearing at the top whenever the user comes back to the list view.The user can mark any crowd as starred or unstar the ones that are already starred at any point of time.
 

### 2011-04-28 intake/search.py
fixed tiny bug in search

@@ -49,7 +49,7 @@ class CrowdIndexFilter(CrowdFilter):
         with CrowdIndexer() as index:
             for crowd in crowds:
                 print "indexing %s"%crowd._id
-                tweets = crowd.tweets(limit=None)
+                tweets = crowd.tweets(limit=0)
                 text = "\n".join(t.text for t in tweets)
                 index.addCrowd(crowd._id,text)
                 yield crowd

### 2011-04-28 intake/network.py
added title to crowds

@@ -36,6 +36,7 @@ class CrowdNetworkFilter(CrowdFilter):
         crowd.central_users = nlargest(10, deg.iterkeys(), key=deg.__getitem__)
 
     def set_title(self, crowd):
-        users = [User.get_id(uid,fields=['sn']) for uid in crowd.central_users[0:3]]
-        crowd.title = ", ".join(u.screen_name for u in users if u)
+        users = (User.get_id(uid,fields=['sn']) for uid in crowd.central_users)
+        names = [u.screen_name for u in users if u][0:2]
+        crowd.title = ", ".join(names+["..."])
         print crowd.title

### 2011-04-28 web/static/scripts/crowd_network.js
change next 5 page style

@@ -164,11 +164,6 @@ function showTweets(list,tweets,users,start,next){
         });
 }
 
-//function nextPage(tweets,users,start){
-//	alert(start)
-//	var nextpage=document.getElementById('next');
-//	nextpage.onclick=showTweets(tweets,users,start);
-//}
 
 function starclick()
 {
@@ -213,7 +208,7 @@ function loadCrowdPopup(cid,elem,users,tweets,star) {
 	showTweets(list,tweets,users,start);
 	start += 5;
 	if(start < tweets.length){
-		next.append("<br><a>Next 5 tweets</a>");
+		next.append("<br><font color='red'><b><u>Next 5 tweets</u></b></font>");
 		next.click(function () { 
 			showTweets(list,tweets,users,start,next);
 			start += 5; 

### 2011-04-28 web/static/scripts/crowd_network.js
changed physics settings to prevent oscillation

@@ -124,7 +124,7 @@ function loadCrowdNetworkGraph(canvas,users,tweets) {
     }
   });
   //start the force directed layout
-  var sys = arbor.ParticleSystem(4000, 500, 0.5, 55)
+  var sys = arbor.ParticleSystem(500, 500, 0.7, 55)
   sys.renderer = Renderer(canvas)
   sys.merge({nodes:nodes, edges:edges})
   sys.parameters({stiffness:600})

### 2011-04-28 docs/crowdy_gui.tex
add snapshot and future work to the report

@@
 shows the set of crowds marked by the user when exploring in the global view
-panel. We have tabs to help our users quickly and easily transit between these
-two views. Inside each view, we need to decide the best format to condense
+panel. Inside each view, we need to decide the best format to condense
 a massive amount of data. Each crowd has metadata associated with it such as
@@
 \begin{itemize}
-    \item \textit{Global View Panel} : The global view shows the global crowds
-    in different format. When a crowded is marked by the user, a flag will be
-    placed in front of each crowd item in each format.
-
-    \begin{itemize}
 				\item Timeline format displays the evolution of each crowd.
@@
         in the pop up box when the user clicks on the crowd line.
+
         \item List format displays each crowd with some specific
@@
         list format, crowds are displayed explicitly in three columns:
-        time period, keywords and some of the participants. The latter
-        two columns are clickable. After clicked, it will show the list
-        of tweets and the full set of participants in a pop up window
+        time period, participants and size of the crowds. If the crowd is clicked, it will show the list
+        of tweets and other detailed information in a slide down window
         form.
-    \end{itemize}
-
-    \item \textit{Personal Workspace Panel} : Similar as the Global View Panel
-    but with only the set of crowds marked by the user in the Global View
-    Panel.
-    \item \textit{Filter Option Panel} : This panel explicitly displays a set of
-    the most frequently used filtering options such as search and timeline scaling.
-    We also provide the user with flexibility to adjust the default
-    settings we provided such as the primary display format in the View
-    Panel, list sorting function and time period filtering. Other filtering
-    options are hidden and can be expanded with a click on the right bottom corner
-    of the Panel.
+%    \item \textit{Global View Panel} : The global view shows the global crowds
+%    in different format. When a crowded is marked by the user, a flag will be
+%    placed in front of each crowd item in each format.
+%
+%    \begin{itemize}
+%        \item Timeline format displays the evolution of each crowd.
+%        First of all, a crowd is shown as a line from the starting time
+%        to the ending time. The size of the participants over time is
+%        indicated by color(e.g., small-large-medium $\longrightarrow$
+%        green-red-blue). The top three keywords that describe the topic of
+%        the crowd are displayed explicitly on the timeline along with
+%        the crowd line. Extra information about the crowd can be viewed
+%        in the pop up box when the user clicks on the crowd line.
+%        \item List format displays each crowd with some specific
+%        sorting order. The default sorting order is by the starting
+%        time. Some other available sorting functions include the
+%        ending time, the size of crowds and the ranging time. In the
+%        list format, crowds are displayed explicitly in three columns:
+%        time period, participants and size of the crowds. If the crowd is clicked, it will show the list
+%        of tweets and other detailed information in a slide down window
+%        form.
+%    \end{itemize}
+%
+%    \item \textit{Personal Workspace Panel} : Similar as the Global View Panel
+%    but with only the set of crowds marked by the user in the Global View
+%    Panel.
+%    \item \textit{Filter Option Panel} : This panel explicitly displays a set of
+%    the most frequently used filtering options such as search and timeline scaling.
+%    We also provide the user with flexibility to adjust the default
+%    settings we provided such as the primary display format in the View
+%    Panel, list sorting function and time period filtering. Other filtering
+%    options are hidden and can be expanded with a click on the right bottom corner
+%    of the Panel.
 \end{itemize}
@@
 
+\begin{figure}
+\centering
+\epsfig{file=img/TimelineView.eps, width= 250pt }
+\caption{Timeline View}
+\label{fig:Timeline View}
+\end{figure}
+
+\begin{figure}
+\centering
+\epsfig{file=img/CrowdViewInTimeline.eps, width= 250pt }
+\caption{Crowd View In Timeline}
+\label{fig:CrowdViewInTimeline}
+\end{figure}
+
 We apply the Simile Timeline library which is developed by MIT's Computer
-Science and Artificial Intelligence Laboratory. The timeline shows all of the
+Science and Artificial Intelligence Laboratory. The timeline as shown in figure \ref{fig:TimelineView} shows all of the
 crowds at a given time span.  The timeline allows the analyist to zoom in on a
@@
 crowd taller or shorter based on the size of the crowd.  We will also display a
-few keywords from each crowd.
+few keywords from each crowd. After a crowd in the timeline is clicked, a pop up ``Crowd View'' window will show the detailed information of this particular crowd (Figure \ref{}).
 
@@
 
-The list view requires a dynamic table in which it displays as many rows as the
-amount of crowds returned by the API. Concretely, we issue a jQuery for all the
-available crowds in the database. The javascript helps to create the dynamic
-table which includes the following columns: Like, Period and number of users in the crowd.
-Users can click on the ``like'' of each crowd to indicate the preference.
-The preferred crowds will be push up to the beginning of the list.
-Once a row of crowd is clicked, a slide down box with detail information(crowd user network, tweets) will be shown below.
-In order to provide users a cleaner page view, we restrict 5 tweets per page to show in the slide down box and thus, a multiple page navigation is possible.
+\begin{figure}
+\centering
+\epsfig{file=img/ListView.eps, width= 250pt }
+\caption{Overall List View}
+\label{fig:ListView}
+\end{figure}
+
+The list view as shown in Figure \ref{fig:ListView} requires a dynamic table in which it displays as many rows as the amount of crowds returned by the API.
+Concretely, we issue a jQuery for all the available crowds in the database.
+The javascript helps to create the dynamic table which includes the following columns: Period, Users and size of the crowd.Once a row of crowd is clicked, a slide down box with detail information(crowd user network, tweets) will be shown below.
+There are three types of information available for users to choose from: Network, Tweets and Graph and a ``star'' mark.
+
 Each crowd has a star-feature attached to it which can be used by the user to mark his favourite crowds.This feature is present in the detailed view of the crowd which is activated as said earlier by selecting the row of a crowd.This is used to rearrange the list of crowds with the starred crowds appearing at the top whenever the user comes back to the list view.The user can mark any crowd as starred or unstar the ones that are already starred at any point of time.
@@
 
+\begin{figure}
+\centering
+\epsfig{file=img/Search.eps, width= 250pt }
+\caption{Search}
+\label{fig:Search}
+\end{figure}
 In the search function of the system, we provide a main search box in which 
@@
 choose options of words, time period of crowd, size of crowd, presentation ways,
-and results they would like to see per page. We maintain indices for each kind
+and results they would like to see per page. The layout is shown in figure \ref{fig:Search}. We maintain indices for each kind
 of queries in the MongoDB database, so that we can efficiently return the results
@@
 \subsubsection{Crowd View}
+
+\begin{figure}
+\centering
+\epsfig{file=img/NetworkInList.eps, width= 250pt }
+\caption{Network View in List}
+\label{fig:NetworkInList}
+\end{figure}
+
+\begin{figure}
+\centering
+\epsfig{file=img/TweetsInList.eps, width= 250pt }
+\caption{Tweets View in List}
+\label{fig:TweetInList}
+\end{figure}
+
+\begin{figure}
+\centering
+\epsfig{file=img/GraphInList.eps, width= 250pt }
+\caption{Graph View in List}
+\label{fig:GraphInList}
+\end{figure}
 When an analyst clicks a crowd in the list, timeline, or map view, we show an
 expanded view of the crowd. This is a form of progressive disclosure, where we
-give the analyst more information as they need it.  At the moment, we just show
-a network graph where nodes represent users, and edges represent the tweets
-between users. We plan to add the ability to drill down even more.  When the
-analyst clicks on a node, we can give the analyst more information about the
-user that was clicked on. When the analyst clicks on an edge, we can show the
-conversation between two users.
+give the analyst more information as they need it.
+
+The default view is the Network information as shown in figure \ref{fig:NetworkInList} where nodes represent users, and edges represent the tweets.
+The network graph show the relationship of the users involved in this particular crowd based on the tweets mentioning activities.
+A thicker edge between two users indicate a tighter mentioning action between them.
+We plan to add the ability to drill down even more.
+When the analyst clicks on a node, we can give the analyst more information about the user that was clicked on.
+When the analyst clicks on an edge, we can show the conversation between two users.
+ %Jeff, would you like to talk more about the network%
+
+In the Tweets tab we can see a set of tweets in this crowd like in figure \ref{fig:TweetInList}.
+In order to provide users a cleaner page view, we restrict 5 tweets per page to show in the slide down box and thus, a multiple page navigation is possible.
+Users can click on the ``Next 5 tweets'' if it is available.
+
+The Graph view shows the activeness of the crowds in an hourly time basis. Figure \ref{fig:GraphInList} gives a crowd graph example. We can see how a crowd start to engage, develop and die over time.
 
@@
 
+Finally, we want to improve the timeline component so it can support zoom in and zoom out functionality for better scaling flexibility.
+For example, crowds within the same day are grouped in the default view.
+The users might want to zoom in and see a hourly-display of crowds in each day or zoom out to browse crowds in each of the 12 months of a year.
+
 \bibliographystyle{abbrv}

### 2011-04-28 docs/crowdy_gui.tex
fixed pilot study

@@
 \section{Evaluation Plan}
-In order to evaluate our system, we planned to conduct a 2-step usability study
+In order to evaluate our system, we plan to conduct a 2-step usability study
 which includes a pilot study, and an evaluation study. In the pilot study, we
@@
 
-The pilot study we propose contains XX 5-scale likert (i.e., very good, good,
-okay, bad, and very bad) questions, and YY open questions. The likert-scale questions
-are listed below:
+The pilot study we propose contains basic demographic information, five questions with a
+five point Likert scale (i.e., strongly agree, agree
+neutral, disagree, and strongly disagree), and four open questions. The
+Likert scale questions are listed below:
 
 \begin{itemize}
-\item Whether the interface for timeline view is easy to use?
-\item Whether the interface for list view is easy to use?
-\item Whether the search feature for timeline view is easy to use?
-\item Whether the search feature for list view is easy to use?
-\item Whether the search results in the timeline view could answer the information
-need for your query.
-\item Whether the search results in the list view could answer the information
-need for your query.
+\item The interface for timeline view is easy to use.
+\item The interface for list view is easy to use.
+\item The search feature for timeline view is easy to use.
+\item The search feature for list view is easy to use.
+\item I could use the search features to find crowds that I was interested in.
 \end{itemize}
 
-Besides, here are the open questions:
+We would also ask some open-ended questions:
 \begin{itemize}
@@
 \item What features that you would like Crowdy to implement in the future?
-\item Any other comments? 
+\item Do you have any other comments? 
 \end{itemize}
+
+Once we have the results of the pilot study, we can refine the test procedures
+and questionnaire. We will run this study on a larger group of poeple.
 

### 2011-04-28 docs/crowdy_gui.tex
added Prateek's questions to likert scale, added info about the network graph

@@
 
-The list view as shown in Figure \ref{fig:ListView} requires a dynamic table in which it displays as many rows as the amount of crowds returned by the API.
-Concretely, we issue a jQuery for all the available crowds in the database.
-The javascript helps to create the dynamic table which includes the following columns: Period, Users and size of the crowd.Once a row of crowd is clicked, a slide down box with detail information(crowd user network, tweets) will be shown below.
-There are three types of information available for users to choose from: Network, Tweets and Graph and a ``star'' mark.
+The list view as shown in Figure \ref{fig:ListView} requires a dynamic table in
+which it displays as many rows as the amount of crowds returned by the API.
+Concretely, we issue an HTTP request to get the crowds in the database in a
+JSON object. The javascript creates the dynamic table which includes the
+following columns: Period, Users and size of the crowd. Once a row of crowd is
+clicked, a slide down box with detail information(crowd user network, tweets)
+will be shown below. There are three types of information available for users
+to choose from: Network, Tweets and Graph and a ``star'' mark.
 
-Each crowd has a star-feature attached to it which can be used by the user to mark his favourite crowds.This feature is present in the detailed view of the crowd which is activated as said earlier by selecting the row of a crowd.This is used to rearrange the list of crowds with the starred crowds appearing at the top whenever the user comes back to the list view.The user can mark any crowd as starred or unstar the ones that are already starred at any point of time.
+Each crowd has a star-feature attached to it which can be used by the user to
+mark his favourite crowds. This feature is present in the detailed view of the
+crowd which is activated as said earlier by selecting the row of a crowd. This
+is used to rearrange the list of crowds with the starred crowds appearing at
+the top whenever the user comes back to the list view. The user can mark any
+crowd as starred or unstar the ones that are already starred at any point of
+time.
 
@@
 
-The default view is the Network information as shown in figure \ref{fig:NetworkInList} where nodes represent users, and edges represent the tweets.
-The network graph show the relationship of the users involved in this particular crowd based on the tweets mentioning activities.
-A thicker edge between two users indicate a tighter mentioning action between them.
-We plan to add the ability to drill down even more.
-When the analyst clicks on a node, we can give the analyst more information about the user that was clicked on.
-When the analyst clicks on an edge, we can show the conversation between two users.
- %Jeff, would you like to talk more about the network%
+The default view is the Network information as shown in figure
+\ref{fig:NetworkInList} where nodes represent users, and edges represent the
+tweets. The network graph show the relationship of the users involved in this
+particular crowd based on the tweets mentioning activities. A thicker edge
+between two users indicates more tweets sent between that pair of users. In the
+future work section of this paper, we discuss ways that this could be improved
+to let the user drill down even more.
 
-In the Tweets tab we can see a set of tweets in this crowd like in figure \ref{fig:TweetInList}.
-In order to provide users a cleaner page view, we restrict 5 tweets per page to show in the slide down box and thus, a multiple page navigation is possible.
-Users can click on the ``Next 5 tweets'' if it is available.
+In the Tweets tab we can see a set of tweets in this crowd like in figure
+\ref{fig:TweetInList}. In order to provide users a cleaner page view, we
+restrict 5 tweets per page to show in the slide down box and thus, a multiple
+page navigation is possible. Users can click on the ``Next 5 tweets'' if it is
+available.
 
-The Graph view shows the activeness of the crowds in an hourly time basis. Figure \ref{fig:GraphInList} gives a crowd graph example. We can see how a crowd start to engage, develop and die over time.
+The Graph view shows the activeness of the crowds in an hourly time basis.
+Figure \ref{fig:GraphInList} gives a crowd graph example. We can see how a
+crowd start to engage, develop and die over time.
 
@@
 
-The pilot study we propose contains basic demographic information, five questions with a
-five point Likert scale (i.e., strongly agree, agree
-neutral, disagree, and strongly disagree), and four open questions. The
-Likert scale questions are listed below:
+The pilot study we propose consists of two parts. First, we will ask the users
+to use our system to find seveal conversations that they find interesting.
+Next, we will use a questionnaire to gather basic demographic information and
+answers to seven questions with a five point Likert scale (i.e., strongly
+agree, agree neutral, disagree, and strongly disagree) and four open questions.
+The Likert scale questions are listed below:
 
@@
 \item I could use the search features to find crowds that I was interested in.
+\item The star feature helped me organize crowds.
+\item When I star a crowd, all the crowds on the page should be re-arranged in real time to place the starred crowd on top.
 \end{itemize}
@@
 
+Fourth, we can make the network view more interactive. For example, when the
+analyst clicks on a node, we can give the analyst more information about the
+Twitter user that was clicked on. When the analyst clicks on an edge, we can show the
+conversation between those two users.
+
 Finally, we want to improve the timeline component so it can support zoom in and zoom out functionality for better scaling flexibility.

### 2011-04-28 docs/crowdy_gui.tex
fixed pics in report

--- 2011-04-28 docs/crowdy_gui.tex
@@
 \centering
-\epsfig{file=img/TimelineView.eps, width= 250pt }
+\includegraphics[width=\linewidth]{imgs/TimeLineView.png}
 \caption{Timeline View}
-\label{fig:Timeline View}
+\label{fig:TimelineView}
 \end{figure}
@@
 \centering
-\epsfig{file=img/CrowdViewInTimeline.eps, width= 250pt }
+\includegraphics[width=\linewidth]{imgs/CrowdViewInTimeLine.png}
 \caption{Crowd View In Timeline}
@@
 crowd taller or shorter based on the size of the crowd.  We will also display a
-few keywords from each crowd. After a crowd in the timeline is clicked, a pop up ``Crowd View'' window will show the detailed information of this particular crowd (Figure \ref{}).
+few keywords from each crowd.
+After a crowd in the timeline is clicked, a pop up ``Crowd View'' window will show the detailed information of this particular crowd (Figure \ref{fig:CrowdViewInTimeline}).
 
@@
 \centering
-\epsfig{file=img/ListView.eps, width= 250pt }
+\includegraphics[width=\linewidth]{imgs/ListView.png}
 \caption{Overall List View}
@@
 \centering
-\epsfig{file=img/Search.eps, width= 250pt }
+\includegraphics[width=\linewidth]{imgs/Search.png}
 \caption{Search}
@@
 Besides, users can also click the link of advanced search, so that they can 
-choose options of words, time period of crowd, size of crowd, presentation ways,
+choose options of words, time period of crowd, size of crowd, value of clustering coefficient of crowds,
 and results they would like to see per page. The layout is shown in figure \ref{fig:Search}. We maintain indices for each kind
@@
 In our future direction, we will also provide query options like location, user's
-screen name. So that users can search crowds that are in a specific city or an 
+screen name, . So that users can search crowds that are in a specific city or an 
 area, and also search crowds that a specific user is involved in.
@@
 \centering
-\epsfig{file=img/NetworkInList.eps, width= 250pt }
+\includegraphics[width=\linewidth]{imgs/NetworkInList.png}
 \caption{Network View in List}
@@
 \centering
-\epsfig{file=img/TweetsInList.eps, width= 250pt }
+\includegraphics[width=\linewidth]{imgs/TweetsInList.png}
 \caption{Tweets View in List}
@@
 \centering
-\epsfig{file=img/GraphInList.eps, width= 250pt }
+\includegraphics[width=\linewidth]{imgs/GraphInList.png}
 \caption{Graph View in List}

### 2011-04-28 docs/crowdy_gui.tex
fixed spelling

--- 2011-04-28 docs/crowdy_gui.tex
@@
 it is not a part of this project, it is important to understand how the backend
-works, and how it fits into this project. The workflows of the system can be
+works, and how it fits into this project. The work flows of the system can be
 decomposed into following parts: (i) a crawler retrieves tweets from Twitter using
@@
 Science and Artificial Intelligence Laboratory. The timeline as shown in figure \ref{fig:TimelineView} shows all of the
-crowds at a given time span.  The timeline allows the analyist to zoom in on a
+crowds at a given time span.  The timeline allows the analyst to zoom in on a
 specific time, and move forward and backward thorough time.  The visualization
@@
 Concretely, we issue an HTTP request to get the crowds in the database in a
-JSON object. The javascript creates the dynamic table which includes the
-following columns: Period, Users and size of the crowd. Once a row of crowd is
+JSON object. The Javascript creates the dynamic table which includes the
+following columns: Period, Users and size of the crowd. We pick the screen
+names of two users with the highest degree centrality to represent the crowd.
+Once the row that represents a crowd is
 clicked, a slide down box with detail information(crowd user network, tweets)
@@
 Each crowd has a star-feature attached to it which can be used by the user to
-mark his favourite crowds. This feature is present in the detailed view of the
+mark his favorite crowds. This feature is present in the detailed view of the
 crowd which is activated as said earlier by selecting the row of a crowd. This
@@
 will ask a relative small number of users (e.g., 5 - 10 people) to try our
-system, and fill in the usability questionaire. Then, we will refine the system
-based on the feedbacks from the pilot study (i.e., fixing bugs reported by users,
-modifying featuers that were not preferred). Finally, a large scale evaluation
-study also in the form of questionaire will be conducted on a user base of 30 -
+system, and fill in the usability questionnaire. Then, we will refine the system
+based on the feedback from the pilot study (i.e., fixing bugs reported by users,
+modifying features that were not preferred). Finally, a large scale evaluation
+study also in the form of questionnaire will be conducted on a user base of 30 -
 50 users including three types of users we mentioned earlier: normal users, 
@@
 The pilot study we propose consists of two parts. First, we will ask the users
-to use our system to find seveal conversations that they find interesting.
+to use our system to find several conversations that they find interesting.
 Next, we will use a questionnaire to gather basic demographic information and
@@
 Once we have the results of the pilot study, we can refine the test procedures
-and questionnaire. We will run this study on a larger group of poeple.
+and questionnaire. We will run this study on a larger group of people.
 
@@
 Currently, the user behaviors are recorded globally as if there is only one user using Crowdy.
-Once the user model component is implemented, we can seperate individual preference and possibly show the preference of users with different level granularity.
+Once the user model component is implemented, we can separate individual preference and possibly show the preference of users with different level granularity.
 In addition, we can better learn the user preference as different role and improve our data filtering mechanism accordingly.
@@
 For example, the search of ``howdy'' should be some crowds with ``howdy'' as the main theme instead of a big crowd with ``howdy'' appears in 1 tweet only.
-Besides, users of the system will be able to distinquish and identify crowds of interest at a first glance.
-This can ease the browsing expereince of users.
+Besides, users of the system will be able to distinguish and identify crowds of interest at a first glance.
+This can ease the browsing experience of users.
 

### 2011-04-29 docs/crowdy_gui.tex
Fixed final report and submitted to the Ship.

@@
 Apart from the original Twitter interface that provides only a local view of
-the most current tweets issued by each user's followee or some local trending
+the most current tweets issued by each user's friends or some local trending
 topics, our final system should be able to aggregate the data to find global,

### 2011-05-03 docs/csce_675/paper.tex
Added latex for paper.

\documentclass{sig-alternate}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{definition}{Definition}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{proposition}{Proposition}[section]
\newtheorem{problem}{Problem}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{subfigure}
\usepackage{verbatim} 
% \usepackage[small,compact]{titlesec}
\pdfpagewidth=8.5in
\pdfpageheight=11in
%\usepackage[small,it]{caption}
\newcommand{\squishlist}{
 \begin{list}{$\bullet$}
  { \setlength{\itemsep}{0pt}
     \setlength{\parsep}{3pt}
     \setlength{\topsep}{3pt}
     \setlength{\partopsep}{0pt}
     \setlength{\leftmargin}{1.5em}
     \setlength{\labelwidth}{1em}
     \setlength{\labelsep}{0.5em} } }

\newcommand{\squishlisttwo}{
 \begin{list}{$\bullet$}
  { \setlength{\itemsep}{0pt}
     \setlength{\parsep}{0pt}
    \setlength{\topsep}{0pt}
    \setlength{\partopsep}{0pt}
    \setlength{\leftmargin}{2em}
    \setlength{\labelwidth}{1.5em}
    \setlength{\labelsep}{0.5em} } }

\newcommand{\squishend}{
  \end{list}  }

%\setlength{\abovecaptionskip}{0pt}
%\setlength{\belowcaptionskip}{0pt}

\begin{document}

\title{A Digital Library for Crowds on the Real-Time Social Web}

\numberofauthors{2} 
\author{
\alignauthor Jeff A. McGee\\
       \affaddr{Texas A\&M University}\\
       \affaddr{College Station, TX 77843}\\
       \email{jeffamcgee@gmail.com}
\alignauthor Krishna Y. Kamath\\
      \affaddr{Texas A\&M University}\\
       \affaddr{College Station, TX 77843}\\
       \email{kykamath@cs.tamu.edu}
}

\maketitle

\begin{abstract}
In this project, we want to build a digital library for transient crowds in highly-dynamic social messaging systems like Twitter and Facebook. A crowd is a short-lived ad-hoc collection of users, representing a ``hot-spot'' on the real-time web.  For example, an event like super-bowl might result in formation of crowds that are discussing various happenings in the game. Successful detection of these hot-spots can positively impact related research directions in online event detection, content personalization, social information discovery, etc. We will build a framework that allows an analyst or curious user to find interesting crowds and see how they evolve.  This framework will have three main parts: a database to store crowds, users, and their messages; a set of crowd detection algorithms and filters; and a tool for searching for crowds by topic, geography, or user-name.
\end{abstract}

\section{Introduction}

\section{Related Work}
\label{sec:reclated_work}

\section{Architecture}
\label{sec:architecture}
\begin{figure}[!t]
\begin{center}
\includegraphics[width=3.0in]{images/architecture}
\caption{Examples for trending phrases discovery problem.}
\label{fig:candidate_phrases}
\end{center}
\end{figure}

\section{Crowd Discovery Algorithm}
\label{sec:crowd_algorithm}

The grouper deals with the transient crowd discovery and tracking in systems like Facebook and Twitter. For practical crowd discovery and tracking in a large time-evolving communication network, however, we face four key challenges:

\begin{list}{\labelitemi}{\leftmargin= 0.3cm}

\item First, systems like Facebook and Twitter are extremely large (on the order
of 100s of millions of unique users), placing huge demands on the computational
cost of traditional community detection approaches (which can be $O(n^3)$ in the
number of users \cite{flake:cut-clustering}).

\item Second, these services support a high-rate of edge addition (new
messages) so the discovered crowds may become stale quickly, resulting in the need to
re-identify all crowds at regular intervals (again, incurring the high cost of
community detection). The bursty nature of user communication demands a crowd
discovery approach that can capture these highly-temporal based clusters.

\item Third, the strength of association between two users may depend on many
factors (e.g., recency of communication), meaning that a crowd discovery approach
based on graph clustering should carefully consider edge weights. With no decay
at all (meaning that edges are only inserted into the network but never removed),
all users will tend towards a single trivial large crowd. Conversely, overly
aggressive edge decay may inhibit any crowd formation at all (since edges between
users may be removed nearly as soon as they are added).

\item Fourth, crowds may evolve at different rates, with some evolving over
several minutes, while others taking several days. Since crowds are inherently
ad-hoc (without unique community identifiers -- e.g., Fans of LA Lakers), the
formation, growth and dispersal of crowds must be carefully managed for
meaningful crowd analysis.
\end{list}

With these challenges in mind, we propose to discover and track transient crowds
through a communication based clustering approach over time-evolving
graphs that captures the natural conversational nature of social messaging
systems. Two of the salient features of the proposed approach are (i) an
efficient locality-based clustering approach for identifying crowds of users in
near real-time compared to more heavyweight static clustering algorithms; and
(ii) a novel crowd tracking and evolution approach for linking crowds across time
periods.

To support transient crowd discovery in Twitter-like services with 100s of
millions of participants, we propose to leverage the inherent locality in social
messaging systems. Concretely, we identify two types of locality that are
evident in Twitter-like messaging systems: (i) temporal locality and (ii) spatial
locality.

\medskip \noindent\textbf{Temporal Locality:} Transient crowds are
intuitively short-lived, since they correspond to actively communicating groups
of users. Hence, the composition of a crowd at a point-in-time should be impacted
by recent messages as opposed to older messages. As more users interact with the
crowd, the crowd should grow reflecting this \textit{temporal locality} and then
shrink as users in the crowd become inactive (that is, their last communication
with the crowd becomes more distant in time).

\medskip \noindent \textbf{Spatial Locality:} Intuitively, transient crowds are
made up of a very small percentage of users compared to the entire population of
the social network. Hence, new messages (corresponding to the addition of edges
to the communication network) should have only a local influence on the crowds
that exist at any given time. That is, changes in a small region of a graph
should not affect the entire graph. In a dataset of 61 million Twitter messages
described in \cite{Kamath:2011:TCD}, we have confirmed the existence of
this \textit{spatial locality} by finding that only about 1\% of users are within
two hops, meaning that an edge insertion has only a local effect.

\medskip Hence, we can take advantage of both, local changes to the overall
communication network (spatial locality) and recent changes to the network
(temporal locality), for supporting efficient transient crowd discovery. The complete algorithm is decsribed in \cite{Kamath:2011:TCD}

\section{Conclusion}
\label{sec:conclusion}

\end{document}

### 2011-05-03 docs/csce_675/sig-alternate.tex
Added latex for paper.

\documentclass{sig-alternate}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{subfigure}
\pdfpagewidth=8.5in
\pdfpageheight=11in
\usepackage[small,it]{caption}
\newcommand{\squishlist}{
 \begin{list}{$\bullet$}
  { \setlength{\itemsep}{0pt}
     \setlength{\parsep}{3pt}
     \setlength{\topsep}{3pt}
     \setlength{\partopsep}{0pt}
     \setlength{\leftmargin}{1.5em}
     \setlength{\labelwidth}{1em}
     \setlength{\labelsep}{0.5em} } }

\newcommand{\squishlisttwo}{
 \begin{list}{$\bullet$}
  { \setlength{\itemsep}{0pt}
     \setlength{\parsep}{0pt}
    \setlength{\topsep}{0pt}
    \setlength{\partopsep}{0pt}
    \setlength{\leftmargin}{2em}
    \setlength{\labelwidth}{1.5em}
    \setlength{\labelsep}{0.5em} } }

\newcommand{\squishend}{
  \end{list}  }

\setlength{\abovecaptionskip}{0pt}
\setlength{\belowcaptionskip}{0pt}

\begin{document}

\title{CrowdBuzz: Trend Discovery and Evolution in \\Social Messaging Systems}

\numberofauthors{2} 
\author{
\alignauthor Krishna Y. Kamath\\
       \affaddr{Texas A\&M University}\\
       \affaddr{College Station, TX 77843}\\
       \email{kykamath@cs.tamu.edu}
\alignauthor James Caverlee\\
       \affaddr{Texas A\&M University}\\
       \affaddr{College Station, TX 77843}\\
       \email{caverlee@cse.tamu.edu}
}

\maketitle
\begin{abstract}
In this paper, we study the problem of automatically discovering and tracking the evolution of \textit{group-based trends} in highly-dynamic social messaging systems like Twitter and Facebook. Unlike trend-tracking systems that aggregate individual actions or posts (e.g., counting tweets including the phrase ``super bowl''), we are interested to track the conversational communication-based patterns across groups of users. These ad-hoc ``crowds'' of users provide an opportunity to identify emergent crowd-based topics of interest that reflect the natural conversational nature of social messaging systems. Two of the salient features of the proposed approach are (i) an efficient locality-based clustering approach for identifying crowds of users in near real-time compared to more heavyweight static clustering algorithms; and (ii) a crowd tracking and evolution approach for linking crowds across time periods. We find that the locality-based clustering approach results in empirically high-quality clusters relative to static graph clustering techniques at a
fraction of the computational cost. Based on a three month snapshot of Twitter consisting of
 711,612 users and 61.3 million messages, we show how the proposed approach can
identify and track interesting crowds based on the Twitter communication structure and find crowd-based topics of interest.

%At its core, CrowdBuzz relies on two key components: (i) an online graph clustering component for identifying important crowds at a particular time based on messages sent between users; and (ii) a crowd tracking and evolution component for linking crowds across time periods. One of the novel contributions of CrowdBuzz is its online social graph clustering approach that is inspired by the Min-Cut graph clustering algorithm for static graphs. 
% and topics that generate high crowd interest (but little individual interest),
% and topics that generate high individual interest (but little crowd interest).
\end{abstract}

\section{Introduction}
\label{sec:introduction}
With the rise of large-scale online social networks, there has been a growing
interest in mining these networks for information discovery, brand management
(e.g., what are users saying about the new iPhone), and other data mining
applications \cite{guo:pattern, zheleva:affiliation, cha:filkr, matsuo:gravity}.
The past few years have seen the development of a number of successful
tools for aggregating online \textit{buzz} (e.g., BlogPulse
\cite{website.blogpulse}, BlogScope \cite{bansal:blogscope}, Meme-tracker
\cite{leskovec:meme}).
% Similarly, Facebook
% has deployed the Lexicon tool for aggregating the posts of users in their social
% network, to reveal how many users are posting about particular topics and give
% insight into the general mood of the network.  
In a related direction, Google
Trends aggregates individual user search queries to provide important insights
into rising or falling issues (e.g., health care, queries like ``coupon'' that
may help predict the direction of the economy \cite{choi:google}), comparison of
subjects (e.g., ipod versus zune, federer versus nadal). These trend discovery
tools are even showing promise for public health and disaster recovery efforts
(e.g., Google Flu Trends).

%In most of these example systems, buzz is a function of the aggregated actions of many individuals, e.g., by counting the number of people searching for ``zune'' or the number of Facebook members posting about ``ipods''. This type of trend analysis is fundamentally \textit{user-centric} by tracking the aggregate of posts from many individuals.

In many trending systems, a given term $t$ is often tracked over the aggregate of many individual actions or posts, e.g., by counting the number of people searching for ``zune'' or the number of Facebook members posting about ``ipods''. However, these systems may overlook \textit{conversations} occurring between participants that are related to the topic but don't necessarily include the actual term being trended over. In addition, the conversational buzz associated with users actually communicating with each other directly about a topic may be a strong indicator of an emergent online phenomenon worth identifying. Discovering these conversational groupings (what we call \textit{crowds}) can support crowd-based trending topics in addition to the more traditional individual-based trending topics.  %The topics can be given their own weight, just as in the user-centric model, based on several factors of the crowd.

%talking to each other may

%``crowd'' is a strong indicator of an emergent online phenomenon that may be worth identifying and directing to interested users.

%This type of trend analysis is fundamentally \textit{user-centric}. With the inherent social-based connectivity in social media, we are interested to examine the communication patterns between users and how these communication patterns may support a \textit{group-centric} notion of buzz. Fundamentally, the group-centric approach, shown in Figure~\ref{fig:single-multi}, seeks to capture the organic buzz that occurs when groups of people talk amongst themselves.
% ; in contrast the
% user-centric approach is typically a one-sided affair, capturing user monologues
% and not necessarily the natural back-and-forth of natural communication among
% users participating in a group.

%Our fundamental insight is that ``crowd''-based emergent information holds the key to effective personalized dissemination of interesting and relevant real-time web information. A single user action -- for example, posting a picture of a smoke plume to Flickr -- though perhaps interesting itself, does not convey a strong community or social-based importance to the user action. In contrast, a flurry of activity associated with a ``crowd'' is a strong indicator of an emergent online phenomenon that may be worth identifying and directing to interested users. Identifying coherent crowds in real-time across a potentially vast collection of non-obviously connected user actions is a major challenge.

But how do we identify \textit{conversations} in the first place? Historically, direct communication between people has been mostly unobservable or
unavailable for analysis by large-scale aggregation services. For example,
private email and instant messages between two users are typically not made
available for natural reasons. But with the rise of new social messaging systems
like Twitter and Facebook, communications between users can be monitored. For example, Twitter
supports the public messaging of users through the inclusion of $@\langle username \rangle$
in a Twitter post (a ``tweet''). So a tweet from the user \textit{nod} can be
addressed to the user \textit{kykamath} like so: ``@kykamath What do you think
about the new iPod?''. This type of observable communication is on the rise and a
significant portion of all messages posted on Twitter, with estimates placing the
percent of all tweets containing the $@\langle username \rangle$  at 30\% (or about 7 million
observable communications per day) \cite{website.gigatweet}. Similar messaging
functionality has recently been adopted by Facebook.

Given these observable communication patterns, we are interested to explore whether we can identify ad-hoc crowds of
users that reflect the real-time interests and affiliations of users? Unlike the
more static and perhaps staler group-based membership offered on many social
networks (e.g., member of Texas A\&M community), this type of 
% , fan of college football),
communication-based crowd discovery promises organic and highly-temporal group
interest identification. 
% Compared to traditional social mining approaches which
% aggregate individual user keywords, by discovering crowds of users based on their
% interactions, we may discover organic linkages among the users. 
% Similarly,
% crowd-based buzzworthy topics may indicate a depth of interest in a subject that
% is not reflected in the straightforward aggregation of user keywords in
% undirected public pronouncements (e.g., status updates, blog
% posts).
However identifying crowds is challenging. Social messaging systems like Twitter
and Facebook have potentially 100s of millions of communicating users inserting
new messages into the system at a high-rate. Even if we can identify a crowd at a
point-in-time, we must additionally track the crowd over time as users join,
multiple crowds merge, and as crowds disband. To deliver up-to-date  crowd
information to group-based trending tools and social mining analytics, the discovery and evolution
approaches must support efficient and near real-time execution.

With these opportunities and challenges in mind, we study the problem of automatically discovering and tracking the evolution of \textit{group-based trends} in highly-dynamic social messaging systems like Twitter and Facebook. Concretely, we propose an efficient locality-based clustering approach for identifying crowds of users in near real-time compared to more heavyweight static clustering algorithms. This locality-based approach relies on the spatial and temporal locality evident in systems like Twitter. Additionally, we propose a crowd tracking and evolution approach for linking crowds across time periods according to varying degrees of evolution granularity (e.g., for tracking very bursty crowds that grow and disperse over several hours versus longer-lived crowds that may last for weeks). Based on a one-week snapshot of Twitter consisting of 706,000 users and 20.3 million messages, we find that the locality-based clustering approach results in empirically high-quality clusters relative to static graph clustering techniques at a fraction of the computational cost. We also  illustrate how the proposed approach can identify and track interesting crowds based on the Twitter communication structure and find crowd-based topics of interest.

% CrowdBuzz relies on two key components: (i) a dynamic graph clustering component for identifying important crowds at a  particular time based on messages sent between users; and (ii) a crowd tracking and evolution component for linking crowds across time periods.  One of the novel  contributions of CrowdBuzz is its dynamic social graph clustering approach that is inspired by the Min-Cut graph clustering algorithm for static graphs. We find  that the dynamic graph clustering component results in empirically high-quality  clusters relative to static graph clustering techniques at a fraction of the  computational cost. Based on a one-week snapshot of Twitter consisting of 250,000  users and 1.2 million messages, we show how CrowdBuzz can identify interesting  crowds based on the Twitter communication structure, topics that generate high  crowd interest (but little individual interest), and topics that generate high  individual interest (but little crowd interest).

%In this paper, we study the problem of automatically discovering and tracking the evolution of \textit{group-based trends} in highly-dynamic social messaging systems like Twitter and Facebook. Unlike trend-tracking systems that aggregate individual actions or posts (e.g., counting tweets including the phrase ``super bowl''), we are interested to track the conversational communication-based patterns across groups of users. These ad-hoc ``crowds'' of users provide an opportunity to identify emergent crowd-based topics of interest that reflect the natural conversational nature of social messaging systems. Two of the salient features of the proposed approach are (i) an efficient locality-based clustering approach for identifying crowds of users in near real-time compared to more heavyweight static clustering algorithms; and (ii) a crowd tracking and evolution approach for linking crowds across time periods. We find that the locality-based clustering approach results in empirically high-quality clusters relative to static graph clustering techniques at a fraction of the computational cost. Based on a one-week snapshot of Twitter consisting of 706,000 users and 20.3 million messages, we show how the proposed approach can identify and track interesting crowds based on the Twitter communication structure and find crowd-based topics of interest.

%At its core, CrowdBuzz relies on two key components: (i) a dynamic graph clustering component for identifying important crowds at a particular time based on messages sent between users; and (ii) a crowd tracking and evolution component for linking crowds across time periods. One of the novel contributions of CrowdBuzz is its dynamic social graph clustering approach that is inspired by the Min-Cut graph clustering algorithm for static graphs. We find that the dynamic graph clustering component results in empirically high-quality clusters relative to static graph clustering techniques at a fraction of the computational cost. Based on a one-week snapshot of Twitter consisting of 250,000 users and 1.2 million messages, we show how CrowdBuzz can identify interesting crowds based on the Twitter communication structure, topics that generate high crowd interest (but little individual interest), and topics that generate high individual interest (but little crowd interest).

% (i) a dynamic graph clustering component for identifying important crowds at a
% particular time; (ii) a crowd tracking and evolution component for linking
% clusters across time periods; and (iii) a crowd visualization and analytics
% component

\begin{figure}[!t]
\begin{center}
\includegraphics[width=3.5in]{../../images/cikm2010/intro}
\caption{Example of crowd discovery in twitter. The table shows the
interactions of users at different time intervals and the corresponding crowds
discovered.}
\label{fig:intro-example}
\end{center}
\end{figure}

\subsection{Crowd Discovery Example}
An example of crowd discovery based on communication between users is shown in
Figure. \ref{fig:intro-example}. The second column in the table shows the
twitter messages sent between users and the third column shows the communication
graph for the interval. To keep the example simple we use the number of
messages transmitted between users as edge weights in the communication
graph and reduce the weight by 1 if no messages are sent in a particular time
interval. The weight is reduced to remove stale users from a crowd. The actual
algorithm in the paper uses a more complex edge weight scheme. The last
column shows the corresponding crowds discovered. In our algorithm we use
graph clustering to identify crowds. But, to simplify this example we use graph
connectivity to identify crowds.

In the first time interval 2 messages are exchanged between A-B and C-D. The
communication graph obtained is shown in the third column. The interaction
between users results in creation of 2 crowds as shown. In the next interval A
and C communicate with each other. This results in the 2 crowds merging
together to form a single crowd. In a real crowd users who do not get
involved in the discussion get bored and move away from the crowd. In the
$3^{rd}$ interval, we observe that user D who has not interacted with rest of
the users for sometime is removed from the crowd and froms a singleton. Finally in
the $5^{th}$ interval user C, like D before, breaks from the crowd and form a
singleton. Thus based on the user communication we can determine user crowds.

\section{Twitter Dataset}
To study crowd detection in a real-world setting, we focus on the Twitter
microblogging service. Through a mix of crawling and API calls to the Twitter
service, we collected a sample of tweets from October $1^{st}$ to December
$31^{st}$, 2008, accounting for 2208 hours (see Table~\ref{table:dataset} for
details). The dataset includes over 710,000 users and over 61.3 million status
updates (``tweets'') of 140 characters or less. Users can annotate their tweets
via the inclusion of hashtags (e.g., ``\#redsox'') to indicate a particular
topic. Similarly, users can include \textit{@mentions} of the form $@\langle
username \rangle$ within a tweet to reference another user. While these
\textit{@mentions} can serve many purposes, the most popular use is as a simple
messaging framework, so that a message posted by user $u_1$ including @$\langle
u_2 \rangle$ is considered a message from $u_1$ to $u_2$.
% (note that users other than $u_2$ may view this public message as well).

\begin{table}[h]
\centering
\label{table:dataset}
\begin{tabular}{|l|r|r|}
\hline
\textbf{Property} & \textbf{Total} & \textbf{Per hour avg.} \\ \hline
Users & 711,612 & 18,713 \\ \hline
Total tweets & 61,314,203 & 27,769 \\ \hline
Messages (@$<u>$) & 20,394,030 & 9,236\\ \hline
User pairs & 3,756,619 & 9,310\\ \hline
% Average degree & 3.48 & - \\ \hline
\end{tabular}
\caption{Twitter dataset properties.}
\end{table}

Of the, 61.3 million tweets in the dataset, 20.4 million contain the $@\langle
username \rangle$ syntax and are considered messages from one user to another.
3.7 million pairs of users are connected by these messages. The hourly
distribution of tweeting users, user pairs, and messages sent is shown in
Figure~\ref{fig:data-distribution}. All are strongly correlated, following a
clear daily and weekly patterns.

\begin{figure}[!t]
\begin{center}
\includegraphics[width=3.5in]{../../images/cikm2010/userInteractions}
\caption{Oct 1 - Dec 31, 2008: Number of users, the number of pairs of users
who have at least one message between them, and the number of messages sent.}
\label{fig:data-distribution}
\end{center}
\end{figure}

%In addition, we observe that messages on Twitter display strong temporal and spatial locality. By \textit{temporal locality}, we mean that messages  BLAH BLAH BLAHB. By \textit{spatial locality}, we mean that messages in the BLAH BLABH ALBHA LBHABH ALBHALBHA BLHA. BLAH BLABH ALBH ABLH ALBHA.  Approximately 1\% of nodes impacted

\section{Problem Statement}
Given the large and growing size of social messaging systems like Twitter and Facebook,  we are interested to explore group formation in these systems and how this group formation can impact the detection of online trends.  Users may be grouped along a number of dimensions including content-based, geographic-based, communication-based, and so on. We focus on the challenge of uncovering and tracking groups of users -- what we refer to as \textit{crowds} -- according to their communication patterns. Intuitively, a crowd is a time-sensitive collection of users who have messaged each other within some recent window of time. Based on the communication patterns, we hope to identify organic \textit{conversations} occurring between participants for identifying trends.

%are related to the topic but don't necessarily include the actual term being trended over.

%In many trending systems, a given term $t$ is often tracked over the aggregate of many individual actions or posts, e.g., by counting the number of people searching for ``zune'' or the number of Facebook members posting about ``ipods''. However, these systems may overlook \textit{conversations} occurring between participants that are related to the topic but don't necessarily include the actual term being trended over.  Our system is group-centric in that we seek to discover crowds based on conversation patterns, and then from that crowd, we derive trending topics.

%\squishlist
%\item \textit{Interest-based grouping}: Reflecting groups of users who share a common interest, e.g., users posting messages about a presidential debate.
%\item \textit{Geographic-based grouping}: Reflecting groups of users who are geographically bounded, e.g., users posting messages from Dallas, Texas.
%\item \textit{Communication-based grouping}: Reflecting groups of users who are actively messaging each other, e.g., users coordinating a meeting.
%\squishend

Formally, we view the users and their communications with other users in a social messaging
system as a \textit{time-evolving communication network}. Let $G(V,E)$ be an
undirected graph with $|V| = n$ vertices and $|E| = m$ edges, where each vertex
corresponds to a user in the social messaging system and an edge corresponds to a
communication between two users. The weight of an edge between vertices $u$ and
$v$ is represented by $w(u, v)$. Each edge is associated with the time of the last communication between two users: $EdgeTime(u,v)$.  Additionally, we will view the graph $G$ as the adjacency list $A$, where $A(u, v) = w(u, v)$ if $(u, v)$ exists, else $A(u, v) = 0$.

Viewing a social messaging system like Twitter as a time-evolving communication network, we face two key challenges:

%Communication patterns These crowds of users are intended to reflect

%can be further refined by \textit{interest-based grouping} 
%Users may be grouped along a number of dimensions, including (but not limited to):

%\squishlist
%\item \textit{Interest-based grouping}: Reflecting groups of users who share a common interest, e.g., users posting messages about a presidential debate.
%\item \textit{Geographic-based grouping}: Reflecting groups of users who are geographically bounded, e.g., users posting messages from Dallas, Texas.
%\item \textit{Communication-based grouping}: Reflecting groups of users who are actively messaging each other, e.g., users coordinating a meeting.
%\squishend
%By considering the content similarity of user tweets via standard information retrieval techniques or by probabilistic topic models (e.g., LDA \cite{}), users can be grouped according to their interests -- e.g., sports, bLAH, Blah.

\textbf{Challenge \#1: Crowd Discovery.}  The first challenge is to identify a set of crowds at any moment in time. Social messaging systems like Facebook and Twitter are extremely large (on the order of 100s of millions of unique users), placing huge demands on the computational cost of traditional community detection approaches (which can be $O(n^3)$ in the number of users). And since these services are characterized by a
high-rate of messages, the discovered crowds may become stale quickly, resulting in the need to re-identify crowds (again, incurring the high cost of community detection).

\textbf{Challenge \#2: Crowd Evolution.} In addition to identifying crowds at any moment in time, the second challenge is to track the evolution of crowds across time. For example, as groups of users begin communicating about an upcoming event (say the Super Bowl), the evolution approach should can track the users participating in this crowd and give
insights into the crowd dynamics leading up to and after the event. Since crowds may evolve at different rates, we must be careful in tracking bursty crowds that grow and disperse over several hours versus longer-lived crowds that may last for weeks.

%However, the bursty nature of user communication places demands on crowd evolution to accurately track these highly-temporal based clusters.

%Evolution module can analyze the discovered crowds from the previous module at system-specified time intervals to provide varying degrees of evolution granularity (e.g., for tracking very bursty crowds that grow and disperse over several hours versus longer-lived crowds that may last for weeks).

%dynamic clustering \cite{saha:clustering,gorke:clustering}, etc.

%In the context of real-time crowd discovery in social messaging systems, however, these graph clustering approaches face challenges.

%he groups of users discussing the event, until a peak during the event, and finally the ...

%The function of this module is to build a hierarchy of clusters called cluster hierarchy graph. This module accepts a set of clusters $K_s$ at time $t_s$ from the clustering module and for every cluster $C_c$ in $K_s$ it then determines its parent cluster $C_p$ in $K_{s-1}$, if it exists. It then adds an edge between the two clusters $C_c$ and $C_p$. The algorithm to build a hierarchy graph is given in Section~\ref{sub-sec:hierarchy-graph}.

%\subsection{Approach:}
%crowd discovery
%crowd evolution

%Output of this module is the current set of clusters maintained by the clustering algorithm. It sends this out to the next module at regular intervals.

% ... This is the central module in our architecture. We will be using an online
% clustering algorithm in this module. Online and offline algorithms expect same
% input to be give in different formats. An offline algorithm requires entire
% input to be available before start of the algorithm, while an online algorithm
% can process input as it arrives piece-by-piece. Since our application doesn't
% have entire input initially, we use an online algorithm. The  motivation and
% details of this algorithm are given in Section~\ref{sec:graph-clustering}.

% The online clustering algorithm continuously maintains a set of clusters for
% the current set of vertices. Any time an edge is added, the algorithm updates
% the set of clusters accordingly. The clustering module takes a tuple $(u_1,
% u_2, m)$ as input. Since, we will be using graph theoretic approach to
% clustering, it maps every user $u$ to a vertex $v$ and the tuple to an edge
% $e$.  The module then uses {\scshape AddEdge}$(v_1, v_2, w)$ procedure to pass
% the newly added edge $e$ to the online clustering algorithm. The procedure
% {\scshape AddEdge}$(v_1, v_2, w)$ is described in the
% Section~\ref{sec:graph-clustering}.

% Output of this module is the current set of clusters maintained by the
% clustering algorithm. It sends this out to the next module at regular
% intervals. This is shown in Figure~\ref{fig:architecture}, where output from
% clustering module is sent to the hierarchy generator module at regular
% intervals $t_1, t_2, t_3 \ldots t_s$.

%\cite{saha:clustering,THAT NEW DYNAMIC CLUSTERING PAPER}

\section{Crowd Discovery and Evolution}
\label{sec:crowd-discovery}
In an effort to tackle these challenges, we propose an efficient locality-based
crowd discovery and evolution approach. We view crowd discovery as a form of
\textit{clustering in time-evolving communication networks}. Formally, a crowd
$C$ is a set of vertices and $K$ is the set of all crowds in $G$. $C_i$
represents the $i^{th}$ crowd in $K$. Vertices are assigned to one and only one
crowd, i.e., $ C_i \cap C_j = \phi, \forall C_i, C_j \in K$. To identify crowds,
we can directly use of many existing approaches, including spectral clustering
\cite{dhillon:multilevel}, min-cut clustering \cite{flake:cut-clustering}, among
many others. In practice, however, these and related graph clustering approaches
can be $O(n^3)$ in the number of nodes (users in our case), which is unreasonable
considering the large size of Twitter and the needs of trend-based applications
to identify crowds in near real-time. To overcome these issues, we rely on two
key insights:

\squishlist

\item  First, the addition of a new edge to the time-evolving communication network $G$ (i.e., a new message from one user to another at time $t$) should only impact a small number of crowds and not the entire graph. We have confirmed this \textit{spatial locality} on Twitter: for each new message observed in our dataset (corresponding to an edge insertion in the communication network), we find that only about 1\% of users are within two hops, meaning that an edge insertion has only a local effect. Hence, we can leverage this spatial locality of impact to reduce the cost of updating all crowds in the network.

\item Second, messages in the social messaging system should impact the time-evolving communication network based on their recency, with older messages having less impact on the discovered crowds than do more recent messages. We refer to this emphasis on the present as \textit{temporal locality} to indicate the degree to which past messages can influence the current state of crowds.

\squishend

%In the following ...

%that edge weights should reflect temporal locality (e.g., decaying based on communication recency).  the strength of association between two users in a social messaging system may depend on the recency of their communication (e.g., a message from $u_1$ to $u_2$ today should be considered a stronger signal of their common crowd membership than a message from $u_1$ to a third user $u_3$ a month ago), meaning that a crowd discovery approach based on graph clustering should carefully consider how to decay edge weights

%Third, the strength of association between two users in a social messaging system may depend on the recency of their communication (e.g., a message from $u_1$ to $u_2$ today should be considered a stronger signal of their common crowd membership than a message from $u_1$ to a third user $u_3$ a month ago), meaning that a crowd discovery approach based on graph clustering should carefully consider how to decay edge weights. Fourth, the bursty nature of user communication demands a crowd discovery approach that can capture these highly-temporal based clusters.

%In this section we present the approach to discover user crowds. We first
%show an example of crowd discovery and then formally describe the problem and
%the algorithms used to discover crowds.

%[NEW] Based on these observations, we propose a new class of highly-efficient locality-based clustering algorithms. Locality-based clustering is developed on the notions that (i) changes in a small region of a graph should not affect the entire graph;  and (ii) that edge weights should reflect temporal and interest locality (e.g., decaying based on communication recency).

%Compared to min-cut clustering \cite{flake:cut-clustering} and related approaches (with $O(n^3)$ time complexity), this locality-based approach can result in $O(k^3)$ complexity, where $k$ is the largest crowd size in $K$.

%Similarly, every crowd $C$ is associated with the time of last communication of any of its users $ClusterTime(C)$

% \begin{itemize}

% \end{itemize}

% In the following three sections, we present these three BLAH BLA HBALHB.

%Recently, there has been some work examining dynamic graph clustering with provable quality guarantees \cite{saha:clustering,THAT NEW DYNAMIC CLUSTERING PAPER}.

%Time-evolving communication networks are huge with large number of vertices. In these graphs, a small change, for example, modification of an edge in one part of a graph should not affect the entire graph. Applying the same intuition in context of clustering, we can say that modification of an edge between two clusters or within a cluster should not affect the rest of the clusters. By handling these modifications locally, we can prevent the need to touch the entire graph, and hence make the clustering algorithm more efficient. We apply this intuition to develop our algorithm.

%Our algorithm has two parts. The first part handles clustering of the graph and second handles reading of clusters.

%\begin{itemize}
%\item \textbf{Phase 1:} All clusters in the graph are kept independent and hence changes in a particular cluster doesn't effect the other clusters. The first part of the algorithm is applied when an edge is added to the graph. We identify the clusters that get effected by addition of this edge and take action to ensure cluster quality specified in Section~\ref{sub-sec:quality} is maintained. 
%\item \textbf{Phase 2:} The second part of the algorithm is applied when an application tries to read the clusters. We need to handle this part separately because weights of edges change with time and there might be a time lag between when the clusters were created (updated) and when they are read.
%\end{itemize}

%In the next section we describe algorithm to handle edge addition and then present an ideal algorithm to read clusters. We then give two efficient approximations of the ideal algorithm.

\subsection{Locality-Based Graph Clustering}
We propose a locality-based graph clustering approach that is designed to leverage both the temporal and spatial locality observed in Twitter and similar social messaging systems. The general principles can be applied across different graph clustering techniques. For concreteness in this paper, we shall focus on a locality-based version of the traditional min-cut clustering algorithm.

\subsubsection{Min-Cut Clustering}
First, we present some preliminaries to describe min-cut clustering, before introducing our locality-based enhancements. Intuitively, min-cut clustering identifies clusters with more intra-cluster edges than inter-cluster edges.

\medskip
\noindent\textbf{Minimum cut:} The minimum cut of $G$ with respect to vertices
$s$ and $t$, where $s \in S, t \in T$, is defined as partition of $V$ into $S$
and $T$ such that, the total weight of edges connecting the partitions is
minimum. This is represented as $c(S, T)$. For an undirected graph $G$ we can
define a weighted tree $T_G$ called the minimum-cut tree \cite{hu:mincut}. We can
determine $c(S, T)$ by finding the path from $s$ to $t$ in $T_G$, where the value
of $c(S, T)$ is equal to the sum of the weights of edges on this path.

\medskip
\noindent\textbf{Min-cut clustering:} The min-cut clustering algorithm
\cite{flake:cut-clustering} clusters a graph $G$ first by adding an artificial
sink $t$. All of the vertices of $G$ are connected to the artificial sink with an
edge capacity of $\alpha$, to form a modified graph $G'$, where $\alpha$ is a
parameter guiding the quality guarantees of the resulting clusters. The
minimum-cut tree $T'$ for $G'$ is then calculated. The connected components of
$T'$ obtained after removing the artificial sink $t$ are clusters in $G$.

% \algsetup{indent=2em}
% \newcommand{\CutClustering}{\ensuremath{\mbox{\sc CutClustering}}}
% \begin{algorithm}
% \caption{$\CutClustering(G(V,E), \alpha)$}\label{alg:cut-clustering}
% \begin{algorithmic}
% \STATE $V' = V \cup t$
% \FORALL{$v \in V'$}
% \STATE Connect $t$ to $v$ with a capacity of $\alpha$
% \ENDFOR
% \STATE $G'(V', E')$ be the graph obtained from $G$
% \STATE Calculate the minimum-cut tree $T'$ for $G'$
% \STATE Remove $t$ from $G'$
% \RETURN All connected components of $G'$ 
% \end{algorithmic}
% \end{algorithm}

%\textbf{Expansion:} The expansion of the (sub)graph, $\Psi(S)$, is the minimum expansion over all the cuts of the (sub)graph. The expansion of clusters in $G$ is defined as the minimum expansion over all the clusters. The larger the value of expansion, the better is the clustering algorithm.

% The quality of clusters generated using the min-cut clustering algorithm is
% closely related to the quality requirements. Following
% \cite{flake:cut-clustering}, we base the cluster quality on the expansion of a
% cut  $(S, \bar{S})$ in $G$

%\begin{align*}
% \label{expansion}
%\Psi(S) &= {\frac{\sum_{u \in S, v \in \bar{S}}w(u,v)}{min\{|S|,|\bar{S}|\}}} = {\frac{c(S, \bar{S})}{min\{|S|,|\bar{S}|\}}}
%\end{align*}

 %The expansion of the (sub)graph is the minimum expansion over all the cuts of
 %the (sub)graph. The expansion of clusters in G is minimum expansion over all
 %the clusters. The larger the value of expansion, the better is the clustering algorithm.

\medskip
Min-cut clustering relies on a special parameter $\alpha$ to
ensure the quality of the clusters generated, where:

% $\alpha$ provides a lower bound on intra-cluster expansion and an upper bound on inter-cluster expansion. Given $S \subset V$ and $P, Q \subset S | P \cap Q = \phi, P \cup Q = S$, $\alpha$ is defined as:
\begin{align}
\label{eq:clustering-quality}
\frac{c(S, V-S)}{|V-S|} \leq \alpha \leq \frac{c(P, Q)}{min(|P|, |Q|)}
\end{align}

By tuning this $\alpha$ parameter, the number and size of the resulting clusters can be varied (from one large cluster with all nodes to a trivial clustering consisting of $n$ singleton nodes).

\subsubsection{Exploiting Temporal Locality}
To reflect the temporal locality observed on Twitter, the first component of our crowd discovery algorithm is an edge impact damping
factor for reducing the weight of older edges. This is important so that the
crowds discovered reflect fresh (and more impactful) messages in the system.
Recall that each edge in the time-evolving communication network is associated
with an edge weight $w(u, v)$ and the time of the last communication between the
two users: $EdgeTime(u,v)$. We can modulate the weight $w(u, v)$ to reflect the
application semantics -- for example, by considering edge weights for all $u$ and
$v$ as $w(u, v) = 1$, we can treat all edges the same (regardless of when the
messages between users were sent -- meaning that crowds discovered at time $t$ reflect the entire history of communication in the network). Another possibility is to consider only edges
within a fixed time-window: e.g., $w(u, v) = 1$ for all edges with $EdgeTime(u,v)
- CurrentTime > \beta$, where $CurrentTime$ ($CT$) is the current time in the
system and $\beta$ is some windowing parameter. In this case, messages sent more
than $\beta$ time units earlier are completely disregarded by the crowd discovery
system, resulting in crowds that reflect the up-to-the-minute state of the network.

Intuitively, since messages sent more recently reflect the current interests of
users in the social messaging system, we propose an edge impact damping function
that gradually fades the impact of older messages relative to newer ones.
Concretely, we propose an exponentially decaying impact factor based on a damping
coefficient  $\xi$ for controlling the rate of damping. For edges $(u, v) |
w(u,v) > 0 $ we  update the new edge weight $w^*(u, v)$ using this exponential fading as:

\[
w^*(u, v) = w(u, v)- \log(CT - EdgeTime(u, v))\times \xi
\]

%$DampEdge:(w(u, v), EdgeTime(u,v), CurrentTime, \xi) \rightarrow w(u, v)$.
% \begin{align*}
% For\ w(u,v) = 1:\\
% DampEdge(u, v) =
% &w(u, v) - w(u, v) \times\ \xi\ \times\\
% &\log(CT - ET(u,v))\\
% For\ w(u,v) > 1:\\
% DampEdge(u, v) =
% &w(u, v) - \log(w(u, v)) \times\ \xi\ \times\\
% &\log(CT - ET(u,v))
% \end{align*}

%To have a notion of time in our algorithm let $CurrentTime$ ($CT$) be a pointer to current time in the system. The function $Time(C)$ gives the time when cluster $C$ was last updated and $EdgeTime(u,v)$ ($ET$) gives the time when the edge $(u, v)$ was last updated.

\begin{figure}[!t]
\begin{center}
\includegraphics[width=3.5in]{../../images/www/edgeDecay}
\caption{The graphs show changes to edge weights when $DampEdge(u, v)$ is
applied. The above graph shows actual edge weight and the bottom graphs show
effect of damping the edges.}
\label{fig:edge-decay}
\end{center}
\end{figure}

To illustrate the impact of this exponential fading, a typical communication graph between two users is shown in Figure~\ref{fig:edge-decay}.
The upper plot shows number of messages (actual weight) exchanged between two users
and the bottom plots shows the damped edge weights. The middle plot shows the effect of damping with $\xi = 0.3$ and
the bottom plot with $\xi = 1.0$. The value of $\xi$ determines the type of
crowd we identify. Crowds forming slowly can be identified with lower values
of $\xi$ while higher value of $\xi$ identifies crowds forming quickly.
Hence, this parameter can be tuned according to the particular application requirements.

Note that the overall clustering algorithm will occasionally need to damp the edges of all nodes in a cluster. We show in Algorithm~\ref{alg1}, the straightforward adaptation of the single edge damping to the damping of all nodes in a cluster $C$.

\algsetup{indent=2em}
\newcommand{\DampCluster}{\ensuremath{\mbox{\sc DampCluster}}}
\begin{algorithm}
\caption{$\DampCluster(C)$}\label{alg:cluster-damp}
\begin{algorithmic}
\STATE \textbf{Update Edges:} Update the edge weights in the
adjacency matrix for all internal and cut edges $(u,v)$ in $C$.
\begin{center}
$A(u, v) = A(u, v)- \log(CT - EdgeTime(u, v))\times \xi$
\end{center}
\end{algorithmic}
\label{alg1}
\end{algorithm}

% between the users results in the weight between the two users reduced overtime. Our algorithm handles formation and breaking of communities based on the weight obtained from $DampEdge$.

\subsubsection{Exploiting Spatial Locality}
Given the edge impact factor, we next consider how the spatial locality of communication on Twitter can enable efficient locality-based clustering. Recall that locality-based clustering is developed on the notion that changes in
 a small region of a graph should not affect the entire graph. Hence, on
 insertion of a new edge (corresponding to a new message between users in the social
 messaging service), we can apply the locality-based clustering to a small number of
 affected crowds only and not the entire set of crowds. This helps in saving the
 computational expense of clustering the entire graph.  Since
 this approximation does not have the strong quality guarantees of min-cut
 clustering, we empirically validate the clustering quality
in Section~\ref{sec:experiments}.

As a first step, we present a local version (see Algorithm~\ref{alg:cluster-recluster}) of the standard min-cut clustering algorithm that can be applied to a particular subgraph of $G$. Given a set of local crowds $S$ to re-cluster, the algorithm first contracts $G$ to $G'$. It then creates a new graph $G''$ by adding an artificial sink $t$ to $G'$ and connecting all the vertices of $S$ to $t$ with edges of capacity $\alpha$ and all the vertices in $(V'-S)$ with edges of capacity of $\alpha|V-S|$. It then determines the minimum-cut tree $T''$ for $G''$. The connected components obtained after removing $t$ from $T''$ are the new crowds. In this way, only a small portion of the communication network is impacted, leading to more efficient clustering that re-clustering the entire network.

\algsetup{indent=2em}
\newcommand{\LocalCutClustering}{\ensuremath{\mbox{\sc LocalCutClustering}}}
\begin{algorithm}
\caption{$\LocalCutClustering(S)$}\label{alg:cluster-recluster}
\begin{algorithmic}
\STATE \textbf{1. Contract $G$:} Reduce $G$ to  $G'$ by replacing
vertices $V-S$ with a new vertex $x$. All the resulting loops are deleted and parallel
edges are replaced with a single edge with weight equal to the sum of the
edges.% \cite{flake:cut-clustering}. 
\STATE \textbf{2. Expand $G'$:} Construct a new graph $G''$ by
adding vertex $t$ to $G'(V', E')$. Connect $t$ to $v, \forall v \in S$ with
edge capacity of $\alpha$ and $t$ to $v', \forall v' \in (V'-S)$ with edge
capacity of $\alpha|V-S|$.% \cite{flake:cut-clustering}\cite{saha:clustering}.
\STATE \textbf{3. Minimum-cut tree:} Determine minimum-cut tree
$T''$ for $G''$. The connected components obtained in $T''$ after removing vertices $t$ and $x$ from it are
the clusters in $S$. 
\end{algorithmic}
\label{alg2}
\end{algorithm}

%Locality-Based clustering essentially has 2 phases. (i) A clustering phase during which local crowds are clustered without affecting the entire graph and, (ii) An edge insertion phase during which we determine the crowds that are affected by the insertion and check if these crowds need to be re-clustered.

%We first present some  preliminary definitions followed by the locality-cut clustering algorithm. We end the section by giving the time complexity of the algorithm.

% [[NEED TO MAKE SURE ALL OF OUR NOTATIONS ARE CORRECT AND CONSISTENT; ALSO NEED TO MAKE SURE WE ARE CONSISTENT IN OUR USE OF CROWD / CLUSTER AND THESE NEW SUBSECTIONS -- e.g., LOCAL CROWD DETECTION, LOCALITY-BASED, etc.]]
%\subsubsection{Locality-Based Clustering: Overview}%

% where $\alpha$ is a lower bound on intra-cluster expansion and an upper bound
% on inter-cluster expansion. %The details of determining $\alpha$ are given in \cite{flake:cut-clustering}.

%Second, the addition of a new edge to the time-evolving communication network $G$ (i.e., a new message from one user to another at time $t$) should only impact a small number of crowds and not the entire clustering. Hence, we can leverage this locality of impact to reduce the cost of updating all clusters in the network.

The question remains, though -- which crowds should be selected for the local version of cut clustering described in Algorithm~\ref{alg2}? Selecting too many crowds for re-clustering may result in expensive computation, whereas selecting too few crowds may result in poor crowd quality. We adopt an approach on each edge insertion that  that makes use of temporal and spatial locality to discover crowds in a time evolving communication network. The psuedocode for the algorithm is given in Algorithm~\ref{alg:add-edge}.

%We now present the algorithm that makes use of temporal and spatial locality to discover crowds in a time evolving communication network. The algorithm is an iterative algorithm that is executed on every edge addition.

\algsetup{indent=2em}
\newcommand{\AddEdge}{\ensuremath{\mbox{\sc UpdateClustersOnEdgeInsertion}}}
\begin{algorithm}[!ht]
\caption{$\AddEdge(u,v,w)$}\label{alg:add-edge}
\begin{algorithmic}
\STATE \textbf{1. Initialization:} If the edge added has vertices
that have not been observed before add them to vertex set $V$. Create singleton clusters
for the new vertices %with  their $ClusterTime$ value set to $CurrentTime$ 
and add them to cluster set $K$. 
\STATE \textbf{2. Update the adjacency matrix: }\\
\begin{center}
$A(u,v) = A(u,v) + w$
\end{center}
\STATE \textbf{3. Clustering:} Let $u$, $v$ belong to clusters $C_u$ and $C_v$
respectively. Update the edge weights within the clusters using DampCluster()
function defined before. Now depending on the conditions that match perform the
corresponding clustering operations: 
\STATE \ \ \ \ \textbf{Case i. } If the vertices belong to same cluster then
updating the edge weights might have resulted in formation of clusters within
this cluster. Check for new clusters using LocalCutClustering($C_u$). 
\STATE \ \ \ \ \textbf{Case ii. } If the vertices belong to different clusters
and the addition of the edge does not reduce the quality of clustering perform no action. 
The quality of the clustering is maintained if the following inequalities
(Equation~\ref{eq:clustering-quality}) are satisfied. \\
\begin{center}
$\frac{c(C_u,V-C_u)}{|V-C_u|} \leq \alpha$ and
$\frac{c(C_v,V-C_v)}{|V-C_v|} \leq \alpha$ 
\end{center}
\STATE \ \ \  \ \ \textbf{Case iii. } If the vertices belong to different clusters
and the addition of the edge satisfies the merging condition
$\frac{2c(C_u, C_v)}{|V|} \geq \alpha$, merge the 2
clusters. % and set the merged clusters $ClusterTime$ value to $CurrentTime$. 
\STATE \ \ \ \ \textbf{Case iv. } If the vertices belong to different clusters
and the previous 2 conditions are not met then the quality of clustering has
reduced. Hence, perform LocalCutClustering($C_u \cup C_v$) to generate clusters
that maintain clustering quality. 
\end{algorithmic}
\end{algorithm}

%The \cite{saha:clustering}

%Edge weights in a time evolving communication network are time dependent. Hence, before clustering the affected crowds, we need to determine current edge-weights of all the edges within these crowds. This is done by updating all the edge-weights of the crowds according to edge impact function {\scshape DampEdge}. The function to update a crowd is given in Algorithm~\ref{alg:cluster-damp}. For a crowd $C$ the function damps every internal and external edge in $C$ and updates $ClusterTime(C)$ to $CurrentTime$.

%To perform clustering on a subset of crowds we first contract the entire graph as proposed in \cite{flake:cut-clustering}. The function to contract a graph is given in Algorithm~\ref{alg:contract}. For a set of crowds $S$ in $G$ it replaces $V - S$ with a single node $x$. All self resulting loops are removed and parallel edges are replaced with a single edge of capacity equal to the sum of capacities of the parallel edges. This procedure has a time complexity of $\theta(|A|^2)$, where $A$ is the adjacency matrix for $G$.

% [[THIS SECTION IS STILL A LITTLE ROUGH -- THE LOGIC OF THE CONTRACTION, DAMPING, ETC. IS NOT OBVIOUS -- COULD USE A LITTLE MORE EXPLANATORY GLUE ]]

% When a new edge is inserted into the network (corresponding to a new message
% between users in the social messaging service), we consider two major cases: (i)
% the two users belong to the same crowd already; (ii) the users belong to
% different crowds. In the first case, we update the edge weights of the crowd
% according to the edge impact damping function defined above and then run a local
% re-clustering algorithm on only the cluster that the two users belong to. In the
% second case, there are three possible outcomes: do nothing, merge the two
% clusters into a single cluster, or re-cluster the two clusters. We first present
% some basic procedures that the local clustering on edge addition algorithm will
% be using and then present the full algorithm.

\subsubsection{Time Complexity} 
The procedure to damp a crowd has a complexity of $O(e)$, where $e$ are the
number of edges in the crowd. The algorithm to re-cluster uses relabel-to-front
approach of push-relabel algorithm \cite{goldberg:push-relabel} to calculate the
minimum-cut tree. It has a time complexity of $O(l^3)$, where $l$ is the number
of vertices in the minimum-cut tree. Let $k = \max_{i = 1}^{|K|}(|C_i|)$, the
size of the largest crowd in $K$. In edge addition algorithm when both the
vertices of the edge belong to the same crowd we damp $O(k^2)$ edges and
re-cluster $O(k)$ vertices. In this case the time complexity is $O(k^3)$. In
case where the quality of crowds is maintained on addition of the edge the time
complexity is $O(2k^2)$ for damping the edges. During merge operation we dampen
$O(2k^2)$ edges and re-cluster $O(2k + 1)$ vertices, which results in a time
complexity of $O(k^3)$. Hence, the time complexity of the algorithm to add edge
in $O(k^3)$, as compared to the time complexity $O(n^3)$ for cut-clustering
algorithm in \cite{flake:cut-clustering}.

% [[Recently, there have been several attempts to create dynamic min-cut
% algorithms with provable quality guarantees \cite{saha:clustering,
% gorke:clustering}; these efforts are BLAH BLAH BLAHB ALHB.]]

%which is same as the
%complexity of algorithm in \cite{saha:clustering} and better than The method to improve this complexity to $O(n\ polylog(n))$ is given in
%\cite{saha:clustering}.

\subsection{Crowd Evolution}
\label{sec:crowd-evolution}
The approach described in the previous section finds crowds at a given time. But
to determine crowd evolution we need to discover crowds at regular intervals and
understand the changes that take place in these crowds between time intervals. In
this section, we show how to build crowd evolution graphs using the crowds
obtained at different time intervals. This graph helps us track the evolution of a crowd and
understand the changes it went through over a period of time.

%The time interval at which we generate the crowds determines the granularity of evolution. For example, mining crowds every hour gives a more granular evolution than mining the crowds every day.

\subsubsection{Problem Statement}
To track evolution of a particular crowd we need a way to represent it uniquely.
Every crowd is made up of a unique set of users and this set can be used to
represent it. But, communication between users changes crowds between time
intervals resulting in different representations for crowds. Hence, absence of a
user-independent way to represent crowds makes the task of tracing the evolution
of a crowd non-trivial.

Let, $K_i$ be the set of crowds identified in time $t_i$. $C_{ij}$ is the
$j^{th}$ crowd of $K_i$. $H$ is the collection of crowd sets and contains a
crowd set $K$ for every time interval. $|H| = s$, where $s$ is the total number
of time intervals. $Crowd(v)$ gives the crowd a vertex
$v$ is currently in. The goal of crowd evolution is to link crowds across these time periods into a unique chain of crowds.

Recently, there has been some work analyzing communities across times. In
\cite{backstrom:group}, the authors look at communities on large social networks
like LiveJournal and MySpace. Since the communities are explicitly defined in
these networks, the task of determining evolution of graph is trivial. The
changes clusters undergo between time intervals are considered as events in
\cite{asur:event}. An example of an event would be two communities merging
together to form a new community or a single community splitting into two or more
communities. 
% But in our case instead of events, we observe a notion of
% parent-child existing among crowds between two consecutive time intervals. We present an algorithm that
% uses this notion to determine crowd evolution.

 %similar approach to define events has been used in several other papers but all of these papers don't provide a mechanism to determine evolution of communities.

\begin{figure}[!t]
\begin{center}
\includegraphics[width=3.5in]{../../images/www/hierarchy}
\caption{Example crowd evolution graphs. The green
nodes represent start of a crowd and the red node shows the dispersing of the
crowd.}
\label{fig:hierarchy-graph}
\end{center}
\end{figure}

% \subsection{Algorithm} \label{sub-sec:hierarchy-graph}
\subsubsection{Crowd Evolution Algorithm}
We propose an algorithm based on events to track the complete evolution of a
crowd. The algorithm builds an evolution graph for every crowd. This graph can be
visualized as a tree with current crowd as its root and traversing down the tree
would give us the evolution of the crowd. Using this we should be able to track
all the splits and merges that occurred during its lifetime.
% But, in this paper we are more interested in identifying crowds that are
% popular and growing. Hence, we develop an algorithm that does not depend on
% identifying events like in other papers.
In our approach we enforce a condition that limits crowds to
have only one parent. We present a method to select one parent in cases where we
have multiple parents. We next present the details of constructing a crowd
evolution graph.

Let every crowd $C$ have an age and a parent, from which it evolved.
$Age(C)$ and $Parent(C)$ give the parent and age of the crowd respectively. The
root crowd has its $Parent$ value set to $None$. A crowd evolution graph for a
crowd $C$ is represented as $G_e$. Ancestors of crowd $C$ are represented as
vertices and the transition the crowd underwent at every time interval are
represented as edges. An example for a collection of crowd evolution graphs is
shown in Figure~\ref{fig:hierarchy-graph}.

The procedure to build an evolution graph is given in
Algorithm~\ref{alg:cluster-hierarchy}. We call this procedure by passing previous
crowd set, $K_{s-1}$,  and current crowd set, $K_s$. If $C_{sj}$ is a new crowd
we set its parent to $None$ and its age to 1. An example for this are the green
crowds in Figure~\ref{fig:hierarchy-graph}. If it is not a new crowd we try to
identify the parent crowd $C_p$ from which it evolved using these cases:

\textit{Case 1}: If there exists a unique crowd in $K_{s-1}$ that
contributed maximum users to this crowd then pick the unique crowd as parent.

\textit{Case 2}: If there are more than one crowds that contributed maximum (but
equal) users, then pick the older crowd as the parent. We do this because,
picking an older crowd as parent allows us to observe the evolution over longer
periods of time.

\textit{Case 3}: If there are more than one crowds like in previous case
and but their ages are same, then pick a crowd at random as the parent crowd.

The evolution graph for a crowd can be obtained by traversing through parent
nodes starting from the crowd node till parent node is $None$.

\algsetup{indent=2em}
\newcommand{\CrowdEvolution}{\ensuremath{\mbox{\sc CrowdEvolution}}}
\begin{algorithm}
\caption{$\CrowdEvolution(K_{s-1}, K_s))$}\label{alg:cluster-hierarchy}
\begin{algorithmic}
\FORALL{$C_{sj} \in K_s$ }
\IF{$Crowd(v) = None\ \forall v \in C_{sj}$}
\STATE $Crowd(v) = C_{sj} \forall v \in C_{sj}$
\STATE $Parent(C_{sj}) = None$
\STATE $Age(C_{sj}) = 1$
\ELSE
\STATE \textbf{Determine} the set of majority contributing crowds $M$ from
$K_{s-1}$
\IF{$|M| > 1$}
\STATE \textbf{Determine} oldest crowd in $M$ as parent $C_p$ 
\\\COMMENT {Select randomly if more than one oldest crowds}
\ELSE
\STATE \textbf{Set} the crowd in $M$ as parent $C_p$
\ENDIF
\FOR{$v \in C_{sj}$}
\STATE $Crowd(v) = C_{sj}$
\ENDFOR
\STATE $Parent(C_{sj}) = C_p$
\STATE $Age(C_{sj}) = Age(C_p) + 1$
\ENDIF
\ENDFOR
\end{algorithmic}
\end{algorithm}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=3.5in]{../../images/www/cluster_events}
\caption{Examples of crowd modification events. Arrows indicate
crowds in $t_s$ that contribute to crowds in $t_{s+1}$. Color of the
crowd in $t_{s+1}$ indicates its parent in $t_s$.}
\label{fig:cluster-events}
\end{center}
\end{figure}

Examples of how parent crowds are selected is shown in
Figure~\ref{fig:cluster-events}. (I) shows two crowds merging. Here, parent of
the crowd in $t_{s+1}$ is the crowd in $t_s$ that contributed maximum nodes. (II)
shows a single crowd in $t_s$ being split into two crowds in $t_{s+1}$. The
parent of crowds in $t_{s+1}$ is obtained directly. (III) shows a case where
three crowds in $t_s$ contribute to three crowds in $t_{s+1}$. Though crowd A and
B contribute two nodes each to D, B is designated as the parent of D since B is
older than A.

\section{Experiments and Results}
\label{sec:experiments}
In this section we present the results of three sets of experiments: (i) we first
explore the impact of locality-based crowd discovery compared to the 
static graph clustering approach without the locality optimizations; (ii) then we investigate the impact of the tunable edge damping parameter; (iii) we then examine the features of the
discovered crowds, including size and lifespan; and (iv) we illustrate some
crowd-based trends that differ from trends aggregated from individual users.

%We first present the details of the dataset that we will be using in our experiments. The results from this paper can be divided into two parts. The first set of results indicate the efficiency and quality  of the crowd discovery algorithm. We then show some of the crowds we discovered and some salient properties of these crowds.

%textit{time-evolving communication network}

Based on the user messages, we built a time evolving communication network
(Recall Section~\ref{sec:crowd-discovery}), with users as vertices and edges
indicating a message between users. Starting from an initial time 00:00:00 on
October 1, we fed messages to the crowd discovery and evolution system as they appear. On each edge
insertion, we ran {\scshape AddEdge} with a damping
coefficient of $\xi$ to 1.0. We extracted crowds every hour,  resulting in 2208 sets of hourly crowds, and connected these
crowds over time using the {\scshape CrowdEvolution} algorithm.

%The first day in our dataset i.e, $1^{st}$ of October, 2008, was an Wednesday. Based on this we observe increased activity during weekdays than on weekends (2 consecutive lower peaks). Some of the events we observe in our dataset with their dates are shown in Table~\ref{table:events}.

%We will be using interaction data obtained from Twitter \cite{website.twitter} in our experiments.

%Number of messages exchanged between two users can be used as weight. Every time a directed message is observed, we trigger an add edge action using Alg.\ref{alg:add-edge}.

%In our prototype system, we collect social messages from the Twitter microblogging service through a mix of crawling and API calls to the Twitter service. On Twitter, users can post status updates of 140 characters or less. A status update message posted by user $u_1$ including @$<u_2>$ is considered a message from $u_1$ to $u_2$ (note that users other than $u_2$ may view this public message as well). The data collection module collects these messages as tuples $(u_1, u_2, i, t)$, where $i$ is the message sent from user $u_1$ to $u_2$ at time $t$. The collected tuples are then passed to the Crowd Discovery module. Note that CrowdBuzz architecture can be flexibly adapted to other domains supporting social messaging services (e.g., Facebook, which has recently adopted a similar user-addressable public messaging system within their status updates).

\subsection{Crowd Discovery: Efficiency and Quality}
In the first set of experiments, we investigate the efficiency and quality of
the proposed locality-based clustering approach for crowd discovery. Since social messaging systems are large
with a high rate of new messages, it is important for crowd discovery to be
efficient; but efficiency must be balanced with the quality of the discovered
crowds. As a baseline for comparison, we considered the min-cut clustering
algorithm \cite{flake:cut-clustering} without the locality-based optimizations. Since min-cut clustering is designed for
static graphs, we took snapshots of the time-evolving communication network every
hour and then ran min-cut clustering over each of these hourly snapshots,
resulting in 2208 total crowd sets.

\begin{figure}[!t]
\begin{center}
\includegraphics[width=3.5in]{../../images/cikm2010/runningTime1}
\caption{Running time comparison: The top chart shows the growth in users and
messages; the middle figure shows the running time of min-cut clustering;
the bottom figure shows the running time of online clustering algorithm. Note
that the middle figure as running time as high as 4800 minutes, while the
max-running time seen in online algorithm is 6 minutes.}
\label{fig:running-time}
\end{center}
\end{figure}

\medskip
\noindent{\textbf{\textbf {Running Time}}}: In Figure~\ref{fig:running-time}, we
show the ratio of the running time between min-cut clustering and the locality-based crowd
discovery approach (note that we focus on the first 30 hours for presentational
detail; the general trends hold across the duration). The first observation is
that the proposed approach is at least 100 times faster than non-locality optimized approach
in all cases, and upwards of 1,000 times faster in some cases.  Second, the ratio
of running times is clearly impacted by the number of messages in the system. The
ratio decreases during intervals 11-15 due to the knee in the number of messages
(the upper figure). This steep increase in messages slows the proposed approach,
but the ratio increases as the number of messages entering the system becomes
more stable.

\medskip\noindent{\textbf {Crowd Quality}}: Although the proposed locality-based approach results in a much faster criwd discovery, there may be a cost in terms of crowd
quality. To gauge the degree of this cost, we measure the quality of the
discovered crowds using the ratio-association value \cite{dhillon:multilevel},
which seeks to maximize the weight of edges within a cluster:
$\operatorname*{maximize} \sum_{i = 1}^k \frac{c(C_i, C_i)}{|C_i|}$. Using this
objective, we measure the ratio-association values for both min-cut clustering
and the proposed approach. In Figure~\ref{fig:ratio-assoc}, we show the
\textit{ratio} of ratio-association values for both algorithms versus the
proposed approach; the ratio-association value for online is indicated using
black bars of height 1. We see that during the initial intervals, the
ratio-association of the min-cut algorithm is more than that for the locality-based approach, but the
ratio continues to decrease with time. We see significant improvements by the
time we reach the $30^{th}$ interval. This shows that as the size of the graph
grows the quality of cluster generated by the locality-based approach increases.

Empirically, we find that the locality-based approach supports efficient crowd discovery
while maintaining crowds of relatively high quality (within 50\% of the ideal
case using static graph clustering).

%We compare the performance of our clustering algorithm with minimum-cut clustering algorithm described in Section~\ref{sub-sec:mincut-algo}. Minimum-cut algorithm is an offline algorithm while our algorithm is an online clustering algorithm, hence to compare the performance of these algorithms input is fed in different ways. To check the performance of minimum-cut algorithm, for a particular time interval, we build the graph consisting of all the users and their interactions until end of that interval and feed this graph as input to the clustering algorithm. In case of our algorithm, since it is online, we need not create a separate graph as such.

%In the context of real-time crowd discovery in social messaging systems, however, these graph clustering approaches face challenges. First, social messaging systems like Facebook and Twitter are extremely large (on the order of 100s of millions of unique users), placing huge demands on the computational cost of graph clustering (which can be $O(n^3)$ in the number of users, as in min-cut clustering \cite{flake:cut-clustering}). Second, these services support a high-rate of edge addition so the discovered crowds may become stale quickly, resulting in the need to re-cluster all users at regular intervals (again, incurring the high cost of static graph clustering). Third, the strength of association between two users in a social messaging system may depend on the recency of their communication (e.g., a message from $u_1$ to $u_2$ today should be considered a stronger signal of their common crowd membership than a message from $u_1$ to a third user $u_3$ a month ago), meaning that a crowd discovery approach based on graph clustering should carefully consider how to decay edge weights. Fourth, the bursty nature of user communication demands a crowd discovery approach that can capture these highly-temporal based clusters.

%We feed individual interactions  (edge) as they appear. This ensures that the graphs algorithms use at different intervals are the same. In case of our algorithm we set the damping co-efficient $\xi$ to 1.0 and user {\scshape GetClustersInWindow} method to read clusters. We determine clusters at intervals of length 1 hour, starting from 00:00:00 $1^{st}$ October, 2008 to 5:59:59 $2^{nd}$ October, 2008, which results in 30 time intervals. (This data will change as we get results).

\subsection{Varying the Edge Damping Coefficient}
In the second set of experiments, we analyze the performance of the algorithm as the damping
coefficient is modified, from 0.5 to 1.0 to 1.5. The damping coefficient is an important tunable parameter that determines the rate the at which crowds disband. We first show the impact varying this parameter has on the number of
crowds discovered and the size of these crowds. We then investigate the impact of this parameter
 on the speed of crowd discovery and the quality of the crowds
discovered.

\medskip\noindent{\textbf {Impact on number of crowds discovered}}: The damping coefficient 
can affect the number of crowds discovered at any time interval. We find that the number for crowds for coefficient of 0.5 is more than the ones for 1.0 and 1.5. In the case of larger coefficient values the crowds disband
quickly and hence we find fewer crowds. Coefficients 1.0 and 1.5 discover
almost the same number of crowds. We observe larger crowd sizes at lower
coefficient values as the crowds disband slowly.

%In this experiment we observed that most of the crowds discovered by 1.0 don't get disbanded even when the threshold is increased to 1.5. Figure. \ref{fig:damp-cluster-count} (bottom) shows the average crowd sizes at different damping coefficients. 
%The impact of different damping coefficients on the running time of the algorithm is shown in Figure. \ref{fig:damp-cluster-time}. To show the closeness between therunning times for all the coefficients, the figure contains values for initial 400 intervals only.

\medskip\noindent{\textbf {Impact on crowd discovery time and crowd sizes}}: We observe that the running time of the algorithm
is not dependent on the coefficient (see Figure~\ref{fig:damp-cluster-time}). This is important because, we can now use
this algorithm to observe crowds at degrees of granularity by changing the
coefficient with affecting the running time performance of the algorithm.

\begin{figure}[!t]
\begin{center}
\includegraphics[width=3.5in]{../../images/sigir/dampClusterTime}
\caption{Time to discover crowds at each time interval for different
damping coefficients.}
\label{fig:damp-cluster-time}
\end{center}
\end{figure}

\medskip\noindent{\textbf {Impact on ratio association values}}: To observe the quality of crowds discovered we use ratio association, as defined before. We observe that the best crowds are obtained when damping coefficients is 1.0. Hence, in the rest of the experiments we set the coefficient to 1.0.

\subsection{Crowd Analysis}
In the third set of experiments, we explore the characteristics of the discovered crowds using the proposed crowd discovery and evolution approach.

\begin{figure}[!t]
\begin{center}
\includegraphics[width=3.5in]{../../images/www/noOfClustersOverTime}
\caption{Number of crowds at each time.}
\label{fig:no-of-clusters-time}
\end{center}
\end{figure}

\medskip\noindent{\textbf{Time-dependent crowding patterns}}: We first consider the number
of crowds discovered over time, which can yield insights into crowding patterns
in social networks. Figure~\ref{fig:no-of-clusters-time} shows the distribution
of crowds during the week. Like the user and message frequency in
Figure~\ref{fig:data-distribution}, we observe crowds following a daily pattern.
But unlike the previous case, where we saw high and uniform usage throughout
afternoon and evening, we observe the largest number of crowds forming in the
evening. We are interested to explore this tension between crowding behavior and
overall Twitter usage in our continuing work.

%[PEOPLE DISCUSS THINGS IN THE EVENING. MAY THIS BE THE REASON?]

\begin{figure}[!t]
\begin{center}
\includegraphics[width=\linewidth]{../../images/www/clusterExamplesOverTime}
\caption{Examples of some of the crowds discovered in the dataset. The text
next to the trend shows the topic being discussed in the crowd.}
\label{fig:cluster-example}
\end{center}
\end{figure}

\medskip\noindent{\textbf {Crowd lifespan}}: Second, we consider the lifespan of crowds,
which is an indicator of a crowd's activeness. A crowd that is constantly
communicating lives for a longer time than an inactive crowd. We illustrate some
of the discovered crowds and their lifespans in Figure~\ref{fig:cluster-example},
with an annotation next to the crowd peak showing the topic of discussion. For
example, we can see a crowd (shown in black) discussing Sarah Palin and the
Vice-Presidential debate from the $40^{th}$ hour to $80^{th}$ hour that peaks
around the time of the actual debate. We observe that crowds that talk about
general everyday things have a greater lifespan than crowds discussing specific
events. In Figure~\ref{fig:cluster-example}, a crowd (annotated with
\textit{thank, whats, wow}) discussing everyday things lives through the entire
week, while, during the same period we observe several event-specific crowds,
like crowds discussing the Red Sox, Sarah Palin, and Girl's Night Out (gno)
forming and dissolving. These event-specific crowds start forming just before the
event and die a few intervals after the completion of that event. This indicates
two type of Twitter usage: one is centered around events; the other uses it as a
source of everyday communication.

%We use the previously described crowd discovery algorithm to obtain crowds at every time interval. In this analysis we consider crowds of size greater than 3 only. Some of the crowds discovered in the dataset are shown in Figure~\ref{fig:cluster-example}. It shows trends of crowd evolution, with the text next to a trend peak showing the topic being discussed in the crowd. For example, we can see a crowd (shown in black) discussing Palin and the Vice-Presidential debate from the $40^{th}$ hour to $80^{th}$ hour.

\ \\
\subsection{Crowd-based vs. User-based Topics}
In the final set of experiments, we compare the topics that interest crowds
versus topics that are discovered through the aggregation of tweets from
individual users.

\medskip\noindent{\textbf {Hashtags vs. Crowd topics}}: Twitter supports the inclusion of
metadata in tweets through the use of hashtags (e.g., ``\#redsox''). We first
aggregated all of the hashtags in our dataset to see what topics were of most
interest. These top hashtags are shown in Table~\ref{table:hashtags-topics} and
most are related to specific events, including several debate-related hashtags,
conference-related hashtags (\textit{wct08, ldsconf, wjs08}), and a hashtag
associated with an election in Brazil (\textit{eleicoes08}). This
individual-based aggregation is similar to how Twitter's trending topics works
(see http://search.twitter.com/). To identify topics of interest to the
discovered crowds, we extracted the nouns used in messages sent by crowd members
(using Python's Natural Language Toolkit) and ranked the nouns by a simple TF-IDF
measure.

\begin{table}
\centering
\begin{tabular}{|p{2cm}|p{2cm}|p{2cm}|}
\hline
\textbf{Rank} & \textbf{Hashtags} &
\textbf{Crowd topics} \\ \hline 
1 & vpdebate & twitter \\ \hline
2 & current & debate \\ \hline
3 & redsox & palin \\ \hline
4 & vmb & money \\ \hline
5 & ldsconf & video \\ \hline
6 & debate08 & kids \\ \hline
7 & palin & obama \\ \hline
8 & wcto08 & school \\ \hline
9 & wjs08 & mccain \\ \hline
10 & eleicos & office \\ \hline
\end{tabular}
\caption{Top hashtags in the dataset and topics observed for the week. Topics
like \textit{money, kids} are not tagged but highly discussed.}
\label{table:hashtags-topics}
\end{table}

\begin{figure}[!t]
\begin{center}
\includegraphics[width=3.5in]{../../images/www/ldsconf}
\caption{Comparison between hashtags and crowd topics for \textit{ldsconf}
shows that many people mention it in their tweets but they don't discuss it.}
\label{fig:ldsconf}
\end{center}
\end{figure}

\begin{figure}[!t]
\begin{center}
\includegraphics[width=3.5in]{../../images/www/palinVsredsox}
\caption{Comparison between hashtags and crowd topics for \textit{redsox} and
\textit{palin}. 
% shows that, even though \textit{redsox} is tagged more often
% than
% \textit{palin}, people discuss \textit{palin} more.
}
\label{fig:palin-redsox}
\end{center}
\end{figure}

We see that the crowd-based topics are more varied and less event-specific,
including topics like \textit{money}, \textit{kids}, and \textit{school}. Some
topics like \textit{ldsconf} (corresponding to the LDS Semi-annual General
Conference) are hashtagged often but are part of no crowds (See
Figure~\ref{fig:ldsconf}). Similar results hold for the conference tags
\textit{wcto08, wjs08}, indicating lots of individual activity via tweeting about
the conference, but little cohesive communication among members of a community.
Another example of the difference between hashtags and topics discussed is shown
in Figure~\ref{fig:palin-redsox}. We see the distribution of the topics
\textit{palin} and \textit{redsox}, where the number of hashtags for
\textit{redsox} is significantly more than the hashtags for \textit{palin}, but
we see that more crowds discuss \textit{palin} than \textit{redsox}.
%Understanding and exploring these differences can be important for BLAH BLA

% Hashtags are meta information attached to tweets by users to indicate the topic
% of the tweet. To identify the topic of a crowd, we find top nouns used in the
% tweets generated by the crowd. We identify nouns by parts of speech tagging on
% these tweets using python Natural Language Toolkit (NLTK). We consider each
% tweet as a separate document and determine tf-idf scores for all the nouns. The
% nouns with maximum tf-idf scores indicate the topic of the crowd.

% The difference in topics identified by hashtags and crowd analysis is shown in
% Table~\ref{table:hashtags-topics}. It shows topics like money and school which
% are never tagged but are discussed in crowds. On the other end, some topics
% that get tagged a lot are never discussed. An example for such a topic is shown
% in Figure~\ref{fig:ldsconf}. We found several topics like this including
% wcto08, wjs08.

\begin{figure}[!t]
\begin{center}
\includegraphics[width=3.5in]{../../images/www/clusterGrowth}
\caption{Topic evolution in a crowd over time.}
\label{fig:topic-time}
\end{center}
\end{figure}

 %Topic in the crowd moves from something generic to specific about Vice-Presidential debate before becoming generic again.

\medskip\noindent{\textbf {Topic evolution}}: Finally, we can track the evolution of topics within a crowd as users join and leave over time. Observing the changing topics in a crowd can give us a
better understanding about the interests of a crowd and hence help us model the
crowd better. An example of such a topic evolution is shown in
Figure~\ref{fig:topic-time}. The crowd at the beginning discusses something
generic and then starts discussing the Vice-Presidential debate as it occurs
(intervals 50-54). The crowd has maximum users during the debate and begins to
lose users on completion of the debate. As we move away from the time of the debate
we see the crowd discussing other topics before disbanding. %[WHAT ELSE CAN BE ADDED?]

% Topic discussed in a crowd evolves with time as users join or leave the crowd. Changes is topics also occur because of some external event.

\section{Conclusions}
\label{sec:conclusions}
In this paper, we have studied the problem of automatically discovering and
tracking the evolution of \textit{group-based trends} in highly-dynamic social
messaging systems like Twitter and Facebook. We believe this is a complementary
but promising alternative to traditional individual-based trend detection. We
presented a locality-based clustering algorithm for a time evolving communication
network that supports efficient crowd discovery while maintaining crowds of
relatively high quality. Two of the key features of this approach are its use of
Twitter's temporal and spatial locality to support efficient crowd detection.
Based on a three month snapshot of Twitter consisting of
 711,612 users and 61.3 million messages, we showed how the proposed approach can
 identify and track interesting crowds based on the Twitter communication
 structure and find crowd-based topics of interest.

As part of future work, we plan to investigate hybrid graph clustering approaches
that build on the communication-based approach presented here -- e.g., by
considering content-based and geographic-based similarity across users. For
example, for content-based crowds, we can define edge weights using a
content-based similarity metric (like cosine or KL-divergence), so that more
similar messages (nodes in the graph) are more strongly linked. Complicating this
semantic distance is the use of non-standard grammar and words in social messages
(e.g., ``about'' vs. ``abt'' vs. ``@bt''); hence, we will need to carefully
explore and enhance techniques for comparing extremely short text segments in the
presence of errors, jargon, and other artifacts of highly variable quality
user-contributed content. Similarly, for location-based crowds, we are
investigating simple distance-based edge weights (240 miles for a message issued
from Dallas, as compared to one from Houston).

%We then examined the features of the discovered crowds and illustrated some crowd-based trends that differ from trends aggregated from individual users.

%In this paper we presented CrowdBuzz system for discovering and tracking the evolution of crowds.

{\scriptsize
\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
}
\balancecolumns % GM July 2000

\end{document}

\subsection{On-Demand Crowd Reporting}
The third component of the CrowdBuzz crowd discovery approach is on-demand crowd
reporting. Recall that crowd evolution and analytics tools will query for the
latest crowd information at regular intervals (e.g., every minute, every hour). This
third and final component for crowd discovery seeks to forgo the cost of constant
crowd maintenance between these intervals through the use of on-demand crowd
reporting.

%The second part of the algorithm is applied when an application tries to read the clusters. We need to handle this part separately because weights of edges change with time and there might be a time lag between when the clusters were created (updated) and when they are read.

We first present the ideal crowd reading approach in 
Algorithm~\ref{alg:get-clusters}. There might be a time lag between the time a
crowd was last updated and the time when an application reads this crowd. Hence,
we update edges in the crowd to account for this lag in {\scshape DampCluster}
method and then re-cluster it ensure quality.

\algsetup{indent=2em}
\newcommand{\GetClusters}{\ensuremath{\mbox{\sc GetClusters}}}
\begin{algorithm}
\caption{$\GetClusters()$}\label{alg:get-clusters}
\begin{algorithmic}
\FORALL{$C_i \in K$}
\STATE DampCluster($C_i$)
\STATE LocalCutClustering($C_i$)
\STATE $CurrentClusters = CurrentClusters \cup C_i$
\ENDFOR
\RETURN $CurrentClusters$
\end{algorithmic}
\end{algorithm}

In this approach, every time an application reads crowds, all crowds need to be
damped and re-clustered. This makes the approach inefficient. As the
goal of CrowdBuzz is to provide efficient access to the current state of crowds, we
suggest two alternative approaches based on {\scshape GetClusters}.

\noindent{\textbf {Active Crowds}}: In the first approach, we try to get
crowds that have been active in the past $\tau$ time units. A crowd is
defined to be active if there is addition of edges in the crowd in the time
interval $( CurrentTime - \tau, CurrentTime )$. In a practical time-evolving
communication network not all crowds interact in every time interval. Hence, by
focusing on the active crowds only, we can reduce the cost of crowd reporting.
The procedure is given in Algorithm~\ref{alg:get-active-clusters}; the time
complexity of this algorithm is $O(|K|)$.

%Though clusters generated ensure quality, it takes a lot of time to generate
%these clusters.

%*Need to change this according to our story.* The objective of the problem in this paper is to identify groups(clusters) that are currently growing or waning in an interaction graph. We have to get clusters at every interval(small) of time and analyze them. Hence, the speed of the clustering algorithm is relatively a more important factor than quality. To match the requirements of our problem, we suggest two relatively efficient algorithms based on {\scshape GetClusters}. Though we don't get the quality guarantee as before, the clusters we get are found to be useful in our application.

\algsetup{indent=2em}
\newcommand{\GetActiveClusters}{\ensuremath{\mbox{\sc GetActiveClusters}}}
\begin{algorithm}
\caption{$\GetActiveClusters(\tau)$}\label{alg:get-active-clusters}
\begin{algorithmic}
\FORALL{$C_i \in K$}
\IF{Time($C_i$) $\geq (CurrentTime - \tau)$}
\STATE $ActiveClusters = ActiveClusters \cup C_i$
\ENDIF
\ENDFOR
\RETURN $ActiveClusters$
\end{algorithmic}
\end{algorithm}

\noindent{\textbf {Crowds Within a Window}}: In the second approach we determine
all the crowds in the window $( CurrentTime - \tau, CurrentTime )$. This is
different from the previous approach because we get all the crowds instead
of only active crowds. Crowds that have not been re-clustered in this interval
are damped and re-clustered to get the current crowds. This approach is more
efficient than ideal algorithm and we get the entire graph clustered. The
procedure is given in Algorithm~\ref{alg:get-clusters-in-window}.

\algsetup{indent=2em}
\newcommand{\GetClustersInWindow}{\ensuremath{\mbox{\sc GetClustersInWindow}}}
\begin{algorithm}
\caption{$\GetClustersInWindow(\tau)$}\label{alg:get-clusters-in-window}
\begin{algorithmic}
\FORALL{$C_i \in K$}
\IF{Time($C_i$) $< (CurrentTime - \tau)$}
\STATE DampCluster($C_i$)
\STATE LocalCutClustering($C_i$)
\ENDIF
\STATE $ClustersInWindow = ClustersInWindow \cup C_i$
\ENDFOR
\RETURN $ClustersInWindow$
\end{algorithmic}
\end{algorithm}

\begin{figure}[!t]
\begin{center}
\includegraphics[width=3.5in]{../../images/www/runningTime}
\caption{Efficiency comparison: The top figure shows the growth in users and messages; the bottom figure shows the running time ratio between min-cut clustering and the proposed crowd discovery approach.}
\label{fig:running-time}
\end{center}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=3.5in]{../../images/www/ratioAssoc}
\caption{Quality comparison: The top figure shows the growth in users and messages; the bottom figure shows the ratio of ratio-association values for each approach.}
\label{fig:ratio-assoc}
\end{center}
\end{figure}

\section{CrowdBuzz System Architecture}
\label{sec:system-architecture}
The CrowdBuzz system depends on four modules: %as illustrated in
(i) Data Collection; (ii) Crowd Discovery; (iii) Crowd Tracking and Evolution;
and (iv) Crowd Visualization and Analytics. The overall goal of CrowdBuzz is to
support real-time crowd-based social mining capabilities.

%\begin{figure}
%\begin{center}
%\includegraphics[width=\linewidth]{architecture}
%\caption{CrowdBuzz system architecture. [[REPLACE]]}
%\label{fig:architecture}
%\end{center}
%\end{figure}

\noindent{\textbf {Data Collection Module}}: This is a generic module through
which data is fed into the CrowdBuzz application. In our prototype system, we
collect social messages from the Twitter microblogging service through a mix of
crawling and API calls to the Twitter service. On Twitter, users can post status
updates of 140 characters or less. A status update message posted by user $u_1$
including @$<u_2>$ is considered a message from $u_1$ to $u_2$ 
% (note that users
% other than $u_2$ may view this public message as well)
. The data collection
module collects these messages as tuples $(u_1, u_2, i, t)$, where $i$ is the
message sent from user $u_1$ to $u_2$ at time $t$. The collected tuples are then
passed to the Crowd Discovery module. Note that CrowdBuzz architecture can be
flexibly adapted to other domains supporting social messaging services (e.g.,
Facebook).
% , which has recently adopted a similar user-addressable public messaging
% system within their status updates

\noindent{\textbf {Crowd Discovery Module}}: As user messages are passed to
the Crowd Discovery Module, the CrowdBuzz system analyzes the incoming and
existing messages to find groups of users (what we refer to as \textit{crowds})
who are connected by their communication patterns among each other. Intuitively,
a crowd is a time-sensitive collection of users who have messaged each other
within some recent window of time. We formally define the crowd discovery problem
in the following section as a form of clustering in time-evolving social
networks. The Crowd Discovery Module is designed to maintain up-to-date crowds,
so that social mining analytics can be directly run over the discovered crowds at
occasional intervals (e.g., to identify what the latest buzz is among
communicating groups on Twitter).

\noindent{\textbf {Crowd Evolution Module}}: In addition to providing analytic
services over the current batch of crowds, the CrowdBuzz system also tracks the
evolution of crowds via this third module. For example, as groups of users begin
communicating about an upcoming event (say the Rose Bowl football game), the
evolution module can track the users participating in this crowd and give
insights into the crowd dynamics leading up to and after the event. The Crowd
Evolution module can analyze the discovered crowds from the previous module at
system-specified time intervals to provide varying degrees of evolution
granularity (e.g., for tracking very bursty crowds that grow and disperse over
several hours versus longer-lived crowds that may last for weeks).

\noindent{\textbf {Crowd Visualization and Analytics}}: Finally, the discovered
crowds can be visualized using off-the-shelf visualization tools (e.g., Flare
Prefuse) and mined for concept trends and other important social dynamics. In
this paper, we present some example crowd-based analytics in
Section~\ref{sec:experiments}.

In the rest of the paper, we present the design of the Crowd Discovery module
(Section~\ref{sec:crowd-discovery}) and the Crowd Evolution module
(Section~\ref{sec:crowd-evolution}), as well as the prototype CrowdBuzz
evaluation in Section~\ref{sec:experiments}.

\begin{figure}[!t]
\begin{center}
\includegraphics[width=3.5in]{../../images/www/clusterSize}
\caption{Crowd size distribution.}
\label{fig:count-cluster-size}
\end{center}
\end{figure}

\noindent{\textbf {Crowd size distribution}}: We first consider the size of
crowds discovered. The crowd size distribution for a social network can help
quantify the degree of collaboration within the network. In
Figure~\ref{fig:count-cluster-size} we show the crowd size distribution for
crowds of size greater than or equal to 3 users in our Twitter dataset. We see
that most users on Twitter communicate in small groups, but there are some larger
crowds, with a maximum crowd size of 17. Note that these crowd size distributions
are impacted by the degree of edge damping; varying the edge damping factor $\xi$
can result in large inactive crowds (since old messages can impact crowd
formation), or extremely short-lived crowds (by considering only messages within
the past hour, for example).
\begin{figure}[!t]
\begin{center}
\includegraphics[width=3.5in]{../../images/www/single_multi}
\caption{The figure shows difference between a user-centric and group centric
approach to gather \textit{buzz}.}
\label{fig:single-multi}
\end{center}
\end{figure}

\noindent \textbf{On-Demand Crowd Reporting:} Finally, since the crowd evolution
and analytics tools may only require new crowd information at regular intervals
(e.g., every minute, every hour), we can forgo the cost of constant crowd
maintenance between these intervals through the use of on-demand crowd reporting.

\algsetup{indent=2em}
\newcommand{\DampEdge}{\ensuremath{\mbox{\sc DampEdge}}}
\begin{algorithm}
\caption{$\DampEdge(u, v)$}\label{alg:damp-edge}
\begin{algorithmic}

\IF{$CT - EdgeTime(u, v) > 1$}
\STATE $w(u, v)$ = $w(u, v)- \log(CT - EdgeTime(u, v))\times \xi$ 
\ENDIF
\STATE $EdgeTime(u, v)$ =  $CurrentTime$
\end{algorithmic}
\end{algorithm}

\subsection{Temporal and Spatial Locality on Twitter}

\begin{table}[h]
\centering
\label{table:dataset}
\begin{tabular}{|l|r|}
\hline
\textbf{Messages} & \textbf{Percent of Vertices Affected} \\ \hline
100,000 & 0.2\% \\ \hline
200,000 & 0.5\% \\ \hline
300,000 & 0.6\% \\ \hline
400,000 & 0.9\% \\ \hline
500,000 & 0.9\% \\ \hline
600,000 & 1.7\% \\ \hline
700,000 & 1.5\% \\ \hline
800,000 & 1.6\% \\ \hline

%Interacting user pairs & 500,942 & 5,395\\ \hline
%Directed tweets & 1,243,820 & 7,403\\ \hline
%Status update tweets & 2,972,951 & 17,696\\ \hline
%Average degree & 3.48 & - \\ \hline
\end{tabular}
\caption{Locality Stuff.}
\end{table}

\begin{figure}[!t]
\begin{center}
\includegraphics[width=3.5in]{../../images/sigir/dampRatioAssoc}
\caption{Ratio association value at each time interval for different
damping coefficients.}
\label{fig:damp-ratio-assoc}
\end{center}
\end{figure}

%%%
%%%
%%%
%%%
%%%
\begin{figure}[!t]
\begin{center}
\includegraphics[width=3.5in]{../../images/sigir/dampClusterCount}
\caption{Number of crowds and average crowd sizes at each time interval
for different damping coefficients.}
\label{fig:damp-cluster-count}
\end{center}
\end{figure}

### 2011-05-03 docs/csce_675/paper.tex
Added latex for paper.

@@
 
+An architecture for the proposed solution is shown in Figure 1. The various modules of this architecture are as follows:
+
+\begin{itemize}
+  \item \noindent\textbf{Crawler}: This module deals with interacting with social media websites to collect information.
+For this project we will be collecting data from Twitter using Twitter Streaming APIs.
+  \item \noindent\textbf{Filter}: This module removes unwanted data like spam messages, from data collected by the crawler.
+  \item \noindent\textbf{Grouper}: The grouper module analyses the data collected, to determine crowds and adds them to the DBMS. 
+  \item \noindent\textbf{HTTP JSON RESTful APIs}: This module will expose a HTTP-based API that clients can query to get data from the collection. The API will return crowds, users, and their tweets.
+\end{itemize}
+
+\begin{itemize}
+  \item \noindent\textbf{Beanstalk}: Beanstalk is a simple, fast work queue. We use it to connect the crawlers, filters, and groupers together.
+   \item \noindent\textbf{Tornado}: Tornado is an open source, non-blocking web server.  We choose it because it is fast and scalable.
+   \item \noindent\textbf{MongoDB}: MongoDB is a scalable, high-performance, open source, document-oriented database.
+We store the crowds discovered by the framework in this DB.
+The API module interacts with this database to retrieve collections as required by the user query.
+\end{itemize}
+
 \section{Crowd Discovery Algorithm}
 \label{sec:crowd_algorithm}
-
 The grouper deals with the transient crowd discovery and tracking in systems like Facebook and Twitter.

### 2011-05-05 docs/csce_675/paper.tex
Modified latex.
Minor modifications to paper.

--- 2011-05-03 docs/csce_675/paper.tex
@@
 
-\section{Related Work}
-\label{sec:reclated_work}
+% \section{Related Work}
+% \label{sec:reclated_work}
 
@@
 
+An architecture for the proposed solution is shown in Figure 1. The various modules of this architecture are as follows:
+
+\medskip \noindent \textbf{Crawler}: This module deals with interacting with social media websites to collect information.
+For this project we will be collecting data from Twitter using Twitter Streaming APIs.
+We collected tweets from [xxxx] users.
+To collect this set of users we started with a set of 5 users and used snowball sampling to collect more users.
+We then used used the ``follow'' parameter of the filter method from Streaming API to generate a data stream for crowd detection.
+
+\medskip \noindent \textbf{Grouper}: The grouper module analyses the data collected, to determine crowds and adds them to the DBMS.
+This is the central module that detects crowds of different types - communication, content, geo-graphical, etc.
+In this project we will be discovering crowds based on communication only.
+The algorithm to discover crowds is described in Section~\ref{sec:crowd_algorithm}.
+Once crowds are discovered, this module formats crowds to a well defined crowds object and adds it to a DBMS.
+
+\medskip \noindent \textbf{Filter}: This module is used to filter un-necessary data from the framework.
+It can appear both before and after the grouper module depending upon its funcationality.
+In the figure we have showed the module appear before grouper only.
+When the module appears before the grouper, it is used to weed out information unnecessary for the grouper.
+For example in case of crowd detection, it remove information like spam messages.
+When the module appears after the grouper, it cleans the data generated by the grouper.
+For, example in case of crowd detection, it analyzes crowds discovered by the grouper and removes un-necessary crowds, or crowds that don't meet specific quality guarentees.
+The module can also have additional function like search.
+
+% \begin{itemize}
+%   \item \noindent\textbf{Crawler}: This module deals with interacting with social media websites to collect information.
+For this project we will be collecting data from Twitter using Twitter Streaming APIs.
+%   \item \noindent\textbf{Filter}: This module removes unwanted data like spam messages, from data collected by the crawler.
+%   \item \noindent\textbf{Grouper}: The grouper module analyses the data collected, to determine crowds and adds them to the DBMS. 
+%   \item \noindent\textbf{HTTP JSON RESTful APIs}: This module will expose a HTTP-based API that clients can query to get data from the collection.
+The API will return crowds, users, and their tweets.
+% \end{itemize}
+
+% \begin{itemize}
+%   \item \noindent\textbf{Beanstalk}: Beanstalk is a simple, fast work queue. We use it to connect the crawlers, filters, and groupers together.
+%    \item \noindent\textbf{Tornado}: Tornado is an open source, non-blocking web server.  We choose it because it is fast and scalable.
+%    \item \noindent\textbf{MongoDB}: MongoDB is a scalable, high-performance, open source, document-oriented database.
+We store the crowds discovered by the framework in this DB.
+The API module interacts with this database to retrieve collections as required by the user query.
+% \end{itemize}
+
 \section{Crowd Discovery Algorithm}
 \label{sec:crowd_algorithm}
-
 The grouper deals with the transient crowd discovery and tracking in systems like Facebook and Twitter.
@@
 
+{\scriptsize
+ \bibliographystyle{abbrv}
+ \bibliography{sigproc}
+}
+\balancecolumns % GM July 2000
+
 \end{document}

### 2011-05-05 docs/csce_675/paper.tex
Minor modifications to paper.

@@
 
-\section{Architecture}
-\label{sec:architecture}
-\begin{figure}[!t]
-\begin{center}
-\includegraphics[width=3.0in]{images/architecture}
-\caption{Examples for trending phrases discovery problem.}
-\label{fig:candidate_phrases}
-\end{center}
-\end{figure}
-
-An architecture for the proposed solution is shown in Figure 1. The various modules of this architecture are as follows:
-
-\medskip \noindent \textbf{Crawler}: This module deals with interacting with social media websites to collect information.
-For this project we will be collecting data from Twitter using Twitter Streaming APIs.
-We collected tweets from [xxxx] users.
-To collect this set of users we started with a set of 5 users and used snowball sampling to collect more users.
-We then used used the ``follow'' parameter of the filter method from Streaming API to generate a data stream for crowd detection.
-
-\medskip \noindent \textbf{Grouper}: The grouper module analyses the data collected, to determine crowds and adds them to the DBMS.
-This is the central module that detects crowds of different types - communication, content, geo-graphical, etc.
-In this project we will be discovering crowds based on communication only.
-The algorithm to discover crowds is described in Section~\ref{sec:crowd_algorithm}.
-Once crowds are discovered, this module formats crowds to a well defined crowds object and adds it to a DBMS.
-
-\medskip \noindent \textbf{Filter}: This module is used to filter un-necessary data from the framework.
-It can appear both before and after the grouper module depending upon its funcationality.
-In the figure we have showed the module appear before grouper only.
-When the module appears before the grouper, it is used to weed out information unnecessary for the grouper.
-For example in case of crowd detection, it remove information like spam messages.
-When the module appears after the grouper, it cleans the data generated by the grouper.
-For, example in case of crowd detection, it analyzes crowds discovered by the grouper and removes un-necessary crowds, or crowds that don't meet specific quality guarentees.
-The module can also have additional function like search.
-
-% \begin{itemize}
-%   \item \noindent\textbf{Crawler}: This module deals with interacting with social media websites to collect information.
-For this project we will be collecting data from Twitter using Twitter Streaming APIs.
-%   \item \noindent\textbf{Filter}: This module removes unwanted data like spam messages, from data collected by the crawler.
-%   \item \noindent\textbf{Grouper}: The grouper module analyses the data collected, to determine crowds and adds them to the DBMS. 
-%   \item \noindent\textbf{HTTP JSON RESTful APIs}: This module will expose a HTTP-based API that clients can query to get data from the collection.
-The API will return crowds, users, and their tweets.
-% \end{itemize}
-
-% \begin{itemize}
-%   \item \noindent\textbf{Beanstalk}: Beanstalk is a simple, fast work queue. We use it to connect the crawlers, filters, and groupers together.
-%    \item \noindent\textbf{Tornado}: Tornado is an open source, non-blocking web server.  We choose it because it is fast and scalable.
-%    \item \noindent\textbf{MongoDB}: MongoDB is a scalable, high-performance, open source, document-oriented database.
-We store the crowds discovered by the framework in this DB.
-The API module interacts with this database to retrieve collections as required by the user query.
-% \end{itemize}
-
 \section{Crowd Discovery Algorithm}
 \label{sec:crowd_algorithm}
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{images/intro}
+\caption{Example of crowd discovery and tracking in Twitter.}
+\label{fig:intro-example}
+\end{figure}
+To illustrate the problem of crowd discovery, consider the simple example in
+Figure~\ref{fig:intro-example}. At time t=1, users A and B send messages to each
+other, as do users C and D.\footnote{For simplicity, the example discretizes
+time so that all messages between users occur in steps. In practice, the proposed
+algorithm relaxes this assumption and can handle arbitrary message sending
+times.} The associated communication graph shows an edge between the two pairs,
+where for simplicity the edge is annotated with the number of messages between
+the users (2, in both cases). Further, suppose we identify crowds based purely on
+graph connectivity. So for time t=1, we see there are two crowds discovered
+\{A,B\} and \{C,D\}. For each crowd, we can characterize the semantics of their
+communication with simple keywords extracted from the content of the tweets:
+(``oil'', ``gulf'') and (``walcott'', ``capello''). At time t=2, the
+communication graph is updated with a new edge (connecting User A and User C),
+and the existing edges are decayed by one (again, a simplifying assumption for
+the purposes of this example). A single crowd is discovered since all users are
+connected via edges with non-zero edge weights. At time t=3, User D leaves the
+main crowd since no messages to or from User D have been observed since time t=1.
+This process continues until time t=5 when User C also leaves the main crowd due
+to inactivity. Note that crowds are discovered from communication graph only and
+not from the content of the messages. As an example of crowd tracking, we can
+track the evolution of the yellow crowd across time periods, observing the
+changes it goes through as it grows in size from t=1 to t=2 and then reduces to
+two users by t=5.
+
 The grouper deals with the transient crowd discovery and tracking in systems like Facebook and Twitter.
@@
 
+\section{Architecture}
+\label{sec:architecture}
+\begin{figure}[!t]
+\begin{center}
+\includegraphics[width=3.0in]{images/architecture}
+\caption{Examples for trending phrases discovery problem.}
+\label{fig:candidate_phrases}
+\end{center}
+\end{figure}
+
+An architecture for the proposed solution is shown in Figure 1. The various modules of this architecture are as follows:
+
+\medskip \noindent \textbf{Crawler}: This module deals with interacting with social media websites to collect information.
+For this project we will be collecting data from Twitter using Twitter Streaming APIs.
+We collected tweets from [xxxx] users.
+To collect this set of users we started with a set of 5 users and used snowball sampling to collect more users.
+We then used used the ``follow'' parameter of the filter method from Streaming API to generate a data stream for crowd detection.
+
+\medskip \noindent \textbf{Grouper}: The grouper module analyses the data collected, to determine crowds and adds them to the DBMS.
+This is the central module that detects crowds of different types - communication, content, geo-graphical, etc.
+In this project we will be discovering crowds based on communication only.
+The algorithm to discover crowds is described in Section~\ref{sec:crowd_algorithm}.
+Once crowds are discovered, this module formats crowds to a well defined crowds object and adds it to a DBMS.
+
+\medskip \noindent \textbf{Filter}: This module is used to filter un-necessary data from the framework.
+It can appear both before and after the grouper module depending upon its funcationality.
+In the figure we have showed the module appear before grouper only.
+When the module appears before the grouper, it is used to weed out information unnecessary for the grouper.
+For example in case of crowd detection, it remove information like spam messages.
+When the module appears after the grouper, it cleans the data generated by the grouper.
+For, example in case of crowd detection, it analyzes crowds discovered by the grouper and removes un-necessary crowds, or crowds that don't meet specific quality guarentees.
+The module can also have additional functions that support features like search.
+
+\medskip \noindent \textbf{HTTP JSON RESTful APIs}: This module provides client an interface to the digital library.
+The module exposes JSON APIs that the clients can use to browze and search the crowds archive.
+
+\begin{itemize}
+  \item \noindent\textbf{Beanstalk}: Beanstalk is a simple, fast work queue. We use it to connect the crawlers, filters, and groupers together.
+   \item \noindent\textbf{Tornado}: Tornado is an open source, non-blocking web server.  We choose it because it is fast and scalable.
+   \item \noindent\textbf{MongoDB}: MongoDB is a scalable, high-performance, open source, document-oriented database.
+We store the crowds discovered by the framework in this DB.
+The API module interacts with this database to retrieve collections as required by the user query.
+\end{itemize}
+
 \section{Conclusion}

### 2011-05-05 docs/csce_675/paper.tex
Minor modifications to paper.

@@
 
-% \section{Related Work}
-% \label{sec:reclated_work}
+\section{Related Work}
+Twitter\footnote{http://www.twitter.com} is a microblogging platform which is
+fast gaining popularity\cite{Oreilly:2009} among broad sections of society and
+has a global outreach spreading from developed, urban nations like the United
+States where it has a high adoption rate \cite{Java:2007}, to developing
+countries in parts of Asia and South America.
+
+Along with working on understanding microblogging usage and communities
+\cite{Java:2007}, the main author - Akshay Java was one of the first few who
+dealt with the measurement of the usage and nature of communities in
+microblogging. In his latter study \cite{Java:2008}, he presented his
+observations of the microblogging phenomena and user intentions by studying the
+content, topological and geographical properties of such communities. He found
+that microblogging provides users with a more immediate form of communication
+to talk about their daily activities and to seek or share information.
+
+When it comes to visualization of the social crowd, a tool which in some ways
+shows similar objectives as us and stands out among the rest is Vizster
+\cite{Heer:2005}. It is a visualization system for which can be used for
+exploration and navigation of the social networks of any scale. The system
+provides facilities to improve the functionalities like discovering people or
+connections which can help in promoting awareness of community structure and
+exposure to information. It maintains a fun element to it while providing these
+given features. It was aimed to provide specific end-users, functionalities
+like situated exploration and visual analysis of big-scale communities. It is
+based on a design of network layouts which have features like supporting visual
+search and analysis, exploring connectivity in large graphs and automatic
+identification and visualization of structures of communities.
+
+Another related study was on how web-based retrieval from twitter can be used
+as knowledge base \cite{Cheong:2009} which shows that the visualization system
+we try to attempt can be helpful. Marc Cheong et al. in this study tried to
+analyze demographics of the Twitter users and attempted to provide and analyze
+the trend in Twitter into what's going on in the real world. They enabled us to
+understand the underlying characteristics behind the trend setting in Twitter
+and thereby providing a new perspective on the contributors of a trend. They
+used visualization techniques along with artificial intelligence-based data
+mining methods to classify the Twitter messages dealing with the trend topic.
+
+Identifying highly dynamic ad-hoc collections of users what we refer to as
+crowds in massive social messaging systems like Twitter and Facebook is
+important \cite{krishna:2010}. Kamath et al. in the study suggest an
+efficient locality-based clustering approach for identifying crowds of users in
+near real-time compared to more heavyweight static clustering algorithm. The
+study consisted of 711,612 users and 61.3 million messages, and tells what
+approaches to follow to efficiently and effectively identify Twitter-based
+crowds.
+
+In the other study based on the previous one, Kamath et al
+\cite{krishna:2011}, they add another salient feature - a novel crowd tracking
+and evolution approach for linking crowds across time periods. Unlike the more
+static and long-lived group-based membership offered on many social networks
+their goal was to support the discovery of organic and highly-temporal group
+affiliation, which they refer to as ``transient crowds''. A transient crowd
+according to them is a potentially short-lived ad-hoc collection of users bound
+together by some common thread - which can be communication-based,
+location-based or interest based. We are inspired by this idea of formation and
+detection of crowds. We try to implement detection of crowd in Crowdy in a
+similar fashion.
+
+Some other studies related come from areas like social network visualization,
+short text visualization, progressive disclosure, and user modeling. Considering
+social network visualization , studies like \cite{Boyd:2008} by Boyd et al described features
+of on-line social networking sites and the history of the social networking sites,
+and the changes during their developments.Deeper understanding of the social
+networks can help boost the research in social network visualization. In Moreno's
+following work \cite{Moreno:1953}, he emphasized the use of pictorial representations to map
+social relations and the embedded patterns. He considered people as nodes in the
+network and relations between people as the edges in the network.Laumann et al
+\cite{Laumann:1966} applied computational procedure, multidimensional scaling to locate nodes in
+visualizing network. The authors are also the first to plot the networks in three
+dimensions. Other examples of good visualizations can be Facebook Friend Wheel
+\cite{facebook_wheel} which visualizes a Facebook user's network of friends in a wheel format and
+Trendsmap \cite{trends_map} which plots real time trending topics over two-dimensional (latitude,
+longitude) world map, and you can zoom in to see the trending topics for a specific
+location or an area.
+
+In the area of short text visualization, studies like \cite{Bishop:2007} tell that these social
+web-sites serve to fulfill their users' desires to interact with and help others.
+The authors also proposed a 3-level framework for understanding why members of online
+communities participate or not. According to the 3-level framework, users make
+comments or short-text post to have their voice be heard. Leggett and Shipman \cite{Leggett:04} 
+proposed and described the characteristic of interactive communication in seven
+dimensions in a similar way to examine characteristics of communication for a
+commenting system like roles,voices,interaction,indirection,history,narrative
+and media. In \cite{Hsu:09}, they tried to understand how an on-line community itself
+perceives the relative quality of its own user-contributed content and further
+used the information to promote valuable opinion from the flood of comments
+that attached to each social object.We compared three different visualization
+approaches including the traditional list view, the quantitative aggregation
+view and the personalized space view. We learned that, to best present massive
+metadata such as user contributed comments to the end user, a personalized
+filtering model is needed and that a 2D space positional layout is desired
+such as in the case of Plurk and Opinion Space systems.
+
+In the area of progressive disclosure, Phan et al built a prototype of a system
+that visualized packet traces from a computer network \cite{Phan:07} which is similar to
+the problem investigated. They introduced the concept of progressive multiples
+which combines progressive disclosure with small multiples. In Scalability in
+System Management GUIs \cite{Dieberger:06}, the authors use semantic zooming to show information
+about network configuration at various levels of detail, which can tell about
+the way progressive disclosure can be used for system administrators.In An
+Interactive Ambient Visualization for Code Smells \cite{Murphy:10}, the authors describe a
+method for alerting uses about code that may need refactoring. They created a
+plug-in for Eclipse that detected questionable code and alerts the programmer.
+This shows progressive disclosure for software developers.
+
+Involving user models and visualization into the picture, studies like \cite{Schlungbaum:97} tell
+that the individualization often depends on the user's expectation of the user
+interface which might be adapted or adaptable or adaptive user interface. Papers
+like \cite{Ho:01} explain that the user model selection is crucial for any tool and how
+the visualization can help in the discovering and building knowledge. Data and
+knowledge visualization module of such a system can be used to help the user
+interaction in other modules. This helps in better user interaction experience
+irrespective of which module of the system he/she is interacting with.The user's
+knowledge, preferences, goals etc. are generally included in the user model when
+visualization is concerned in such tools \cite{Henderson}. Also, critical factors like cognitive
+load on the user ought to be considered when such tools are made to ensure
+effectiveness.The identification of target users is also a important factor to be
+considered.Model-based tools like TADEUS can include explicit task and user models
+in their system, over potential to work in integrated user interface development
+environments and support the entire user interface life cycle. Although research
+papers like \cite{Schlungbaum:97}, talk about how different software tools can be used for helping
+the user designers create interfaces with consideration of user models , there have
+been efforts to combine user model with task and domain models to help developers
+in creating and designing user interface \cite{Tran:10}. Systems like DB-USE along with TADEUS
+help us in understanding of how user model can be combined with other models to help
+in creating/designing better user interface for applications which are mainly
+concerned with visualization.
 
@@
 
+\subsection{Sample Crowds Discovered}
+\begin{figure}[!t]
+\centering
+\includegraphics[width=\linewidth]{images/clusterExamplesOverTime}
+\caption{Examples of the crowds discovered in the dataset.}
+\label{fig:cluster-example}
+\end{figure}
+We illustrate
+some of the discovered crowds and their lifespans in
+Figure~\ref{fig:cluster-example}, with an annotation next to the crowd peak
+showing the topic of discussion. We see a crowd (shown in black)
+discussing Sarah Palin and the Vice-Presidential debate from the $40^{th}$ hour
+to $80^{th}$ hour that peaks around the time of the actual debate. We
+observe that crowds that talk about general everyday things have a greater
+lifespan than crowds discussing specific events. For example in
+Figure~\ref{fig:cluster-example}, a crowd (annotated with \textit{thank, whats,
+wow}) discussing everyday things lives through the entire week, while, during the
+same period we observe several event-specific crowds, like crowds discussing the
+Red Sox, Sarah Palin, and Girl's Night Out (gno) forming and dispersing. These
+event-specific crowds start forming just before the event and die a few intervals
+after the completion of that event. This distinction between the crowds
+discovered clearly indicates two types of Twitter usage: first, it is used as a
+platform to discuss and debate specific events, and second, it as also used a means of
+everyday communication.
+
 \section{Architecture}

### 2011-05-05 docs/csce_675/paper.tex
Made minor modifications to paper.

@@
 social relations and the embedded patterns. He considered people as nodes in the
-network and relations between people as the edges in the network.Laumann et al
+network and relations between people as the edges in the network. Laumann et al
 \cite{Laumann:1966} applied computational procedure, multidimensional scaling to locate nodes in
@@
 
+\subsection{Tools}
+
+The tool we used to develop this framework are as follows:
 \begin{itemize}
+ \item \noindent\textbf{PyLucene}: To provide the search functionality we use Apache Lucene.
+It provides methods for text indexing and searching.
+To integrate Lucene with our framework we use Pylucene which is a Python wrapper for Lucene.
+This is used in the filter module of our architecture.
+ \item \noindent\textbf{CherryPy}: This is an object-oriented web framework for Python. The JSON REST API that interface the digital library with clients is hosted using this web framework.
+ \item \noindent\textbf{NetworkX}: This is a library for manipulating graphs in Python.
+We use this to determine quality of crowds generated by crowd detection framework and filter out crowds of poor quality.
+This sits in the filter module.
   \item \noindent\textbf{Beanstalk}: Beanstalk is a simple, fast work queue. We use it to connect the crawlers, filters, and groupers together.
-   \item \noindent\textbf{Tornado}: Tornado is an open source, non-blocking web server.  We choose it because it is fast and scalable.
    \item \noindent\textbf{MongoDB}: MongoDB is a scalable, high-performance, open source, document-oriented database.
@@
 
-{\scriptsize
+{
  \bibliographystyle{abbrv}

### 2011-05-05 docs/csce_675/paper.tex
Modified related work.

--- 2011-05-05 docs/csce_675/paper.tex
@@
 
-% \section{Related Work}
-% \label{sec:reclated_work}
+\section{Related Work}
+Twitter\footnote{http://www.twitter.com} is a microblogging platform which is
+fast gaining popularity\cite{Oreilly:2009} among broad sections of society and
+has a global outreach spreading from developed, urban nations like the United
+States where it has a high adoption rate \cite{Java:2007}, to developing
+countries in parts of Asia and South America.
+
+Along with working on understanding microblogging usage and communities
+\cite{Java:2007}, the main author - Akshay Java was one of the first few who
+dealt with the measurement of the usage and nature of communities in
+microblogging. In his latter study \cite{Java:2008}, he presented his
+observations of the microblogging phenomena and user intentions by studying the
+content, topological and geographical properties of such communities. He found
+that microblogging provides users with a more immediate form of communication
+to talk about their daily activities and to seek or share information.
+
+%When it comes to visualization of the social crowd, a tool which in some ways
+%shows similar objectives as us and stands out among the rest is Vizster
+%\cite{Heer:2005}. It is a visualization system for which can be used for
+%exploration and navigation of the social networks of any scale. The system
+%provides facilities to improve the functionalities like discovering people or
+%connections which can help in promoting awareness of community structure and
+%exposure to information. It maintains a fun element to it while providing these
+%given features. It was aimed to provide specific end-users, functionalities
+%like situated exploration and visual analysis of big-scale communities. It is
+%based on a design of network layouts which have features like supporting visual
+%search and analysis, exploring connectivity in large graphs and automatic
+%identification and visualization of structures of communities.
+
+%Another related study was on how web-based retrieval from twitter can be used
+%as knowledge base \cite{Cheong:2009} which shows that the visualization system
+%we try to attempt can be helpful. Marc Cheong et al. in this study tried to
+%analyze demographics of the Twitter users and attempted to provide and analyze
+%the trend in Twitter into what's going on in the real world. They enabled us to
+%understand the underlying characteristics behind the trend setting in Twitter
+%and thereby providing a new perspective on the contributors of a trend. They
+%used visualization techniques along with artificial intelligence-based data
+%mining methods to classify the Twitter messages dealing with the trend topic.
+
+Identifying highly dynamic ad-hoc collections of users what we refer to as
+crowds in massive social messaging systems like Twitter and Facebook is
+important \cite{krishna:2010}. Kamath et al. in the study suggest an
+efficient locality-based clustering approach for identifying crowds of users in
+near real-time compared to more heavyweight static clustering algorithm. The
+study consisted of 711,612 users and 61.3 million messages, and tells what
+approaches to follow to efficiently and effectively identify Twitter-based
+crowds.
+
+In the other study based on the previous one, Kamath et al
+\cite{krishna:2011}, they add another salient feature - a novel crowd tracking
+and evolution approach for linking crowds across time periods. Unlike the more
+static and long-lived group-based membership offered on many social networks
+their goal was to support the discovery of organic and highly-temporal group
+affiliation, which they refer to as ``transient crowds''. A transient crowd
+according to them is a potentially short-lived ad-hoc collection of users bound
+together by some common thread - which can be communication-based,
+location-based or interest based. We are inspired by this idea of formation and
+detection of crowds. We try to implement detection of crowd in Crowdy in a
+similar fashion.
+
+%Some other studies related come from areas like social network visualization,
+%short text visualization, progressive disclosure, and user modeling. Considering
+%social network visualization , studies like \cite{Boyd:2008} by Boyd et al described features
+%of on-line social networking sites and the history of the social networking sites,
+%and the changes during their developments.Deeper understanding of the social
+%networks can help boost the research in social network visualization. In Moreno's
+%following work \cite{Moreno:1953}, he emphasized the use of pictorial representations to map
+%social relations and the embedded patterns. He considered people as nodes in the
+%network and relations between people as the edges in the network. Laumann et al
+%\cite{Laumann:1966} applied computational procedure, multidimensional scaling to locate nodes in
+%visualizing network. The authors are also the first to plot the networks in three
+%dimensions. Other examples of good visualizations can be Facebook Friend Wheel
+%\cite{facebook_wheel} which visualizes a Facebook user's network of friends in a wheel format and
+%Trendsmap \cite{trends_map} which plots real time trending topics over two-dimensional (latitude,
+%longitude) world map, and you can zoom in to see the trending topics for a specific
+%location or an area.
+
+%In the area of short text visualization, studies like \cite{Bishop:2007} tell that these social
+%web-sites serve to fulfill their users' desires to interact with and help others.
+%The authors also proposed a 3-level framework for understanding why members of online
+%communities participate or not. According to the 3-level framework, users make
+%comments or short-text post to have their voice be heard. Leggett and Shipman \cite{Leggett:04} 
+%proposed and described the characteristic of interactive communication in seven
+%dimensions in a similar way to examine characteristics of communication for a
+%commenting system like roles,voices,interaction,indirection,history,narrative
+%and media. In \cite{Hsu:09}, they tried to understand how an on-line community itself
+%perceives the relative quality of its own user-contributed content and further
+%used the information to promote valuable opinion from the flood of comments
+%that attached to each social object.We compared three different visualization
+%approaches including the traditional list view, the quantitative aggregation
+%view and the personalized space view. We learned that, to best present massive
+%metadata such as user contributed comments to the end user, a personalized
+%filtering model is needed and that a 2D space positional layout is desired
+%such as in the case of Plurk and Opinion Space systems.
+
+%In the area of progressive disclosure, Phan et al built a prototype of a system
+%that visualized packet traces from a computer network \cite{Phan:07} which is similar to
+%the problem investigated. They introduced the concept of progressive multiples
+%which combines progressive disclosure with small multiples. In Scalability in
+%System Management GUIs \cite{Dieberger:06}, the authors use semantic zooming to show information
+%about network configuration at various levels of detail, which can tell about
+%the way progressive disclosure can be used for system administrators.In An
+%Interactive Ambient Visualization for Code Smells \cite{Murphy:10}, the authors describe a
+%method for alerting uses about code that may need refactoring. They created a
+%plug-in for Eclipse that detected questionable code and alerts the programmer.
+%This shows progressive disclosure for software developers.
+
+%Involving user models and visualization into the picture, studies like \cite{Schlungbaum:97} tell
+%that the individualization often depends on the user's expectation of the user
+%interface which might be adapted or adaptable or adaptive user interface. Papers
+%like \cite{Ho:01} explain that the user model selection is crucial for any tool and how
+%the visualization can help in the discovering and building knowledge. Data and
+%knowledge visualization module of such a system can be used to help the user
+%interaction in other modules. This helps in better user interaction experience
+%irrespective of which module of the system he/she is interacting with.The user's
+%knowledge, preferences, goals etc. are generally included in the user model when
+%visualization is concerned in such tools \cite{Henderson}. Also, critical factors like cognitive
+%load on the user ought to be considered when such tools are made to ensure
+%effectiveness.The identification of target users is also a important factor to be
+%considered.Model-based tools like TADEUS can include explicit task and user models
+%in their system, over potential to work in integrated user interface development
+%environments and support the entire user interface life cycle. Although research
+%papers like \cite{Schlungbaum:97}, talk about how different software tools can be used for helping
+%the user designers create interfaces with consideration of user models , there have
+%been efforts to combine user model with task and domain models to help developers
+%in creating and designing user interface \cite{Tran:10}. Systems like DB-USE along with TADEUS
+%help us in understanding of how user model can be combined with other models to help
+%in creating/designing better user interface for applications which are mainly
+%concerned with visualization.
 

### 2011-05-05 docs/csce_675/paper.tex
Modified related work.

@@
 \label{sec:conclusion}
+In this project, we presented a framework of a digital library for transient crowds in highly-dynamic social messaging systems like Twitter and Facebook.
+We built a framework that allows an analyst or curious user to find interesting crowds and see how they evolve.
+The framework enabled clients to interact with the library using JSON APIs.
+The APIs enabled searching and browsing of the digital library.
 

### 2011-05-05 docs/csce_675/paper.tex
working on architecture

@@
 
-An architecture for the proposed solution is shown in Figure 1. The various modules of this architecture are as follows:
+An architecture for our solution is shown in Figure 1.  Data flows from a
+crawler, through zero or more filters, to a grouper, and then through zero or
+more filters, and then it is finally stored in a MongoDB database.  The various
+modules of this architecture are as follows:
 
-\medskip \noindent \textbf{Crawler}: This module deals with interacting with social media websites to collect information.
-For this project we will be collecting data from Twitter using Twitter Streaming APIs.
-We collected tweets from [xxxx] users.
-To collect this set of users we started with a set of 5 users and used snowball sampling to collect more users.
-We then used used the ``follow'' parameter of the filter method from Streaming API to generate a data stream for crowd detection.
+\subsection{Crawler}
+Crawlers interact with social media websites to collect information. All of the
+crawlers we use in this project acquire tweets and users from Twitter using
+their APIs.
 
-\medskip \noindent \textbf{Grouper}: The grouper module analyses the data collected, to determine crowds and adds them to the DBMS.
-This is the central module that detects crowds of different types - communication, content, geo-graphical, etc.
-In this project we will be discovering crowds based on communication only.
-The algorithm to discover crowds is described in Section~\ref{sec:crowd_algorithm}.
-Once crowds are discovered, this module formats crowds to a well defined crowds object and adds it to a DBMS.
+\medskip \noindent \textbf{Localcrawl}: This crawler collects data from users
+in a region using the standard Twitter API. We started with a tiny sample set
+of seed users. It uses snowball sampling to collect more users that are likely
+to live in an area. Once we have a list of users
 
-\medskip \noindent \textbf{Filter}: This module is used to filter un-necessary data from the framework.
-It can appear both before and after the grouper module depending upon its funcationality.
-In the figure we have showed the module appear before grouper only.
-When the module appears before the grouper, it is used to weed out information unnecessary for the grouper.
-For example in case of crowd detection, it remove information like spam messages.
-When the module appears after the grouper, it cleans the data generated by the grouper.
-For, example in case of crowd detection, it analyzes crowds discovered by the grouper and removes un-necessary crowds, or crowds that don't meet specific quality guarentees.
-The module can also have additional functions that support features like search.
+We have used this crawler and the crowd detection algorithms on both Bryan/College
+Station and the Houston area, but the demo is currently exclusively running on the
+Bryan/College Station data.
+
+\medskip \noindent \textbf{GeoStream}: This crawler listens to Twitter's
+streaming API to find geo-located tweets.  It recieves every geo-located tweet
+posted from anywhere in the world.  In the future, this data may be used to
+show crowds on a map.
+
+\subsection{Grouper}
+Groupers detect crowds in the data collected by a crawler.  The precise
+definition of a crowd depends on the implementation of the grouper.  A grouper
+could create crowds based on comunication patterns, geographical proximity, or
+textual similarity. Once crowds are discovered, this module formats crowds to a
+well defined crowds object and adds it to a DBMS.
+
+\medskip \noindent \textbf{Mentions}:
+For this project, we exclusivly discover crowds based on communtion.
+
+...
+
+The grouper module analyses the data
+collected, to determine crowds and adds them to the DBMS. This is the central
+module that detects crowds of different types - communication, content,
+geo-graphical, etc. In this project we will be discovering crowds based on
+communication only. The algorithm to discover crowds is described in
+Section~\ref{sec:crowd_algorithm}.
+
+\subsection{Filter}
+Filters are used to remove unnecessary data and 
+\medskip \noindent \textbf{Filter}: This module is used to filter un-necessary
+data from the framework. It can appear both before and after the grouper module
+depending upon its funcationality. In the figure we have showed the module
+appear before grouper only. When the module appears before the grouper, it is
+used to weed out information unnecessary for the grouper. For example in case
+of crowd detection, it remove information like spam messages. When the module
+appears after the grouper, it cleans the data generated by the grouper. For,
+example in case of crowd detection, it analyzes crowds discovered by the
+grouper and removes un-necessary crowds, or crowds that don't meet specific
+quality guarentees. The module can also have additional functions that support
+features like search.
 

### 2011-05-05 docs/csce_675/paper.tex
Added introduction.

@@
 
+In much the same way as web search engines provide instant access to the
+\textit{retrospective web} of previously crawled and indexed content, there is
+growing excitement over a new generation of applications for monitoring,
+analyzing, and distilling information from the \textit{prospective web} of
+real-time content that reflects the current activity of the web's participants. As a step towards this vision of a prospective web information platform, this
+paper developing a digital library for ``hotspots'' on the real-time social web.
+In general, a ``hotspot'' could be defined by the posting and sharing actions of
+users in social systems, for example triggered by an offline event (e.g.,
+Facebook posts and Tweets in response to a live Presidential debate or a chemical
+fire at a nearby refinery) or by an online phenomenon (e.g., reaction to Internet
+memes, online discussion). Detecting these hotspots as they arise in real-time and providing a framework for browsing and searching them, is
+an important and fundamental building block for enabling new real-time web
+applications, applications related to identification and dissemination of
+disaster and emergency-related information, among many other emerging social
+mining applications.
+
+In Section~\ref{sec:related_work}, we describe some papers that discuss the problem we are interested in and in Section~\ref{sec:crowd_algorithm}, we briefly describe our method to discover crowds.
+We finally present our architecture in Section~\ref{sec:architecture}.
+
 \section{Related Work}
+\label{sec:related_work}
 Twitter\footnote{http://www.twitter.com} is a microblogging platform which is
@@
 to talk about their daily activities and to seek or share information.
-
-%When it comes to visualization of the social crowd, a tool which in some ways
-%shows similar objectives as us and stands out among the rest is Vizster
-%\cite{Heer:2005}. It is a visualization system for which can be used for
-%exploration and navigation of the social networks of any scale. The system
-%provides facilities to improve the functionalities like discovering people or
-%connections which can help in promoting awareness of community structure and
-%exposure to information. It maintains a fun element to it while providing these
-%given features. It was aimed to provide specific end-users, functionalities
-%like situated exploration and visual analysis of big-scale communities. It is
-%based on a design of network layouts which have features like supporting visual
-%search and analysis, exploring connectivity in large graphs and automatic
-%identification and visualization of structures of communities.
-
-%Another related study was on how web-based retrieval from twitter can be used
-%as knowledge base \cite{Cheong:2009} which shows that the visualization system
-%we try to attempt can be helpful. Marc Cheong et al. in this study tried to
-%analyze demographics of the Twitter users and attempted to provide and analyze
-%the trend in Twitter into what's going on in the real world. They enabled us to
-%understand the underlying characteristics behind the trend setting in Twitter
-%and thereby providing a new perspective on the contributors of a trend. They
-%used visualization techniques along with artificial intelligence-based data
-%mining methods to classify the Twitter messages dealing with the trend topic.
 
@@
 similar fashion.
-
-%Some other studies related come from areas like social network visualization,
-%short text visualization, progressive disclosure, and user modeling. Considering
-%social network visualization , studies like \cite{Boyd:2008} by Boyd et al described features
-%of on-line social networking sites and the history of the social networking sites,
-%and the changes during their developments.Deeper understanding of the social
-%networks can help boost the research in social network visualization. In Moreno's
-%following work \cite{Moreno:1953}, he emphasized the use of pictorial representations to map
-%social relations and the embedded patterns. He considered people as nodes in the
-%network and relations between people as the edges in the network. Laumann et al
-%\cite{Laumann:1966} applied computational procedure, multidimensional scaling to locate nodes in
-%visualizing network. The authors are also the first to plot the networks in three
-%dimensions. Other examples of good visualizations can be Facebook Friend Wheel
-%\cite{facebook_wheel} which visualizes a Facebook user's network of friends in a wheel format and
-%Trendsmap \cite{trends_map} which plots real time trending topics over two-dimensional (latitude,
-%longitude) world map, and you can zoom in to see the trending topics for a specific
-%location or an area.
-
-%In the area of short text visualization, studies like \cite{Bishop:2007} tell that these social
-%web-sites serve to fulfill their users' desires to interact with and help others.
-%The authors also proposed a 3-level framework for understanding why members of online
-%communities participate or not. According to the 3-level framework, users make
-%comments or short-text post to have their voice be heard. Leggett and Shipman \cite{Leggett:04} 
-%proposed and described the characteristic of interactive communication in seven
-%dimensions in a similar way to examine characteristics of communication for a
-%commenting system like roles,voices,interaction,indirection,history,narrative
-%and media. In \cite{Hsu:09}, they tried to understand how an on-line community itself
-%perceives the relative quality of its own user-contributed content and further
-%used the information to promote valuable opinion from the flood of comments
-%that attached to each social object.We compared three different visualization
-%approaches including the traditional list view, the quantitative aggregation
-%view and the personalized space view. We learned that, to best present massive
-%metadata such as user contributed comments to the end user, a personalized
-%filtering model is needed and that a 2D space positional layout is desired
-%such as in the case of Plurk and Opinion Space systems.
-
-%In the area of progressive disclosure, Phan et al built a prototype of a system
-%that visualized packet traces from a computer network \cite{Phan:07} which is similar to
-%the problem investigated. They introduced the concept of progressive multiples
-%which combines progressive disclosure with small multiples. In Scalability in
-%System Management GUIs \cite{Dieberger:06}, the authors use semantic zooming to show information
-%about network configuration at various levels of detail, which can tell about
-%the way progressive disclosure can be used for system administrators.In An
-%Interactive Ambient Visualization for Code Smells \cite{Murphy:10}, the authors describe a
-%method for alerting uses about code that may need refactoring. They created a
-%plug-in for Eclipse that detected questionable code and alerts the programmer.
-%This shows progressive disclosure for software developers.
-
-%Involving user models and visualization into the picture, studies like \cite{Schlungbaum:97} tell
-%that the individualization often depends on the user's expectation of the user
-%interface which might be adapted or adaptable or adaptive user interface. Papers
-%like \cite{Ho:01} explain that the user model selection is crucial for any tool and how
-%the visualization can help in the discovering and building knowledge. Data and
-%knowledge visualization module of such a system can be used to help the user
-%interaction in other modules. This helps in better user interaction experience
-%irrespective of which module of the system he/she is interacting with.The user's
-%knowledge, preferences, goals etc. are generally included in the user model when
-%visualization is concerned in such tools \cite{Henderson}. Also, critical factors like cognitive
-%load on the user ought to be considered when such tools are made to ensure
-%effectiveness.The identification of target users is also a important factor to be
-%considered.Model-based tools like TADEUS can include explicit task and user models
-%in their system, over potential to work in integrated user interface development
-%environments and support the entire user interface life cycle. Although research
-%papers like \cite{Schlungbaum:97}, talk about how different software tools can be used for helping
-%the user designers create interfaces with consideration of user models , there have
-%been efforts to combine user model with task and domain models to help developers
-%in creating and designing user interface \cite{Tran:10}. Systems like DB-USE along with TADEUS
-%help us in understanding of how user model can be combined with other models to help
-%in creating/designing better user interface for applications which are mainly
-%concerned with visualization.
 

### 2011-05-05 docs/csce_675/paper.tex
added more about the modules

--- 2011-05-05 docs/csce_675/paper.tex
@@
 crawler, through zero or more filters, to a grouper, and then through zero or
-more filters, and then it is finally stored in a MongoDB database.  The various
-modules of this architecture are as follows:
+more filters, and then it is finally stored in a MongoDB database.  We went
+with an extremely modular architecture to make the system flexible.  We can
+easily integrate new crawlers, filters, and groupers into the system.The
+various modules of this architecture are described in the remainder of this
+section.
 
@@
 
-\medskip \noindent \textbf{Localcrawl}: This crawler collects data from users
+\subsubsection{Localcrawl}
+This crawler collects data from users
 in a region using the standard Twitter API. We started with a tiny sample set
@@
 
-\medskip \noindent \textbf{GeoStream}: This crawler listens to Twitter's
+\subsubsection{GeoStream}
+This crawler listens to Twitter's
 streaming API to find geo-located tweets.  It recieves every geo-located tweet
@@
 
-\medskip \noindent \textbf{Mentions}:
-For this project, we exclusivly discover crowds based on communtion.
-
-...
-
-The grouper module analyses the data
-collected, to determine crowds and adds them to the DBMS. This is the central
-module that detects crowds of different types - communication, content,
-geo-graphical, etc. In this project we will be discovering crowds based on
-communication only. The algorithm to discover crowds is described in
+\subsubsection{Mentions}
+For this project, we exclusivly discover crowds based on communication.  The
+mentions grouper looks for sets of people who are communicating with each
+other.  The algorithm to discover crowds is described in
 Section~\ref{sec:crowd_algorithm}.
@@
 \subsection{Filter}
-Filters are used to remove unnecessary data and 
-\medskip \noindent \textbf{Filter}: This module is used to filter un-necessary
-data from the framework. It can appear both before and after the grouper module
-depending upon its funcationality. In the figure we have showed the module
-appear before grouper only. When the module appears before the grouper, it is
-used to weed out information unnecessary for the grouper. For example in case
-of crowd detection, it remove information like spam messages. When the module
-appears after the grouper, it cleans the data generated by the grouper. For,
-example in case of crowd detection, it analyzes crowds discovered by the
-grouper and removes un-necessary crowds, or crowds that don't meet specific
-quality guarentees. The module can also have additional functions that support
-features like search.
+Filters are used to remove unnecessary data, such as spam tweets, and add
+automatically generated metadata to tweets, users, and crowds.  A filter can
+appear before or after the grouper module as needed.  In the following
+sections, we discuss two filters that we implemented and several that we plan
+to add in the future.
 
-\medskip \noindent \textbf{HTTP JSON RESTful APIs}: This module provides client an interface to the digital library.
-The module exposes JSON APIs that the clients can use to browze and search the crowds archive.
+\subsubsection{Lucene Filter}
+The Lucene module creates a Lucene index from the text of the tweets in a
+crowd.  This index is used to speed up searching through the text of the
+tweets. This filter is designed so that a crowd can be updated as new data
+arrives from a crowd.
+
+\subsubsection{Network Filter}
+We also have a network filter that builds a graph that represents the
+communication between the users in a crowd. At the moment, it analyzes two things:
+degree centrality and clustering coefficient.  The degree centrality is used to
+find the most important users in a given crowd. The clustering coefficient of
+the crowd is added to the crowd as automatically generated metadata
+
+\subsubsection{Planned Filters}
+There are several filters that we have not implemented, but may implement in
+the future. The ability to easily add new filters and create an automated
+workflow is an important part of our design.
+\begin{itemize}
+\item Remove users that appear to be spammers.
+\item Add metadata to each user that contains an estimate of the users
+    location, and some information about the quality of the estimate.
+\item Find the key terms in a crowd and add that metadata to the crowd.
+\item Summarize the tweets from a crowd.
+\end{itemize}
+
+\subsection{HTTP JSON RESTful APIs}: This module provides client an interface to the digital library. The module exposes JSON APIs that the clients can use to browse and search the crowds archive.
 

### 2011-05-05 docs/csce_675/paper.tex
added api info

@@
 
-\subsection{HTTP JSON RESTful APIs}: This module provides client an interface to the digital library. The module exposes JSON APIs that the clients can use to browse and search the crowds archive.
+\subsection{HTTP JSON RESTful APIs}: This module provides client an interface to the digital library.
+The module exposes JSON APIs that the clients can use to browse and search the crowds archive.
+Here is a brief description of the more important methods:
+\begin{description}
+ \item[search/crowd] Find crowds sorted by relevance or time.
+ \item[crowd/id] Retrieve all of the data for a crowd.
+ \item[crowd/users] Retrieve a list of all the users in the crowd.
+ \item[crowd/tweets] Retrieve a list of all the tweets in the crowd.
+ \item[crowd/star] Mark a crowd as significant.
+ \item[user/edges] Retrieve the friend and follower relationships for a given user.
+\begin{description}
 

### 2011-05-05 docs/csce_675/paper.tex
fixed minor bug - that crashed pdflatex
fixed spelling

@@
 communication network (spatial locality) and recent changes to the network
-(temporal locality), for supporting efficient transient crowd discovery. The complete algorithm is decsribed in \cite{Kamath:2011:TCD}
+(temporal locality), for supporting efficient transient crowd discovery. The complete algorithm is described in \cite{Kamath:2011:TCD}
 
@@
 This crawler listens to Twitter's
-streaming API to find geo-located tweets.  It recieves every geo-located tweet
+streaming API to find geo-located tweets.  It receives every geo-located tweet
 posted from anywhere in the world.  In the future, this data may be used to
@@
 definition of a crowd depends on the implementation of the grouper.  A grouper
-could create crowds based on comunication patterns, geographical proximity, or
+could create crowds based on communication patterns, geographical proximity, or
 textual similarity. Once crowds are discovered, this module formats crowds to a
@@
 \subsubsection{Mentions}
-For this project, we exclusivly discover crowds based on communication.  The
+For this project, we exclusively discover crowds based on communication.  The
 mentions grouper looks for sets of people who are communicating with each
@@
  \item[user/edges] Retrieve the friend and follower relationships for a given user.
-\begin{description}
+\end{description}
 

### 2011-07-19 serve.py
modified code for fcgi

@@ -27,8 +27,26 @@ if __name__ == '__main__':
             name=settings.mongo_database,
             host=settings.mongo_host)
         cherrypy.config.update("etc/crowdy.conf")
-        cherrypy.tree.mount(api,"/api/1",config="etc/api.conf")
-        cherrypy.quickstart(web,"/",config="etc/web.conf")
+        # Code added for fastcgi
+        if "--fastcgi" in sys.argv:
+#            app = cherrypy.tree.mount(WebPWMan())
+            app = cherrypy.tree.mount(api,"/api/1",config="etc/api.conf")
+            # CherryPy autoreload must be disabled for the flup server to work
+            
+            cherrypy.config.update({'engine.autoreload_on':False})
+            cherrypy.config.update({
+                    "tools.sessions.on": True,
+                    "tools.sessions.timeout": 5,
+                    "log.screen": False,
+                    "log.access_file": "/tmp/cherry_access.log",
+                    "log.error_file": "/tmp/cherry_error.log",
+            })
+            from flup.server.fcgi import WSGIServer
+            cherrypy.config.update({'engine.autoreload_on':False})
+            WSGIServer(app).run()
+        else:
+            cherrypy.tree.mount(api,"/api/1",config="etc/api.conf")
+            cherrypy.quickstart(web,"/",config="etc/web.conf")
     except:
         traceback.print_exc()
         pdb.post_mortem(sys.exc_info()[2])

### 2011-07-19 serve.py
modified server for fcgi

@@ -30,7 +30,7 @@ if __name__ == '__main__':
         # Code added for fastcgi
         if "--fastcgi" in sys.argv:
 #            app = cherrypy.tree.mount(WebPWMan())
-            app = cherrypy.tree.mount(api,"/api/1",config="etc/api.conf")
+            app = cherrypy.tree.mount(api,os.path.dirname(os.path.abspath(__file__))+"/api/1",config="etc/api.conf")
             # CherryPy autoreload must be disabled for the flup server to work
             
             cherrypy.config.update({'engine.autoreload_on':False})

### 2011-07-20 serve.py
modified server for fcgi

@@ -26,11 +26,10 @@ if __name__ == '__main__':
         maroon.Model.database = maroon.MongoDB(
             name=settings.mongo_database,
             host=settings.mongo_host)
-        cherrypy.config.update("etc/crowdy.conf")
         # Code added for fastcgi
         if "--fastcgi" in sys.argv:
-#            app = cherrypy.tree.mount(WebPWMan())
-            app = cherrypy.tree.mount(api,os.path.dirname(os.path.abspath(__file__))+"/api/1",config="etc/api.conf")
+            app = cherrypy.tree.mount(api)
+#            app = cherrypy.tree.mount(api,os.path.dirname(os.path.abspath(__file__))+"/api/1",config="etc/api.conf")
             # CherryPy autoreload must be disabled for the flup server to work
             
             cherrypy.config.update({'engine.autoreload_on':False})
@@ -45,6 +44,7 @@ if __name__ == '__main__':
             cherrypy.config.update({'engine.autoreload_on':False})
             WSGIServer(app).run()
         else:
+            cherrypy.config.update("etc/crowdy.conf")
             cherrypy.tree.mount(api,"/api/1",config="etc/api.conf")
             cherrypy.quickstart(web,"/",config="etc/web.conf")
     except:

### 2011-07-20 serve.py
modified server for fcgi

@@ -28,10 +28,10 @@ if __name__ == '__main__':
             host=settings.mongo_host)
         # Code added for fastcgi
         if "--fastcgi" in sys.argv:
-            app = cherrypy.tree.mount(api)
-#            app = cherrypy.tree.mount(api,os.path.dirname(os.path.abspath(__file__))+"/api/1",config="etc/api.conf")
-            # CherryPy autoreload must be disabled for the flup server to work
+#            app = cherrypy.tree.mount(api)
+            cherrypy.tree.mount(api,os.path.dirname(os.path.abspath(__file__))+"/api/1",config=os.path.dirname(os.path.abspath(__file__))+"/etc/api.conf")
             
+            # CherryPy autoreload must be disabled for the flup server to work
             cherrypy.config.update({'engine.autoreload_on':False})
             cherrypy.config.update({
                     "tools.sessions.on": True,
@@ -42,7 +42,7 @@ if __name__ == '__main__':
             })
             from flup.server.fcgi import WSGIServer
             cherrypy.config.update({'engine.autoreload_on':False})
-            WSGIServer(app).run()
+            WSGIServer(web,script_name="/",config="etc/web.conf").run()
         else:
             cherrypy.config.update("etc/crowdy.conf")
             cherrypy.tree.mount(api,"/api/1",config="etc/api.conf")

### 2011-07-20 serve.py
modified server for fcgi

@@ -42,7 +42,7 @@ if __name__ == '__main__':
             })
             from flup.server.fcgi import WSGIServer
             cherrypy.config.update({'engine.autoreload_on':False})
-            WSGIServer(web,script_name="/",config="etc/web.conf").run()
+            WSGIServer(web,script_name="/",config=os.path.dirname(os.path.abspath(__file__))+"/etc/web.conf").run()
         else:
             cherrypy.config.update("etc/crowdy.conf")
             cherrypy.tree.mount(api,"/api/1",config="etc/api.conf")

### 2011-07-20 serve.py
modified server for fcgi

@@ -1,6 +1,6 @@
 #!/usr/bin/env python
 import traceback
-import pdb
+import pdb, os
 import sys
 
 import cherrypy

### 2011-07-20 serve.py
modified server for fcgi

@@ -42,7 +42,7 @@ if __name__ == '__main__':
             })
             from flup.server.fcgi import WSGIServer
             cherrypy.config.update({'engine.autoreload_on':False})
-            WSGIServer(web,script_name="/",config=os.path.dirname(os.path.abspath(__file__))+"/etc/web.conf").run()
+            WSGIServer(web).run()
         else:
             cherrypy.config.update("etc/crowdy.conf")
             cherrypy.tree.mount(api,"/api/1",config="etc/api.conf")

### 2011-07-20 serve.py
modified serve for fcgi

@@ -22,31 +22,31 @@ if __name__ == '__main__':
     except ImportError:
         print "WARNING: ignoring lucene"
 
-    try:
-        maroon.Model.database = maroon.MongoDB(
-            name=settings.mongo_database,
-            host=settings.mongo_host)
-        # Code added for fastcgi
-        if "--fastcgi" in sys.argv:
+#    try:
+    maroon.Model.database = maroon.MongoDB(
+        name=settings.mongo_database,
+        host=settings.mongo_host)
+    # Code added for fastcgi
+    if "--fastcgi" in sys.argv:
 #            app = cherrypy.tree.mount(api)
-            cherrypy.tree.mount(api,os.path.dirname(os.path.abspath(__file__))+"/api/1",config=os.path.dirname(os.path.abspath(__file__))+"/etc/api.conf")
-            
-            # CherryPy autoreload must be disabled for the flup server to work
-            cherrypy.config.update({'engine.autoreload_on':False})
-            cherrypy.config.update({
-                    "tools.sessions.on": True,
-                    "tools.sessions.timeout": 5,
-                    "log.screen": False,
-                    "log.access_file": "/tmp/cherry_access.log",
-                    "log.error_file": "/tmp/cherry_error.log",
-            })
-            from flup.server.fcgi import WSGIServer
-            cherrypy.config.update({'engine.autoreload_on':False})
-            WSGIServer(web).run()
-        else:
-            cherrypy.config.update("etc/crowdy.conf")
-            cherrypy.tree.mount(api,"/api/1",config="etc/api.conf")
-            cherrypy.quickstart(web,"/",config="etc/web.conf")
-    except:
-        traceback.print_exc()
-        pdb.post_mortem(sys.exc_info()[2])
+        cherrypy.tree.mount(api,os.path.dirname(os.path.abspath(__file__))+"/api/1",config=os.path.dirname(os.path.abspath(__file__))+"/etc/api.conf")
+        
+        # CherryPy autoreload must be disabled for the flup server to work
+        cherrypy.config.update({'engine.autoreload_on':False})
+        cherrypy.config.update({
+                "tools.sessions.on": True,
+                "tools.sessions.timeout": 5,
+                "log.screen": False,
+                "log.access_file": "/tmp/cherry_access.log",
+                "log.error_file": "/tmp/cherry_error.log",
+        })
+        from flup.server.fcgi import WSGIServer
[…]

### 2011-07-20 hello.py
playing with fcgi

@@ -1,0 +1,28 @@
+'''
+Created on Jul 20, 2011
+
+@author: kykamath
+'''
+import cherrypy, sys
+
+class HelloWorld:
+    def index(self):
+        return "Hello world!"
+    index.exposed = True
+    
+if "--fastcgi" in sys.argv:
+    app = cherrypy.tree.mount(HelloWorld())
+    # CherryPy autoreload must be disabled for the flup server to work
+    cherrypy.config.update({'engine.autoreload_on':False})
+    cherrypy.config.update({
+            "tools.sessions.on": True,
+            "tools.sessions.timeout": 5,
+            "log.screen": False,
+            "log.access_file": "/tmp/cherry_access.log",
+            "log.error_file": "/tmp/cherry_error.log",
+    })
+    from flup.server.fcgi import WSGIServer
+    cherrypy.config.update({'engine.autoreload_on':False})
+    WSGIServer(app).run()
+else:
+    cherrypy.quickstart(HelloWorld(), config="hello.conf")

### 2011-07-20 serve.py
modified conf

@@ -30,6 +30,7 @@ if __name__ == '__main__':
     if "--fastcgi" in sys.argv:
 #            app = cherrypy.tree.mount(api)
         cherrypy.tree.mount(api,os.path.dirname(os.path.abspath(__file__))+"/api/1",config=os.path.dirname(os.path.abspath(__file__))+"/etc/api.conf")
+        cherrypy.tree.mount(web,os.path.dirname(os.path.abspath(__file__))+"/web",config=os.path.dirname(os.path.abspath(__file__))+"/etc/web.conf")
         
         # CherryPy autoreload must be disabled for the flup server to work
         cherrypy.config.update({'engine.autoreload_on':False})

### 2011-07-20 hello.py
modified conf

@@ -25,4 +25,6 @@ if "--fastcgi" in sys.argv:
     cherrypy.config.update({'engine.autoreload_on':False})
     WSGIServer(app).run()
 else:
+    cherrypy.config.update("etc/crowdy.conf")
+#    cherrypy.tree.mount(api,"/api/1",config="etc/api.conf")
     cherrypy.quickstart(HelloWorld(), config="hello.conf")

### 2011-07-20 hello.py
modified conf

@@ -25,6 +25,4 @@ if "--fastcgi" in sys.argv:
     cherrypy.config.update({'engine.autoreload_on':False})
     WSGIServer(app).run()
 else:
-    cherrypy.config.update("etc/crowdy.conf")
-#    cherrypy.tree.mount(api,"/api/1",config="etc/api.conf")
     cherrypy.quickstart(HelloWorld(), config="hello.conf")

### 2011-07-20 hello.py
modified conf

@@ -11,18 +11,22 @@ class HelloWorld:
     index.exposed = True
     
 if "--fastcgi" in sys.argv:
-    app = cherrypy.tree.mount(HelloWorld())
+#    app = cherrypy.tree.mount(HelloWorld())
+#    # CherryPy autoreload must be disabled for the flup server to work
+#    cherrypy.config.update('hello.conf')
+#    cherrypy.config.update({'engine.autoreload_on':False})
+#    cherrypy.config.update({
+#            "tools.sessions.on": True,
+#            "tools.sessions.timeout": 5,
+#            "log.screen": False,
+#            "log.access_file": "/tmp/cherry_access.log",
+#            "log.error_file": "/tmp/cherry_error.log",
+#    })
+#    from flup.server.fcgi import WSGIServer
+#    cherrypy.config.update({'engine.autoreload_on':False})
+#    WSGIServer(app).run()
+    cherrypy.tree.mount(HelloWorld())
     # CherryPy autoreload must be disabled for the flup server to work
     cherrypy.config.update({'engine.autoreload_on':False})
-    cherrypy.config.update({
-            "tools.sessions.on": True,
-            "tools.sessions.timeout": 5,
-            "log.screen": False,
-            "log.access_file": "/tmp/cherry_access.log",
-            "log.error_file": "/tmp/cherry_error.log",
-    })
-    from flup.server.fcgi import WSGIServer
-    cherrypy.config.update({'engine.autoreload_on':False})
-    WSGIServer(app).run()
 else:
     cherrypy.quickstart(HelloWorld(), config="hello.conf")

### 2011-07-20 hello.py
modified conf

@@ -1,32 +1,46 @@
-'''
-Created on Jul 20, 2011
+#'''
+#Created on Jul 20, 2011
+#
+#@author: kykamath
+#'''
+#import cherrypy, sys
+#
+#class HelloWorld:
+#    def index(self):
+#        return "Hello world!"
+#    index.exposed = True
+#    
+#if "--fastcgi" in sys.argv:
+##    app = cherrypy.tree.mount(HelloWorld())
+##    # CherryPy autoreload must be disabled for the flup server to work
+##    cherrypy.config.update('hello.conf')
+##    cherrypy.config.update({'engine.autoreload_on':False})
+##    cherrypy.config.update({
+##            "tools.sessions.on": True,
+##            "tools.sessions.timeout": 5,
+##            "log.screen": False,
+##            "log.access_file": "/tmp/cherry_access.log",
+##            "log.error_file": "/tmp/cherry_error.log",
+##    })
+##    from flup.server.fcgi import WSGIServer
+##    cherrypy.config.update({'engine.autoreload_on':False})
+##    WSGIServer(app).run()
+#    cherrypy.tree.mount(HelloWorld())
+#    # CherryPy autoreload must be disabled for the flup server to work
+#    cherrypy.config.update({'engine.autoreload_on':False})
+#else:
+#    cherrypy.quickstart(HelloWorld(), config="hello.conf")
 
-@author: kykamath
-'''
-import cherrypy, sys
+
+#!/usr/bin/python
+import cherrypy
 
 class HelloWorld:
+    """Sample request handler class."""
     def index(self):
         return "Hello world!"
     index.exposed = True
-    
-if "--fastcgi" in sys.argv:
-#    app = cherrypy.tree.mount(HelloWorld())
-#    # CherryPy autoreload must be disabled for the flup server to work
-#    cherrypy.config.update('hello.conf')
-#    cherrypy.config.update({'engine.autoreload_on':False})
-#    cherrypy.config.update({
-#            "tools.sessions.on": True,
-#            "tools.sessions.timeout": 5,
-#            "log.screen": False,
-#            "log.access_file": "/tmp/cherry_access.log",
-#            "log.error_file": "/tmp/cherry_error.log",
-#    })
-#    from flup.server.fcgi import WSGIServer
-#    cherrypy.config.update({'engine.autoreload_on':False})
-#    WSGIServer(app).run()
-    cherrypy.tree.mount(HelloWorld())
[…]

### 2011-07-20 hello.py
modified conf

@@ -1,46 +1,46 @@
-#'''
-#Created on Jul 20, 2011
-#
-#@author: kykamath
-#'''
-#import cherrypy, sys
-#
-#class HelloWorld:
-#    def index(self):
-#        return "Hello world!"
-#    index.exposed = True
-#    
-#if "--fastcgi" in sys.argv:
-##    app = cherrypy.tree.mount(HelloWorld())
-##    # CherryPy autoreload must be disabled for the flup server to work
-##    cherrypy.config.update('hello.conf')
-##    cherrypy.config.update({'engine.autoreload_on':False})
-##    cherrypy.config.update({
-##            "tools.sessions.on": True,
-##            "tools.sessions.timeout": 5,
-##            "log.screen": False,
-##            "log.access_file": "/tmp/cherry_access.log",
-##            "log.error_file": "/tmp/cherry_error.log",
-##    })
-##    from flup.server.fcgi import WSGIServer
-##    cherrypy.config.update({'engine.autoreload_on':False})
-##    WSGIServer(app).run()
-#    cherrypy.tree.mount(HelloWorld())
-#    # CherryPy autoreload must be disabled for the flup server to work
-#    cherrypy.config.update({'engine.autoreload_on':False})
-#else:
-#    cherrypy.quickstart(HelloWorld(), config="hello.conf")
+'''
+Created on Jul 20, 2011
 
-
-#!/usr/bin/python
-import cherrypy
+@author: kykamath
+'''
+import cherrypy, sys
 
 class HelloWorld:
-    """Sample request handler class."""
     def index(self):
         return "Hello world!"
     index.exposed = True
+    
+if "--fastcgi" in sys.argv:
+#    app = cherrypy.tree.mount(HelloWorld())
+#    # CherryPy autoreload must be disabled for the flup server to work
+#    cherrypy.config.update('hello.conf')
+#    cherrypy.config.update({'engine.autoreload_on':False})
+#    cherrypy.config.update({
+#            "tools.sessions.on": True,
+#            "tools.sessions.timeout": 5,
+#            "log.screen": False,
+#            "log.access_file": "/tmp/cherry_access.log",
+#            "log.error_file": "/tmp/cherry_error.log",
+#    })
+#    from flup.server.fcgi import WSGIServer
+#    cherrypy.config.update({'engine.autoreload_on':False})
+#    WSGIServer(app).run()
+    cherrypy.tree.mount(HelloWorld())
[…]

### 2011-07-20 hello.py
modified conf

@@ -25,9 +25,13 @@ if "--fastcgi" in sys.argv:
 #    from flup.server.fcgi import WSGIServer
 #    cherrypy.config.update({'engine.autoreload_on':False})
 #    WSGIServer(app).run()
-    cherrypy.tree.mount(HelloWorld())
+
+    app = cherrypy.tree.mount(HelloWorld())
+    cherrypy.config.update(os.path.dirname(os.path.abspath(__file__))+'/hello.conf')
     # CherryPy autoreload must be disabled for the flup server to work
     cherrypy.config.update({'engine.autoreload_on':False})
+    from flup.server.fcgi import WSGIServer
+    WSGIServer(app).run()
 else:
     cherrypy.quickstart(HelloWorld(), config="hello.conf")
 

### 2011-07-20 hello.py
modified conf

@@ -3,7 +3,7 @@ Created on Jul 20, 2011
 
 @author: kykamath
 '''
-import cherrypy, sys
+import cherrypy, sys, os
 
 class HelloWorld:
     def index(self):

### 2011-07-20 hello.py
modified conf

@@ -31,7 +31,7 @@ if "--fastcgi" in sys.argv:
     # CherryPy autoreload must be disabled for the flup server to work
     cherrypy.config.update({'engine.autoreload_on':False})
     from flup.server.fcgi import WSGIServer
-    WSGIServer(app).run()
+    WSGIServer(app, bindAddress=('0.0.0.0', 8000)).run()
 else:
     cherrypy.quickstart(HelloWorld(), config="hello.conf")
 

### 2011-07-20 hello.py
modified conf

@@ -1,50 +1,50 @@
-'''
-Created on Jul 20, 2011
-
-@author: kykamath
-'''
-import cherrypy, sys, os
-
-class HelloWorld:
-    def index(self):
-        return "Hello world!"
-    index.exposed = True
-    
-if "--fastcgi" in sys.argv:
-#    app = cherrypy.tree.mount(HelloWorld())
-#    # CherryPy autoreload must be disabled for the flup server to work
-#    cherrypy.config.update('hello.conf')
-#    cherrypy.config.update({'engine.autoreload_on':False})
-#    cherrypy.config.update({
-#            "tools.sessions.on": True,
-#            "tools.sessions.timeout": 5,
-#            "log.screen": False,
-#            "log.access_file": "/tmp/cherry_access.log",
-#            "log.error_file": "/tmp/cherry_error.log",
-#    })
-#    from flup.server.fcgi import WSGIServer
-#    cherrypy.config.update({'engine.autoreload_on':False})
-#    WSGIServer(app).run()
-
-    app = cherrypy.tree.mount(HelloWorld())
-    cherrypy.config.update(os.path.dirname(os.path.abspath(__file__))+'/hello.conf')
-    # CherryPy autoreload must be disabled for the flup server to work
-    cherrypy.config.update({'engine.autoreload_on':False})
-    from flup.server.fcgi import WSGIServer
-    WSGIServer(app, bindAddress=('0.0.0.0', 8000)).run()
-else:
-    cherrypy.quickstart(HelloWorld(), config="hello.conf")
-
-
-##!/usr/bin/python
-#import cherrypy
+#'''
+#Created on Jul 20, 2011
+#
+#@author: kykamath
+#'''
+#import cherrypy, sys, os
 #
 #class HelloWorld:
-#    """Sample request handler class."""
 #    def index(self):
 #        return "Hello world!"
 #    index.exposed = True
+#    
+#if "--fastcgi" in sys.argv:
+##    app = cherrypy.tree.mount(HelloWorld())
+##    # CherryPy autoreload must be disabled for the flup server to work
+##    cherrypy.config.update('hello.conf')
+##    cherrypy.config.update({'engine.autoreload_on':False})
+##    cherrypy.config.update({
+##            "tools.sessions.on": True,
+##            "tools.sessions.timeout": 5,
+##            "log.screen": False,
+##            "log.access_file": "/tmp/cherry_access.log",
[…]

### 2011-07-20 hello.py
modified conf

@@ -45,6 +45,7 @@ class HelloWorld:
         return "Hello world!"
     index.exposed = True
 
-cherrypy.tree.mount(HelloWorld())
-# CherryPy autoreload must be disabled for the flup server to work
-cherrypy.config.update({'engine.autoreload_on':False})
+#cherrypy.tree.mount(HelloWorld())
+## CherryPy autoreload must be disabled for the flup server to work
+#cherrypy.config.update({'engine.autoreload_on':False})
+cherrypy.quickstart(HelloWorld(), config="hello.conf")

### 2011-07-20 hello.py
modified conf

@@ -45,7 +45,8 @@ class HelloWorld:
         return "Hello world!"
     index.exposed = True
 
-#cherrypy.tree.mount(HelloWorld())
-## CherryPy autoreload must be disabled for the flup server to work
-#cherrypy.config.update({'engine.autoreload_on':False})
-cherrypy.quickstart(HelloWorld(), config="hello.conf")
+cherrypy.tree.mount(HelloWorld())
+cherrypy.config.update("hello.conf")
+# CherryPy autoreload must be disabled for the flup server to work
+cherrypy.config.update({'engine.autoreload_on':False})
+#cherrypy.quickstart(HelloWorld(), config="hello.conf")

### 2011-07-20 hello.py
modified helllo

@@ -1,52 +1,60 @@
-#'''
-#Created on Jul 20, 2011
-#
-#@author: kykamath
-#'''
-#import cherrypy, sys, os
-#
-#class HelloWorld:
-#    def index(self):
-#        return "Hello world!"
-#    index.exposed = True
-#    
-#if "--fastcgi" in sys.argv:
-##    app = cherrypy.tree.mount(HelloWorld())
-##    # CherryPy autoreload must be disabled for the flup server to work
-##    cherrypy.config.update('hello.conf')
-##    cherrypy.config.update({'engine.autoreload_on':False})
-##    cherrypy.config.update({
-##            "tools.sessions.on": True,
-##            "tools.sessions.timeout": 5,
-##            "log.screen": False,
-##            "log.access_file": "/tmp/cherry_access.log",
-##            "log.error_file": "/tmp/cherry_error.log",
-##    })
-##    from flup.server.fcgi import WSGIServer
-##    cherrypy.config.update({'engine.autoreload_on':False})
-##    WSGIServer(app).run()
-#
-#    app = cherrypy.tree.mount(HelloWorld())
-#    cherrypy.config.update(os.path.dirname(os.path.abspath(__file__))+'/hello.conf')
-#    # CherryPy autoreload must be disabled for the flup server to work
-#    cherrypy.config.update({'engine.autoreload_on':False})
-#    from flup.server.fcgi import WSGIServer
-#    WSGIServer(app, bindAddress=('0.0.0.0', 8000)).run()
-#else:
-#    cherrypy.quickstart(HelloWorld(), config="hello.conf")
+'''
+Created on Jul 20, 2011
 
-
-#!/usr/bin/python
-import cherrypy
+@author: kykamath
+'''
+import cherrypy, sys, os
 
 class HelloWorld:
-    """Sample request handler class."""
     def index(self):
         return "Hello world!"
     index.exposed = True
+    
+if "--fastcgi" in sys.argv:
+#    app = cherrypy.tree.mount(HelloWorld())
+#    # CherryPy autoreload must be disabled for the flup server to work
+#    cherrypy.config.update('hello.conf')
+#    cherrypy.config.update({'engine.autoreload_on':False})
+#    cherrypy.config.update({
+#            "tools.sessions.on": True,
+#            "tools.sessions.timeout": 5,
+#            "log.screen": False,
+#            "log.access_file": "/tmp/cherry_access.log",
[…]

### 2011-07-20 hello.py
modified helllo

@@ -7,7 +7,7 @@ import cherrypy, sys, os
 
 class HelloWorld:
     def index(self):
-        return "Hello world!"
+        return "Hello world! ilab"
     index.exposed = True
     
 if "--fastcgi" in sys.argv:

### 2011-07-21 serve.py
made it work with fcgi

@@ -1,15 +1,17 @@
 #!/usr/bin/env python
 import traceback
-import pdb, os
+import pdb
 import sys
 
 import cherrypy
 from cherrypy import tools
+from cherrypy.process import plugins, servers
 import maroon
 
 from etc.settings import settings
 import api
 import web
+
 
 if __name__ == '__main__':
     try:
@@ -22,32 +24,29 @@ if __name__ == '__main__':
     except ImportError:
         print "WARNING: ignoring lucene"
 
-#    try:
-    maroon.Model.database = maroon.MongoDB(
-        name=settings.mongo_database,
-        host=settings.mongo_host)
-    # Code added for fastcgi
-    if "--fastcgi" in sys.argv:
-#            app = cherrypy.tree.mount(api)
-        cherrypy.tree.mount(api,os.path.dirname(os.path.abspath(__file__))+"/api/1",config=os.path.dirname(os.path.abspath(__file__))+"/etc/api.conf")
-        cherrypy.tree.mount(web,os.path.dirname(os.path.abspath(__file__))+"/web",config=os.path.dirname(os.path.abspath(__file__))+"/etc/web.conf")
-        
-        # CherryPy autoreload must be disabled for the flup server to work
-        cherrypy.config.update({'engine.autoreload_on':False})
-        cherrypy.config.update({
-                "tools.sessions.on": True,
-                "tools.sessions.timeout": 5,
-                "log.screen": False,
-                "log.access_file": "/tmp/cherry_access.log",
-                "log.error_file": "/tmp/cherry_error.log",
-        })
-        from flup.server.fcgi import WSGIServer
-        cherrypy.config.update({'engine.autoreload_on':False})
-        WSGIServer(web).run()
-    else:
+    try:
+        maroon.Model.database = maroon.MongoDB(
+            name=settings.mongo_database,
+            host=settings.mongo_host)
         cherrypy.config.update("etc/crowdy.conf")
         cherrypy.tree.mount(api,"/api/1",config="etc/api.conf")
-        cherrypy.quickstart(web,"/",config="etc/web.conf")
-#    except:
-#        traceback.print_exc()
-#        pdb.post_mortem(sys.exc_info()[2])
+        cherrypy.tree.mount(web, "/", config="etc/web.conf")
+
+        engine = cherrypy.engine
+        if hasattr(engine, "signal_handler"):
+            engine.signal_handler.subscribe()
+        if hasattr(engine, "console_control_handler"):
[…]

### 2011-07-21 etc/settings.py
run fcgi server if settings.production is True

@@ -14,6 +14,7 @@ settings = SettingsBunch(
     log_dir = 'logs',
     lucene_index_dir = '/tmp/twitter_search',
     pdb = pdb.set_trace,
+    production = False,
 )
 
 try:

### 2011-07-21 serve.py

@@ -28,25 +28,31 @@ if __name__ == '__main__':
         maroon.Model.database = maroon.MongoDB(
             name=settings.mongo_database,
             host=settings.mongo_host)
-        cherrypy.config.update("etc/crowdy.conf")
-        cherrypy.tree.mount(api,"/api/1",config="etc/api.conf")
-        cherrypy.tree.mount(web, "/", config="etc/web.conf")
 
-        engine = cherrypy.engine
-        if hasattr(engine, "signal_handler"):
-            engine.signal_handler.subscribe()
-        if hasattr(engine, "console_control_handler"):
-            engine.console_control_handler.subscribe()
-        cherrypy.config.update({'engine.autoreload_on': False})
-        cherrypy.server.unsubscribe()
-        addr = cherrypy.server.bind_addr
-        f = servers.FlupFCGIServer(application=cherrypy.tree,
-                                   bindAddress=addr)
-        s = servers.ServerAdapter(engine, httpserver=f, bind_addr=addr)
-        s.subscribe()
+        if settings.production:
+            cherrypy.config.update("etc/crowdy_prod.conf")
+            cherrypy.tree.mount(api,"/api/1",config="etc/api.conf")
+            cherrypy.tree.mount(web, "/", config="etc/web.conf")
 
-        engine.start()
-        engine.block()
+            # taken from the cherryd script
+            engine = cherrypy.engine
+            if hasattr(engine, "signal_handler"):
+                engine.signal_handler.subscribe()
+            if hasattr(engine, "console_control_handler"):
+                engine.console_control_handler.subscribe()
+            cherrypy.server.unsubscribe()
+            addr = cherrypy.server.bind_addr
+            f = servers.FlupFCGIServer(application=cherrypy.tree,
+                                       bindAddress=addr)
+            s = servers.ServerAdapter(engine, httpserver=f, bind_addr=addr)
+            s.subscribe()
+
+            engine.start()
+            engine.block()
+        else:
+            cherrypy.config.update("etc/crowdy.conf")
+            cherrypy.tree.mount(api,"/api/1",config="etc/api.conf")
+            cherrypy.quickstart(web,"/",config="etc/web.conf")
     except:
         traceback.print_exc()
 

### 2011-07-21 web/static/scripts/crowd_network.js
open overlay in list view

@@ -157,10 +157,22 @@ function loadTweets(div, tweets) {
   $(".scrollable").scrollable({mousewheel:true, vertical:true});
 }
 
-function loadCrowdPopup(cid, elem, crowd_info) {
-    elem.find('.tabs').tabs("div.pane")
-    loadCrowdNetworkGraph(elem.find('canvas'), crowd_info.users, crowd_info.index);
-    $('#startTime').html(new Date(1000*crowd_info.crowd.start).toString())
-    $('#endTime').html(new Date(1000*crowd_info.crowd.end).toString())
-    loadTweets($('#crowdTweets'), crowd_info.tweets)
+function loadCrowdPopup(ev) {
+    var elem = $("#crowdBox")
+    elem.html("Loading...")
+    jQuery.getJSON('/crowd/'+ev.data.cid, function(crowd_info) {
+        elem.html(crowd_info.html)
+        elem.overlay({
+            load: true,
+            mask: {
+              color: '#000',
+              effect: 'apple'
+            }
+        });
+        elem.find('.tabs').tabs("div.pane")
+        loadCrowdNetworkGraph(elem.find('canvas'), crowd_info.users, crowd_info.index);
+        $('#startTime').html(new Date(1000*crowd_info.crowd.start).toString())
+        $('#endTime').html(new Date(1000*crowd_info.crowd.end).toString())
+        loadTweets($('#crowdTweets'), crowd_info.tweets)
+    });
 }

### 2011-07-21 intake/ats/KeyWords.py
modified keywords generation code

@@ -10,7 +10,7 @@ from itertools import groupby
 from operator import itemgetter
 
 class KeyWords:
-    mongodb_connection = Connection('sid', 27017)
+    mongodb_connection = Connection('sarge', 27017)
     tweets = mongodb_connection.hou.Tweet
     crowds = mongodb_connection.hou.Crowd
     crowdTweets = mongodb_connection.hou.CrowdTweets

### 2011-07-22 web/root.py
cleaned up tabs and made everything 900px wide

@@ -22,22 +22,17 @@ def _render(path, **kwargs):
 
 @cherrypy.expose
 def index():
-    return _render('index.html')
+    return _render('crowds.html')
 
 
 @cherrypy.expose
-def list():
+def search():
     return _render('list.html')
 
 
 @cherrypy.expose
-def snapshot():
-    return _render('snapshot.html')
-
-
-@cherrypy.expose
-def crowds():
-    return _render('crowds.html')
+def about():
+    return _render('about.html')
 
 
 def _chart_html(stamps, crowd):

### 2011-07-23 web/static/scripts/crowd_network.js
style tweaks and fixed bug with crowd display

@@ -22,7 +22,7 @@ Renderer = function(canvas){
       ctx.strokeStyle = "#d3d3d3"
       particleSystem.eachEdge(function(edge, pt1, pt2){
           ctx.beginPath()
-          ctx.lineWidth = Math.min(10,edge.data.weight);
+          ctx.lineWidth = Math.min(5, .5*edge.data.weight)
           ctx.moveTo(pt1.x, pt1.y)
           ctx.lineTo(pt2.x, pt2.y)
           ctx.stroke()
@@ -36,7 +36,7 @@ Renderer = function(canvas){
         var lls = String(label)
         ctx.fillStyle = '#' + lls.substring(lls.length-3,lls.length)
         ctx.beginPath()
-        ctx.arc(pt.x,pt.y,3,0,2*Math.PI)
+        ctx.arc(pt.x,pt.y,2,0,2*Math.PI)
         ctx.fill()
       })
       if(labeled) {
@@ -158,8 +158,9 @@ function loadTweets(div, tweets) {
 }
 
 function loadCrowdPopup(ev) {
-    var elem = $("#crowdBox")
-    elem.html("Loading...")
+    $("#crowdBox").remove()
+    var elem = $('<div id="crowdBox">Loading...</div>')
+    elem.insertBefore("#footer")
     jQuery.getJSON('/crowd/'+ev.data.cid, function(crowd_info) {
         elem.html(crowd_info.html)
         elem.overlay({
